### 2019-02-08 article_english.tex
Word to latex first commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\addbibresource{References/article_references.bib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Procedural generation of levels fot he angry birds videogame using evolutionary computation\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
salinas.jaime1217@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
mariosky@gmail.com}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.

For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.

The evolutionary computation system as the main objective of generating structures based on the existent pieces of the game and evolving said pieces by combining them in a process that simulates the rules of the Open-Ended Evolution algorithm in which the evolution of this compounds is not inclined towards a numeric objective rather than to extend the diversity from which the pieces may be selected for a level.
\end{abstract}

\begin{IEEEkeywords}
genetic algorithm, procedural generated content, open-ended evolution, evolutionary computa
\end{IEEEkeywords}

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easines and quickness provided to generate content for diferent video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.

For this project a procedural generation content system is proposed for the game angly birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives. \cite{RovioEntertainmentCorporation2009}

While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.

In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the diferent menthods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions

\section{Background}

In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the fisrt one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.

\subsection{Procedural content generation}

Procedural content generation (PCG) denotes the way to automatically generate content by algorithms instead of generating the same content by manual means such as with different personnel.

In the videogame industry many developers use a PCG style software that produces raw images and designs used by other personnel to improve it and use it in order to reduce the development cycles, and the productions cost. 
PCG as six focus areas listed below

PCG as six focus areas listed as follows:

\begin{itemize}
    \item Level Design: This aspect involves only the design of specific sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual representations of objects on games such as giving raw designs of players faces of improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on which a game is based by trying to play as a human would in order to improve said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017}
\end{itemize}

\subsection{Genetic algorithm}
Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic algorithm (GA) is an optimization and search technique based on the principles of genetic and natural selection, it allows a population composed of many individuals, which by themselves represent a possible solution to the problem, to evolve under specific selection rules in order to obtain the maximum fitness.

In other words a genetic algorithm is a method to solve optimization problems by creating a population that will represent a possible solution and repeatedly doing genetic operations as selection, crossover and mutation on each member of the population in order to generate the members of the population for the next generation that would be closer to the best solution of the problem than their parents, the cycles in this method where the operations are made are called generations and by moving over this the population “evolves” o in other words, they get closer to the best possible solution  to a specific problem.

\begin{figure}[htbp]
\centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
\caption{Life cycle of a genetic algorithm.}
\label{fig}
\end{figure}

The main life cycle of a genetic algorithm shown of figure 1 is described as follows:
\begin{enumerate}
    \item Initialize a random n population of values suitable for the solution.
    \item Evaluate the fitness of each individual (solution) in the population.
    \item Check if the stopping criteria has been met.
    \item If not.
    \begin{enumerate}
        \item Introduce new individuals to the population by crossover operations.
        \item Mutate a random value of the new individuals.
        \item Select new cross over individuals according to their fitness for the next generation.
    \end{enumerate}
    \item Loop from step 2 until an end condition is satisfied.
    \item Select the best individual of the population as the solution for the problem
\end{enumerate}

\subsection{Open-Ended Evolution}\label{AA}
Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which the objective differs from the regular genetic algorithm one, in this case the final objective is not to reach a final state of the evolution but to continue evolving and creating new types of entities more complex on each new generation, these same entities have the possibility to evolve not only inside the frame of their type but create entirely new groups. \cite{Standish2003}

Another explanation provided by T. Taylor et al. \cite{Taylor2016} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.

For this project OEE is defined simply has a process of genetic evolution that encapsulates a group of similar processes and that is able to increase their number by the more complex the entities become.

\section{Overview of existing work}

In this Section we present some of the different approaches to the procedural generation of content for the angry birds video game.

M. Kaidan et al. \cite{Kaidan2015} propose a model in which the generation of content is controlled by the skill of a player while actively playing the game, the moment the player finishes a certain level the algorithm obtains the score and generates the next level to be played.

J. Renz et al. \cite{Renz} created an article in which the angry birds level generation contest mechanics of the IEEE Conference on Computational Intelligence and Games are based on, it explains some of the solving methods proposed by previous competitors.

Y. Jiang et al. \cite{Jiang2017} proposed the use of predefined letter style patterns and combined the to create a small pool of word used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels

\section{Current approach}

In this Section we describe the approach that was used for this project, 
The game contains a total of 11 pieces as shown on figure 2 that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:

\begin{enumerate}
\item Generate the first generation of the population
\item Run a Simulation
\item Evaluate each member of the population
\item If a member of the population has remaining pieces obtain the location and angle of the pieces, create a bundle and add it to the pool
\item Select the parents for the next generation
\item Do the crossover and mutation operations
\item Repeat the cycle
\end{enumerate}

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/list_pieces.png}}
\caption{List of pieces in the angry birds game.}
\label{fig}
\end{figure}

The Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure 3, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
\caption{Structure at beginning and end of a simulation.}
\label{fig}
\end{figure}

In order to add a bundle of pieces as a new component first it has to be measured, an imaginary bounding box is defined by calculating the lengths of all the pieces, finding the borders of said pieces and find the points that could define a box around all of them, calculate the height and width then calculate the center point of said box and calculate the offsets from the center of the group to the center of each respective piece as shown on figure 4, this information is needed in order to add it as a new element so it can be used to place the pieces in their respective new positions when the files needed for the simulation are being created.

The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/bounding_box_calculation.png}}
\caption{bounding box calculation.}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/chromosome_chain_example.png}}
\caption{Chromosome chain of an individual.}
\label{fig}
\end{figure}

Once the pieces have been added and the individuals are ready to be evaluated a simulation on the game environment is scheduled by order in the population, all the individuals have a maximum of ten seconds to maintain balance or reach absolute stability, if absolute stability is reached it means one of two things, first the generated structure is completely stable or second, the tower fell to either side and the pieces were destroyed or stopped moving by gravitational pull, when either of this happens by more than two seconds the simulation ends regardless of time remaining and the next individual is simulated.

The evaluation process for this project is still in the development stages, however in order to check that the evolution is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be a elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.

First, after each of the individual simulations are over the evaluation process takes place, in this phase the resulting level is checked for pieces, each one of them is counted and then the resulting number is compared to that of the initial quantity of pieces that were originally put in before the simulation in order to calculate the first element of the evaluation process, each piece represents a certain percentage of 100\% so the missing pieces are subtracted from the total.

Second, after removing percentage according to the missing pieces an individual remaining pieces are checked for their positions in comparison to the original ones before the simulation, using the formula 1 each piece within the individual is evaluated according to the center point of the piece, if the piece moved more than a certain threshold half the percentage for one piece is removed from the remaining percentage, after this using the formula 2 the position of the piece is further checked this time by the difference in angle from the original one, in case the difference of angles is more than a certain threshold half a piece value is further removed from the total.

\begin{equation}
    \begin{aligned}
    error_{xy} = \left\{ \,
        \begin{IEEEeqnarraybox}[][c]{l?s}
            \IEEEstrut
            0.1 & if $ 0.08 > d $, \\
            \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
            \IEEEstrut
        \end{IEEEeqnarraybox}
    \right. \\
    where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
    \end{aligned}
\end{equation}

\begin{equation}
    \begin{aligned}
    error_{r} = \left\{ \,
        \begin{IEEEeqnarraybox}[][c]{l?s}
            \IEEEstrut
            0 & if $ -5 \le r \le 5 $, \\
            \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 or r > 5 $.
            \IEEEstrut
        \end{IEEEeqnarraybox}
    \right. \\
    where: r= |rotation_0| - |rotation_f|   
    \end{aligned}
\end{equation}

Finally, the total height of the remaining group of pieces is calculated by combining the bonding boxes of all pieces, then the individuals are ordered by the obtained percentage and then further ordered by the total height, this way the most balanced ones will have the best probability to be selected together for a crossover operation to create the next generation.

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/result_example.png}}
\caption{Result samples of current system.}
\label{fig}
\end{figure}

\section{Future work}
Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 7, using this rule different distribution groups or masks are created has shown on figure 8 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 9.
Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure 8 there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also propose to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual

\begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
    \caption{Rule of thirds example.}
    \label{fig}
\end{figure}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
    \caption{Rule of thirds applied to an individual.}
    \label{fig}
\end{figure}

\section{Conclusions}

The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games

\printbibliography
\newrefcontext[sorting=ydnt]

\end{document}

### 2019-02-20 IEEE_ConferenceOnGames/Template_Files/thesis_base.tex
Moved required files and added the book chapter format

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{sPaper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernandez Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This documents is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-02-20 Springer_IntlCongress/author/authorsample.tex
Moved required files and added the book chapter format

--- 2019-02-08 article_english.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
+%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% sample root file for your "contribution" to a contributed volume
+%
+% Use this file as a template for your own input.
+%
+%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[graybox]{svmult}
+
+% choose options for [] as required from the list
+% in the Reference Guide
+
+\usepackage{type1cm}        % activate if the above 3 fonts are
+                            % not available on your system
+%
+\usepackage{makeidx}         % allows index generation
+\usepackage{graphicx}        % standard LaTeX graphics tool
+                             % when including figure files
+\usepackage{multicol}        % used for the two-column index
+\usepackage[bottom]{footmisc}% places footnotes at page bottom
+
+\usepackage{newtxtext}       % 
+\usepackage{newtxmath}       % selects Times Roman as basic font
+
 \usepackage{xcolor}
-\addbibresource{References/article_references.bib}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage[misc]{ifsym}
+
+\renewcommand*\keywordname{\textbf{keywords}}
+%\usepackage[backedn=biber,style=numeric,sorting=none]{biblatex}
+%\addbibresource{References/article_references.bib}
+
+% see the list of further useful packages
+% in the Reference Guide
+
+\makeindex             % used for the subject index
+                       % please use the style svind.ist with
+                       % your makeindex program
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\title{Procedural generation of levels fot he angry birds videogame using evolutionary computation\\
-}
-
-\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
-\textit{Tijuana Institute of Technology}\\
-Tijuana, México \\
-salinas.jaime1217@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
-\textit{Tijuana Institute of Technology}\\
-Tijuana, México \\
-mariosky@gmail.com}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-}
-
+\title*{Procedural generation of levels for the angry birds videogame using evolutionary computation}
+% Use \titlerunning{Short Title} for an abbreviated version of
+% your contribution title if the original one is too long
+\author{\textbf{Jaime Salinas-Hernández and Mario Garcia-Valdez}}
+% Use \authorrunning{Short Title} for an abbreviated version of
+% your contribution title if the original one is too long
+\institute{Jaime Salinas-Hernández \at Tijuana Institute of Technology, Tijuana, México \email{salinas.jaime1217@gmail.com}
+\and Mario Garcia-Valdez(\Letter) \at Tijuana Institute of Technology, Tijuana, México \email{mariosky@gmail.com}}
+%
+% You can put both on the same level as in:
+% Name
+% e-mail
+% Name 2
+% e-mail 2
+% Institution
+%
+% Use the package "url.sty" to avoid
+% problems with special characters
+% used in your e-mail or web address
+%
+\titlerunning{Procedural generation of levels for the angry birds videogame}
 \maketitle
 
-\begin{abstract}
-This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
+\abstract{This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
+For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.
+The evolutionary computation system as the main objective of generating structures based on the existent pieces of the game and evolving said pieces by combining them in a process that simulates the rules of the Open-Ended Evolution algorithm in which the evolution of this compounds is not inclined towards a numeric objective rather than to extend the diversity from which the pieces may be selected for a level.}
 
-For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.
-
-The evolutionary computation system as the main objective of generating structures based on the existent pieces of the game and evolving said pieces by combining them in a process that simulates the rules of the Open-Ended Evolution algorithm in which the evolution of this compounds is not inclined towards a numeric objective rather than to extend the diversity from which the pieces may be selected for a level.
-\end{abstract}
-
-\begin{IEEEkeywords}
-genetic algorithm, procedural generated content, open-ended evolution, evolutionary computa
-\end{IEEEkeywords}
+\keywords{Genetic Algorithm, Procedural generated content, Open-ended evolution, Evolutionary computation}
 
 \section{Introduction}
+\label{sec:1}
 Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easines and quickness provided to generate content for diferent video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
@@
 \section{Background}
-
+\label{sec:3}
 In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the fisrt one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
@@
 \subsection{Genetic algorithm}
+
 Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic algorithm (GA) is an optimization and search technique based on the principles of genetic and natural selection, it allows a population composed of many individuals, which by themselves represent a possible solution to the problem, to evolve under specific selection rules in order to obtain the maximum fitness.
@@
 
-\subsection{Open-Ended Evolution}\label{AA}
+\subsection{Open-Ended Evolution}
+
 Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which the objective differs from the regular genetic algorithm one, in this case the final objective is not to reach a final state of the evolution but to continue evolving and creating new types of entities more complex on each new generation, these same entities have the possibility to evolve not only inside the frame of their type but create entirely new groups.
@@
 \cite{Kaidan2015} propose a model in which the generation of content is controlled by the skill of a player while actively playing the game, the moment the player finishes a certain level the algorithm obtains the score and generates the next level to be played.
+The generation of the levels is based on a formula which take into account the average velocities to evaluate the levels however the generation of the levels did not take into account the number of birds and pigs placed on the level and as such the levels wee able to be clared with ease by the participants.
 
@@
 \cite{Renz} created an article in which the angry birds level generation contest mechanics of the IEEE Conference on Computational Intelligence and Games are based on, it explains some of the solving methods proposed by previous competitors.
+Here it is explained that there are two tracks of the angry birds competition, the first one is focused on training agents capable of playing the game as well as a human could, taking into consideration the angle of the shots and the movement or destruction of the pieces created with that shot, the second track of the competition is based on the levels themselves in which a system can automatically create levels that are interesting to a human player, playable as well as difficult able to be completed with a given amount of birds.
 
@@
 Jiang et al.
-\cite{Jiang2017} proposed the use of predefined letter style patterns and combined the to create a small pool of word used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels
+\cite{Jiang2017} proposed the use of predefined letter style patterns and combined to create a small pool of words used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels, the way the requirements for the competition were fullfilled were by creating the letter structures as stable as possible, use the provided layered structures, generating a said number of usable birds and pigs by using an heuristic calculation.
 
@@
     \begin{aligned}
-    error_{xy} = \left\{ \,
-        \begin{IEEEeqnarraybox}[][c]{l?s}
-            \IEEEstrut
-            0.1 & if $ 0.08 > d $, \\
+        error_{xy} =
+            \begin{cases}
+                0.1 & if 0.08 > d, \\
                 \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
-            \IEEEstrut
-        \end{IEEEeqnarraybox}
-    \right. \\
+            \end{cases} \\
         where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
@@
     \begin{aligned}
-    error_{r} = \left\{ \,
-        \begin{IEEEeqnarraybox}[][c]{l?s}
-            \IEEEstrut
-            0 & if $ -5 \le r \le 5 $, \\
+    error_{r} = 
+        \begin{cases}
+            0 & if -5 \le r \le 5, \\
             \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 or r > 5 $.
-            \IEEEstrut
-        \end{IEEEeqnarraybox}
-    \right. \\
+        \end{cases} \\
     where: r= |rotation_0| - |rotation_f|   
@@
 
-\printbibliography
-\newrefcontext[sorting=ydnt]
-
+\bibliographystyle{ieeetr}
+\bibliography{article_references}
 \end{document}

### 2019-02-20 Springer_IntlCongress/author/english.tex
Moved required files and added the book chapter format

--- 2019-02-20 Springer_IntlCongress/author/authorsample.tex
@@
 % your contribution title if the original one is too long
-\institute{Jaime Salinas-Hernández \at Tijuana Institute of Technology, Tijuana, México \email{salinas.jaime1217@gmail.com}
-\and Mario Garcia-Valdez(\Letter) \at Tijuana Institute of Technology, Tijuana, México \email{mariosky@gmail.com}}
+\institute{Jaime Salinas-Hernández $\cdot$ Mario Garcia-Valdez(\Letter) \\ Department of Computer Science \at Tijuana Institute of Technology, Tijuana, México \\
+\email{salinas.jaime1217@gmail.com, mariosky@gmail.com}}
 %

### 2019-02-20 Springer_IntlCongress/author/references.tex
Moved required files and added the book chapter format

%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
\biblstarthook{}

\begin{thebibliography}{10}

    \bibitem{DarrenRowse} Darren Rowse: Rule of Thirds in Photography.
    \bibitem{Holland1975} John~H. Holland.: Adaptation in Natural and Artificial Systems In:Sgart Newsletter, 1975.
    \bibitem{Jiang2017} Yuxuan Jiang, Tomohiro Harada, and Ruck Thawonmas.: Procedural generation of angry birds fun levels using pattern-struct and preset-model In: IEEE Conference on Computational Intelligence and Games, 2017.
    \bibitem{Kaidan2015} Misaki Kaidan, Chun~Yin Chu, Tomohiro Harada, and Ruck Thawonmas.: Procedural generation of angry birds levels that adapt to the player's skills using genetic algorithm}. In: 2015 IEEE 4th Global Conference on Consumer Electronics (GCCE), pages 535--536. IEEE, oct 2015.
    \bibitem{Renz} Jochen Renz, Xiaoyu Ge, Rohan Verma, and Peng Zhang.: Angry Birds as a Challenge for Artificial Intelligence. In: Technical report.
    \bibitem{RovioEntertainmentCorporation2009} Rovio Entertainment Corporation}. In: Angry Birds, 2009.
    \bibitem{Smith2009} Gillian Smith, Mike Treanor, Jim Whitehead, and Michael Mateas.: Rhythm-Based Level Generation for 2D Platformers. In:Technical report, 2009.
    \bibitem{Standish2003}Russell~K Standish.: OPEN-ENDED ARTIFICIAL EVOLUTION. In:Technical Report~2, 2003.
    \bibitem{Sural} S.~Sural and P.K. Das.: A genetic algorithm for feature selection in a neuro-fuzzy OCR system. In: Proceedings of Sixth International Conference on Document Analysis and Recognition}, pages 987--991. IEEE Comput. Soc.
    \bibitem{Taylor2016} Tim Taylor, Mark Bedau, Alastair Channon, David Ackley, Wolfgang Banzhaf, Guillaume Beslon, Emily Dolson, Tom Froese, Simon Hickinbotham, Takashi Ikegami, Barry McMullin, Norman Packard, Steen Rasmussen, Nathaniel Virgo, Eran Agmon, Edward Clark, Simon McGregor, Charles Ofria, Glen Ropella, Lee Spector, Kenneth~O. Stanley, Adam Stanton, Christopher Timperley, Anya Vostinar, and Michael Wiser.: Open-Ended Evolution: Perspectives from the OEE Workshop in York. In: Artificial Life, 22(3):408--423, aug 2016.
    \bibitem{Yannakakis2017} Georgios~N Yannakakis and Julian Togelius.: Artificial Intelligence and Games (First Public Draft). page 359, 2017.

\end{thebibliography}

### 2019-02-28 Springer_IntlCongress/author/authorsample.tex
Modification to the book chapter document

@@
 %
-\titlerunning{Procedural generation of levels for the angry birds videogame}
+\titlerunning{Procedural generation of levels for the angry birds videogame ...}
 \maketitle
@@
 \label{sec:1}
-Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easines and quickness provided to generate content for diferent video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
+Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easiness and quickness provided to generate content for different video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
 
-For this project a procedural generation content system is proposed for the game angly birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
+For this project a procedural generation content system is proposed for the game angry birds, angry birds is a game developed by Rovio Entertainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
 \cite{RovioEntertainmentCorporation2009}
 
-While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.
+While it is possible to create an evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.
 
-In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the diferent menthods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions
+In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the different methods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions.
 
@@
 \label{sec:3}
-In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the fisrt one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
+In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the first one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
 
@@
 \cite{Kaidan2015} propose a model in which the generation of content is controlled by the skill of a player while actively playing the game, the moment the player finishes a certain level the algorithm obtains the score and generates the next level to be played.
-The generation of the levels is based on a formula which take into account the average velocities to evaluate the levels however the generation of the levels did not take into account the number of birds and pigs placed on the level and as such the levels wee able to be clared with ease by the participants.
+The generation of the levels is based on a formula which take into account the average velocities to evaluate the levels however the generation of the levels did not take into account the number of birds and pigs placed on the level and as such the levels were able to be cleared with ease by the participants.
 
@@
 Jiang et al.
-\cite{Jiang2017} proposed the use of predefined letter style patterns and combined to create a small pool of words used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels, the way the requirements for the competition were fullfilled were by creating the letter structures as stable as possible, use the provided layered structures, generating a said number of usable birds and pigs by using an heuristic calculation.
+\cite{Jiang2017} proposed the use of predefined letter style patterns and combined to create a small pool of words used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels, the way the requirements for the competition were fulfilled were by creating the letter structures as stable as possible, use the provided layered structures, generating a said number of usable birds and pigs by using an heuristic calculation.
 
@@
 
-In this Section we describe the approach that was used for this project, 
+In this Section we describe the approach that was used for the development of this project, first presenting a quick overview of the integration of a genetic algorithm with the combination of pieces, the way the open-ended segment of the project handled the creation of new compounds for the pool of pieces and then an explanation on the way the individuals are evaluated.
+
 The game contains a total of 11 pieces as shown on figure 2 that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:
@@
 
-The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population
+The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population.
 
@@
 
-The evaluation process for this project is still in the development stages, however in order to check that the evolution is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be a elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.
+The evaluation process for this project is still in the development stages, however in order to check that the evolution is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be an elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.
 
@@
 
+Using the proposed approach a modification to the generation of individuals was developed, this modification allowed the generation to create structures that are able to maintain balance except for some cases where some element of the individual where irregular pieces, this pieces like triangles and circles when placed in positions between the base of the tower to before the top caused the tower to fall depending if the subsequent pieces in the individual where able to outbalance the structure.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/results_v1.png}}
+    \caption{Results with current approach.}
+    \label{fig}
+    \end{figure}
+
+With this in consideration the results as shown in figure 6 and subsequently figure 7 where able to be obtained, however since the objective of the project is to construct more complex structures the obtained results will be used as a base for the further development of the project with the implementation of the concepts presented in the future work section.
+
 \section{Future work}
-Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 7, using this rule different distribution groups or masks are created has shown on figure 8 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 9.
-Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure 8 there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also propose to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual
+Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 8, using this rule different distribution groups or masks are created has shown on figure 9 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 10.
+
+Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure 8 there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also propose to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual.
 
@@
     \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
+    \caption{Masks examples with the rule of thirds.}
+    \label{fig}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/chromosome_thirds.png}}
     \caption{Rule of thirds applied to an individual.}
@@
 
+Another proposed method for the evolution of the individuals is to use a mutation operation that is capable of adding or removing pieces from an individual, this way the diversity of the population will be greater on future generations, also by using the same mutation idea a change on the mask assigned to a particular individual can be modified as well, in the case a mask is either too small or too big for an individual because of the orientation of the pieces a precaution has been created, in case the mask is too small for the number of pieces after filling the mask areas the code will take the remaining pieces and begin placing them as if the mask was repeated, and in the case the number of pieces is too small the system will simply return the pieces that were able to be fitted in and continue with the process as usual.
+
 \section{Conclusions}
 
-The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games
+The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games.
 

### 2019-05-13 IEEE_ConferenceOnGames/article_english.tex
Updated article

--- 2019-02-08 article_english.tex
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
+\author{\IEEEauthorblockN{ Jaime Salinas-Hernández}
 \IEEEauthorblockA{\textit{Department of Computer Science} \\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
+\IEEEauthorblockN{ Mario Garcia-Valdez}
 \IEEEauthorblockA{\textit{Department of Computer Science} \\
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockN{ Given Name Surname}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \caption{Life cycle of a genetic algorithm.}
-\label{fig}
+\label{algorithm_model}
 \end{figure}
 
-The main life cycle of a genetic algorithm shown of figure 1 is described as follows:
+The main life cycle of a genetic algorithm shown of figure \ref{algorithm_model} is described as follows:
 \begin{enumerate}
@@
 In this Section we describe the approach that was used for this project, 
-The game contains a total of 11 pieces as shown on figure 2 that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:
+The game contains a total of 11 pieces as shown on figure \ref{piece_list} that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:
 
@@
 \caption{List of pieces in the angry birds game.}
-\label{fig}
+\label{piece_list}
 \end{figure}
 
-The Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure 3, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
+The rules for the competition specify that a configuration file must be used to generate the levels of the game in a limited amount of time, the infornmation on the configuration file is first the number of \textbf{\textit{diferent}} levels that must be generated, the second value is the diferent materials \textit{not allowed} to be used, for instance a group of generated levels must not have circles which composition material is ice or stone moreover it des not have to integrate a triangle piece with ice, stone or wood material so this combinations must be removed from the pool of options, the third configuration value is the \textit{number of pigs} that must be placed in a level, and finally the \textit{limit} of time that the system has to create the required amount of levels.
+
+After taking into account this restrictions the strcture of our current approach had to be changed, so this section will be divided in tow subsections, the first will explain the approach that was used and after that second will explain the modifications that had to be made in order to integrate the configuration files for the competition.
+
+\subsection{Original approach}
+
+Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure \ref{test_old}, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
 
@@
 \caption{Structure at beginning and end of a simulation.}
-\label{fig}
+\label{test_old}
 \end{figure}
 
-In order to add a bundle of pieces as a new component first it has to be measured, an imaginary bounding box is defined by calculating the lengths of all the pieces, finding the borders of said pieces and find the points that could define a box around all of them, calculate the height and width then calculate the center point of said box and calculate the offsets from the center of the group to the center of each respective piece as shown on figure 4, this information is needed in order to add it as a new element so it can be used to place the pieces in their respective new positions when the files needed for the simulation are being created.
+In order to add a bundle of pieces as a new component first it has to be measured, an imaginary bounding box is defined by calculating the lengths of all the pieces, finding the borders of said pieces and find the points that could define a box around all of them, calculate the height and width then calculate the center point of said box and calculate the offsets from the center of the group to the center of each respective piece as shown on figure \ref{bounding_boc_calc}, this information is needed in order to add it as a new element so it can be used to place the pieces in their respective new positions when the files needed for the simulation are being created.
 
-The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population
+The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure \ref{old_chrom} where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population
 
@@
 \centerline{\includegraphics[width=80mm]{Images/bounding_box_calculation.png}}
-\caption{bounding box calculation.}
-\label{fig}
+\caption{Bounding box calculation.}
+\label{bounding_boc_calc}
 \end{figure}
@@
 \caption{Chromosome chain of an individual.}
-\label{fig}
+\label{old_chrom}
 \end{figure}
@@
     \end{aligned}
+    \label{error_xy}
 \end{equation}
@@
     \end{aligned}
+    \label{error_angle}
 \end{equation}
@@
 \caption{Result samples of current system.}
-\label{fig}
+\label{results_old}
 \end{figure}
 
-\section{Future work}
-Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 7, using this rule different distribution groups or masks are created has shown on figure 8 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 9.
-Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure 8 there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also propose to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual
+Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure \ref{rule_of_thirds}, using this rule different distribution groups or masks are created has shown on figure \ref{rule_of_thirds_applied} in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure \ref{results_old}.
 
@@
     \caption{Rule of thirds example.}
-    \label{fig}
+    \label{rule_of_thirds}
 \end{figure}
@@
     \caption{Rule of thirds applied to an individual.}
-    \label{fig}
+    \label{rule_of_thirds_masks}
 \end{figure}
+
+Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure \ref{rule_of_thirds_masks} there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also proposed to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual, this way the results shown on figure \ref{rule_of_thirds_result} are obtained, this however gave us a new problem because as shown in the image and the previous image as well the were instances in which a certain combination of pieces could be to big for the area and this pieces resulted in a level that had structural flaws from the beginning which cold provoke the entire structure and immeadiately nearby others to fall at the beginning of the simulation however it was able to
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/chromosome_thirds.png}}
+    \caption{Rule of thirds applied to an individual.}
+    \label{rule_of_thirds_applied}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/result_example_thirds.png}}
+    \caption{Results obtained with rule of thirds.}
+    \label{rule_of_thirds_result}
+\end{figure}
+
+\subsection{New approach}
+
+The first differece that the new approach as is that the masks that are assigned to each individual are no longer pre-generated ones, this is because we decided that pre-generating them would not allow the generator to \textit{evolve} because the individuals would be limited to a certain number of possibles combinations which will in turn prevent diversity in the population, so in order to prevent this the modification to this section allows the individuals to generate a mask in which a number of columns is defines by default but the amount of pieces in each one is random, however the total of assigned pieces in all columns must be the same as the total pieces alloweed in each individual which is a number assigned at before beginning the system, an example of this can be seen in figure \ref{new_chrom} where the total of pieces in a individual is 18 and this pieces are distributed on all the columns available.
+This is further explained in this section.
+
+The competition also requires that a generator gives a set output a file is used to simulate the ruleset provided at a competition, this \textit{text file (parameters.txt)} provides the specifications that must be met in the competition, the parameters in the file are as follows:
+
+\begin{itemize}
+    \item Total requiered levels
+    \item Restrictions to pieces or piece-material combinations that cannot be placed or used in the levels, in this case if the file specifies that a \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be able to verify that said combination is not used.
+    \item Total number of pigs, this value can be a single value or a range of values that represent how many pigs must be placed on a level.
+    \item The amount of time in which the system must give an output.
+\end{itemize}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=80mm]{Images/chromosome_chain_new_model.png}}
+\caption{New chromosome chain.}
+\label{new_chrom}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=80mm]{Images/new_model.png}}
+\caption{New system diagram based on the parameter file and the new chromosome representation.}
+\label{new_model}
+\end{figure}
+
+Using this as a base a new system diagram is proposed as shown of figure \ref{new_model} in which the file with parameters is integrated with the input data  the system requires, the way the individuals of the population are further presresented and the way the simulation phase is taken, the method to representate the individuals is proposed by dividing the individual on three layers represented as follows:
+
+\begin{itemize}
+    \item Element layer: also known as pieces layer, this layer represent the elements assigned to a particular individual by an array of numbers from 0 to infinite where each number represents a reference to the class of a piece in the selection pool including the ones generated by the OOE algorithm, the representetion of this is was shown in figure \ref{old_chrom}.
+    \item  Mask layer: this layer is represented by a 7 digit array in which the value assigned in each column represents the amount of pieces from the element layer that will be assigned to said column, a representation of this is shown on figure \ref{mask_layer}.
+    \item Enemy layer: also known as pig layer, this layer is represented by two elments a single numeric value representing the total amount of pigs assigned to the level and an array of locations for the placement of this same pigs, a representation of it is shown on figure \ref{enemy_layer}.
+\end{itemize}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/mask_layer.png}}
+    \caption{Mask array with column and fenotype representation.}
+    \label{mask_layer}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/enemy_layer.png}}
+    \caption{Amount of pigs in a level, their location relative to the mask layer (green) and fenotype representation.}
+    \label{enemy_layer}
+\end{figure}
+
+In order to select the parents of the next generation the parents are ordered by their fitness, then the system can choose between 2 options for the selection, tournament selection or roulette selection:
+
+\begin{itemize}
+    \item Tournament selection: in order to select the parent by this method the system checks the amount of crossovers assigned, then calculates the ammount of parent required to compete in pairs, then by doing a descendent selection the slots for the tournament are filled and the winners are calculated in each group.
+    \item Roulette selection: this method of selection was first decided to be used directly by giving a proportional amount of chances to be selected according to the fitness of a individual, however since one of the objectives is to obtain variety of levels the roulette must first be ranked in order to ensure that low fitness individuals can be selected as parents.
+\end{itemize}
+
+As for the crossover operations the system currently uses two types, single point crossover and double point crossover, however this crossover operation is not only applied to the piece array of an individual, but it is also applied to the mask of said individual, this way the mask can ensure that some pieces of some childs in the population are now placed in the level, this can bring the possibility that a mask that uses less pieces that it normally as can obtain a better fitness than one that uses all of them.
+An example of this two crossover thypes cna be seen in figure \ref{crossover} in which the mask of an individual is combined with another and the resulting mask for the childs have different amount of pieces to be placed.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/crossover.png}}
+    \caption{Single point crossover(up) and double point crossover(bottom) aplied to an individual mask.}
+    \label{crossover}
+\end{figure}
+
+The mutation operations of the generator work with the pieces layer of an individual, the four types of mutations used are:
+
+\begin{itemize}
+    \item Add or remove elements from the piece list
+    \item Change the piece that is being used in a point of the list
+    \item Change the material a piece is made offsets
+    \item Change the x and y coordinates of a piece
+\end{itemize}
+
+This mutations do not have to be used all at once on a single individual but depending on the probabilities they can happen all at once, since most of the pieces on a individual are mostly the same type of material then at least the material mutation can occurr on all or most of the individuals to ensure that all levels will not have all the pieces with the same material which could render a level \textit{"boring"} by the fitness function.
+
+\section{Future work}
 

### 2019-05-13 Springer_IntlCongress/author/authorsample.tex
Updated article

@@
 \usepackage{newtxmath}       % selects Times Roman as basic font
+\usepackage{minted}
 
@@
 
-\abstract{This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
+\abstract{This paper consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
 For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.
@@
 \label{sec:1}
-Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easiness and quickness provided to generate content for different video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
+Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easiness and quickness provided to generate content for different video game projects, in this paper a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
 
-For this project a procedural generation content system is proposed for the game angry birds, angry birds is a game developed by Rovio Entertainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
+For this paper a procedural generation content system is proposed for the game angry birds, angry birds is a game developed by Rovio Entertainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
 \cite{RovioEntertainmentCorporation2009}
 
-While it is possible to create an evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.
+While it is possible to create an evolutionary agent to play the levels and obtain the best score the main objective of this paper is to generate the levels that can be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way \cite{Stephenson2018,Stephenson}.
 
-In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the different methods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions.
+In Section 2, a background of the subjects used on this paper will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the generated system is explained, from the basis of the development to the different methods that have been used to progress on the different sections of the system, in Section 5 we explain the future work of the paper, where we are in the development phase and how the future implementations are to further improve the paper as well as the conclusions that we reached.
 
@@
 \label{sec:3}
-In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the first one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
+In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current paper, this section is divided in three parts, the first one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
 
@@
 In the videogame industry many developers use a PCG style software that produces raw images and designs used by other personnel to improve it and use it in order to reduce the development cycles, and the productions cost.
+\cite{togelius2016introduction}
+Nowadays there are game developer of AAA games that use software to auto generate some elements of the enviroment such as vegetation of terrain layout specialy for open-world games, this in turn cuts a great amount of development time for said games \cite{TogeliusTaxonomy,Smith2012}.
 PCG as six focus areas listed below
@@
     \item Gameplay: This aspect uses agents to test and evaluate the mechanic on which a game is based by trying to play as a human would in order to improve said mechanics.
-    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017}
+    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
 \end{itemize}
@@
 Taylor et al.
-\cite{Taylor2016} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
+\cite{Taylor2016, Taylor} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
 
-For this project OEE is defined simply has a process of genetic evolution that encapsulates a group of similar processes and that is able to increase their number by the more complex the entities become.
+For this paper OEE is defined simply has a process of genetic evolution that encapsulates a group of similar processes and that is able to increase their number by the more complex the entities become.
 
@@
 
-In this Section we describe the approach that was used for the development of this project, first presenting a quick overview of the integration of a genetic algorithm with the combination of pieces, the way the open-ended segment of the project handled the creation of new compounds for the pool of pieces and then an explanation on the way the individuals are evaluated.
+In this Section we describe the approach that was used for the development of this paper, first presenting a quick overview of the integration of a genetic algorithm with the combination of pieces, the way the open-ended segment of the system handled the creation of new compounds for the pool of pieces and then an explanation on the way the individuals are evaluated.
 
@@
 
-The Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure 3, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
+Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the system is to generate structures that are capable of maintaining their own balance as shown on figure 3, since the objective of open-ended evolution for this system is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
 
@@
 
-The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population.
+In case one or more of this pieces is rotated or needs to be rotated we defined a function that first obtains the data of a each piece in the group, finds the 4 edges of it and then if the piece needs a rotation different than 0 degrees a function to rotate the figure is called, the function returns a list of points that represent the borders of the rotated piece, after this the other pieces are processed the same way and with the points we calculate the entire bounding box as well as the center of the group that will be added.
+
+In order to create a level generation algorithm there has to be a way to represent the level structure in a a way that the genetic algorithm is able to interpret it and at the same time be able to be interpreted by the game itself \cite{togelius2016Representationsforsearch-basedmethods}, so in this case the way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population.
 
@@
 
-The evaluation process for this project is still in the development stages, however in order to check that the evolution is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be an elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.
+The evaluation process for this paper is still in the development stages, according to another work by Yannakakis et al.
+\cite{YannakakisContentGeneration} there are various ways to evaluate the generated content, one example of this a an adaptive generation to optimize the player experience \cite{Shaker2010}, however in order to check that the evolution in this current system is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be an elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.
 
@@
 
-With this in consideration the results as shown in figure 6 and subsequently figure 7 where able to be obtained, however since the objective of the project is to construct more complex structures the obtained results will be used as a base for the further development of the project with the implementation of the concepts presented in the future work section.
+With this in consideration the results as shown in figure 6 and subsequently figure 7 where able to be obtained, however since them objective of the generated system is to construct more complex structures the obtained results will be used as a base for the further development of the system with the implementation of the concepts presented in the future work section.
 
-\section{Future work}
+\section{Conclusions and future work}
+
+The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this system the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games.
+
 Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 8, using this rule different distribution groups or masks are created has shown on figure 9 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 10.
+
+Using this same distributions as a base, the masks that will be used on the individuals to balance the content in the level will be defined the example below where a value of 1 represents an area of the level that needs to have pieces and 0 represents sections were no piece will be added.
+
+\begin{minted}{Python}
+    type_castle = [[0,0,0,1,0,0,0],
+                   [1,0,1,1,1,0,1],
+                   [1,1,1,1,1,1,1]]
+    type_house = [[0,0,1,1,0,0,0],
+                  [0,1,1,1,1,0,0],
+                  [0,1,1,1,1,0,0]]
+\end{minted}
 
@@
 
-\section{Conclusions}
-
-The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games.
-
 \bibliographystyle{ieeetr}

### 2019-05-13 IEEE_ConferenceOnGames/article_english.tex
Update 13/5/2019 13:57

@@
 \begin{itemize}
-    \item Total requiered levels
+    \item Total required levels
     \item Restrictions to pieces or piece-material combinations that cannot be placed or used in the levels, in this case if the file specifies that a \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be able to verify that said combination is not used.
@@
 
+Since this group of mutations further ensures diversity in the populations a different way to evaluate the individuals is needed, by using the previous proposed method as a base a way to evaluate the \textit{"diversity"} and \textit{"uniqueness"} of a individual, for this we first remove the \textit{x} and \textit{y} position as well as the \textit{angle} errors in order to add two new evaluation formulas as follows:
+
+\begin{itemize}
+    \item Hamming distance: a simle explanation for the \textit{Hamming distance} is that it is a calculation applied to a pair of strings where the obecive is to find the minimum required number of substitutions required in order to convert a string exactly the same as the other, its formula is shown in equation \ref{hamming_distance}, since the formula itself locates the minimum required number of substitutions then we compare the individual with the rest of the population trying to found the maximum number of substitutions required efectively using the formula to give a better fitness to those individuals that are different from the group.
+    \item Shannon entropy: the shannon entropy is used on information theory to calculate the disorder or uncertainty, in this case it will be used to determine if a level is \textit{"boring"} or \textit{"interesting"} based on the amount of entropy calculated according to the pieces used in a level where a low entropy is boring because if a determined level as a lot of repeated pieces then it will look simple, the formula used is shown in equation \ref{shannon_entropy} where the elements calculated are the pieces of a level and their appearance probability against all others.
+\end{itemize}
+
+\begin{equation}
+    \begin{aligned}
+    d = min \left\{ \ d(x,y): x,y \in C, if \: x \neq y, 1 \: else \: 0 \: \right\} \
+    \end{aligned}
+    \label{hamming_distance}
+\end{equation}
+
+\begin{equation}
+    \begin{aligned}
+    S = - \Sigma_i P_i \log P_i
+    \end{aligned}
+    \label{shannon_entropy}
+\end{equation}
+
 \section{Future work}

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Updated article 12/5/2019 18:44

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
+\usepackage[style=ieee,backend=biber,style=numeric,sorting=none]{biblatex}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 
-For this project a procedural generation content system is proposed for the game angly birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
+For this project a procedural generation content system is proposed for the game angry birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game uses a gravity and collition system that allows the structures to fall and be destroyed by means of damage as well as the use of three diferent construction materials \textit{ice}, \textit{wood} and \textit{stone} each one with different resistances ranging from fragile, normal and sturdy in that order, the game mechanic is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives, it is possible to obtain a high score by doing the most destruction as possible with the least birds as you can.
 \cite{RovioEntertainmentCorporation2009}
 
-While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.
+While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels that can be played by naive agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way \cite{Stephenson,Stephenson2018}.
 
@@
 Taylor et al.
-\cite{Taylor2016} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
+\cite{Taylor2016,Taylor} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
 
@@
 
+Using all this configurations the system is capable of creating levels, some of them playable as shown in figure \ref{result_1} however the levels that can be generated are far from optimized to be played on, this is an issue that must be changed in future instances but the generator itself is able to be used as a base for a more complex one, and as shown in the future work section this issues can be solved by different means.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/Result_n2.png}}
+    \caption{Example of resulting level with current system.}
+    \label{result_1}
+\end{figure}
+
 \section{Future work}
+
+The system as been able to generate levels that fulfill the requirements provided by the parameters file, however a way to evaluate that the levels generated are indeed \textit{"fun"}
+ or \textit{"interesting"} is still needed, at this point we have two was to evaluate the results:
+ \begin{itemize}
+    \item User survey, in case a survey is used as an evaluation tool then first the system has to generate the levels and a group of people must participate by playing the levels and answering a set of questions afterwards, the questions themselves must try to capture the feeling of a person towards the game like questioning if a level was too easy or too dificult to solve, if the generated structures look interesting or if the level required them to strategize how to use the provided birds to solve the level, the survey must be applied to a equal quantity of people of three diferent game skill levels,\textit{"non video game players"}, \textit{"casual video game players"} and \textit{"avid video game players"}, this way we can evaluate a level or the entire system by knowing if all skill levels did not enjoyed a level because it was too simple or easy.
+    \item By using a naive agent, if a naive agent is used to play the levels we can obtain data of how the agent solves the levels placed before them, and the way to evaluate if the level is or not \textit{"interesting"} will be by checking how easily the aggent is able to solve a level, the point here is to have a level that cannot be solved by a single movement but to have one that a human player has to think a while to solve tryingto place the difficulty of a level just at the middle point between easy and hard difficulty levels.
+\end{itemize}
+
+Other aspects that the system need to improve is in the processing time required, since the current way to calculate the fitness and create the next generations of a population the system requires the system to execute simulations of the levels on every generation that passes therefore increasing the time it takes to complete an entire cycle of execution, so in order to change this we require to create a way to evaluate a level using only the information of the pieces, locations and pigs locations and using this data to predict the way a level will behave when placed in a real simulation environment therefore drastically reducing execution times.
+
+Finally a different method to evaluate the individuals must be created, this is because the current evaluation method allows us to generate playable levels, this levels are far from ideal in the way that they only use a certain range of items present in the game therefore reducing the potential of a level, we expect to make the current fitness function work the most eficient that it can but another possible solution is found a good combination of formulas to generate the fitness function.
 
@@
 
-The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games
+The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games.
 

### 2019-05-14 article_english.tex
Hard Text Wrap applied to the whole document.
Absrtact comments

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+% The preceding line is only needed to identify funding in the first footnote.
+% If that is unneeded, please comment it out.
 \usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
@@
 
-\title{Procedural generation of levels fot he angry birds videogame using evolutionary computation\\
+\title{Procedural generation of levels fot he angry birds videogame using
+evolutionary computation\\
 }
@@
 \author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
 \textit{Tijuana Institute of Technology}\\
@@
 \IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
 \textit{Tijuana Institute of Technology}\\
 Tijuana, México \\
-mariosky@gmail.com}
+mario@tectijuana.edu.mx}
 \and
@@
 \begin{abstract}
-This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
+% We do not say this project, is more like: In this paoer an evolutionary ... 
+% is presented or In this paper we present a .... (in third or first person plural) - MG    
+This project consisted in the generation of an evolutionary computation-based
+system capable of generate and evolve the structures of which one level of the
+Angry Birds game is composed, these structures are evaluated according to the
+stability of the structure as well as for the complexity of said structure.
+% This is not true any more. Also the evaluation of the level is not the most
+% important aspect - MG
 
-For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.
+A level generation system was designed based on the data obtained from
+the game, said data consist in the number and type of pieces that appear and the
+applied gravity of the game, proposed solutions are evaluated by a
+simulation of the generated level and then checking how the structures are
+affected by the gravity of the game. % This is not what the systems does any more
+% It seems like you are describing Laura's work - M
 
-The evolutionary computation system as the main objective of generating structures based on the existent pieces of the game and evolving said pieces by combining them in a process that simulates the rules of the Open-Ended Evolution algorithm in which the evolution of this compounds is not inclined towards a numeric objective rather than to extend the diversity from which the pieces may be selected for a level.
+The evolutionary computation system has the main objective of generating
+structures based on the existent pieces of the game and evolving said pieces by
+combining them in a process that simulates the rules of the Open-Ended Evolution
+algorithm in which the evolution of this compounds is not inclined towards a
+numeric objective rather than to extend the diversity from which the pieces may
+be selected for a level.
+
+% The abstract is not only for stating what whas done, it is also for 
+% telling readers, why they should care, what's novel, how good it is, how you tested.
+% Please get some inspirtation from other abstracts on the same subject,
+% this should be the last section we write. - M   
 \end{abstract}
@@
 \begin{IEEEkeywords}
-genetic algorithm, procedural generated content, open-ended evolution, evolutionary computa
+genetic algorithm, procedural generated content, open-ended evolution,
+evolutionary computa
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easines and quickness provided to generate content for diferent video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
+Procedural content generation is an interesting subject on the entertainment
+area, primarily in the video game industry because of the easines and quickness
+provided to generate content for diferent video game projects, in this project a
+evolutionary computation-based system is proposed to generate complex content
+for videogames based on an evolutionary algorithm and open-ended- evolution.
 
-For this project a procedural generation content system is proposed for the game angly birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game mechanics is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives.
+For this project a procedural generation content system is proposed for the game
+angly birds, angry birds is a game developed by Rovio Entrtainment in which the
+objective is to destroy structures placed on the map as well as eliminating
+green pig-like entities in order to obtain the highest score possible, the game
+mechanics is to use a slingshot to shoot a certain number of birds with
+different abilities to destroy the structures and the objectives.
 \cite{RovioEntertainmentCorporation2009}
 
-While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels can ca be played by the agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way.
+While it is possible to create a evolutionary agent to play the levels and
+obtain the best score the main objective of this project is to generate the
+levels can ca be played by the agents or physical players, the levels themselves
+need to be complex in the sense that interesting structures can be created but
+it has to be possible to complete in some way.
 
-In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the diferent menthods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions
+In Section 2, a background of the subjects used on this project will be
+presented, this subjects, while not all being used on by different authors on
+their works provide a great help on the development of the proposed system,
+Section 3, contains a quick overview of some aspects used by different authors
+in order to tackle this problem, their design and basic functionality, in
+Section 4 the description of the current state of the project is explained, from
+the basis of the development to the diferent menthods that have been used to
+progress on the different sections of the project, in Section 5 we explain the
+future work of the project, where we are in the development phase and how the
+future implementations are to further improve the project and finally, in
+Section 6 we present our conclusions
 
@@
 
-In this Section we provide a quick overview of the literature about the areas that provide the basis to the development of the current project, this section is divided in three parts, the fisrt one gives us an explanation of what procedural content generation entails, the second one provides an explanation on genetic algorithms and how can they be used to solve optimization problems, and finally, the third one provides us with an overview of Open-Ended Evolution and what it means to have an Open-Ended Evolutionary algorithm.
+In this Section we provide a quick overview of the literature about the areas
+that provide the basis to the development of the current project, this section
+is divided in three parts, the fisrt one gives us an explanation of what
+procedural content generation entails, the second one provides an explanation on
+genetic algorithms and how can they be used to solve optimization problems, and
+finally, the third one provides us with an overview of Open-Ended Evolution and
+what it means to have an Open-Ended Evolutionary algorithm.
 
@@
 
-Procedural content generation (PCG) denotes the way to automatically generate content by algorithms instead of generating the same content by manual means such as with different personnel.
+Procedural content generation (PCG) denotes the way to automatically generate
+content by algorithms instead of generating the same content by manual means
+such as with different personnel.
 
-In the videogame industry many developers use a PCG style software that produces raw images and designs used by other personnel to improve it and use it in order to reduce the development cycles, and the productions cost.
-PCG as six focus areas listed below
+In the videogame industry many developers use a PCG style software that produces
+raw images and designs used by other personnel to improve it and use it in order
+to reduce the development cycles, and the productions cost. PCG as six focus
+areas listed below
 
@@
 \begin{itemize}
-    \item Level Design: This aspect involves only the design of specific sections of a game, primarily those in which the player is able to interact.
-    \item Audio: This aspect is focused on designing soundtracks that are able to react to a player specific action.
-    \item Visuals: This area is focused on creating or improving visual representations of objects on games such as giving raw designs of players faces of improving the images of other graphics.
-    \item Narrative: This aspect is focused on the generation of readable and coherent stories or plotlines of games.
-    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on which a game is based by trying to play as a human would in order to improve said mechanics.
+    \item Level Design: This aspect involves only the design of specific
+    sections of a game, primarily those in which the player is able to interact.
+    \item Audio: This aspect is focused on designing soundtracks that are able
+    to react to a player specific action.
+    \item Visuals: This area is focused on creating or improving visual
+    representations of objects on games such as giving raw designs of players
+    faces of improving the images of other graphics.
+    \item Narrative: This aspect is focused on the generation of readable and
+    coherent stories or plotlines of games.
+    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
+    which a game is based by trying to play as a human would in order to improve
+    said mechanics.
     \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017}
@@
 \subsection{Genetic algorithm}
-Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic algorithm (GA) is an optimization and search technique based on the principles of genetic and natural selection, it allows a population composed of many individuals, which by themselves represent a possible solution to the problem, to evolve under specific selection rules in order to obtain the maximum fitness.
+Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic
+algorithm (GA) is an optimization and search technique based on the principles
+of genetic and natural selection, it allows a population composed of many
+individuals, which by themselves represent a possible solution to the problem,
+to evolve under specific selection rules in order to obtain the maximum fitness.
 
-In other words a genetic algorithm is a method to solve optimization problems by creating a population that will represent a possible solution and repeatedly doing genetic operations as selection, crossover and mutation on each member of the population in order to generate the members of the population for the next generation that would be closer to the best solution of the problem than their parents, the cycles in this method where the operations are made are called generations and by moving over this the population “evolves” o in other words, they get closer to the best possible solution  to a specific problem.
+In other words a genetic algorithm is a method to solve optimization problems by
+creating a population that will represent a possible solution and repeatedly
+doing genetic operations as selection, crossover and mutation on each member of
+the population in order to generate the members of the population for the next
+generation that would be closer to the best solution of the problem than their
+parents, the cycles in this method where the operations are made are called
+generations and by moving over this the population “evolves” o in other words,
+they get closer to the best possible solution  to a specific problem.
 
@@
 
-The main life cycle of a genetic algorithm shown of figure 1 is described as follows:
+The main life cycle of a genetic algorithm shown of figure 1 is described as
+follows:
 \begin{enumerate}
@@
     \begin{enumerate}
-        \item Introduce new individuals to the population by crossover operations.
+        \item Introduce new individuals to the population by crossover
+        operations.
         \item Mutate a random value of the new individuals.
-        \item Select new cross over individuals according to their fitness for the next generation.
+        \item Select new cross over individuals according to their fitness for
+        the next generation.
     \end{enumerate}
     \item Loop from step 2 until an end condition is satisfied.
-    \item Select the best individual of the population as the solution for the problem
+    \item Select the best individual of the population as the solution for the
+    problem
 \end{enumerate}
@@
 \subsection{Open-Ended Evolution}\label{AA}
-Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which the objective differs from the regular genetic algorithm one, in this case the final objective is not to reach a final state of the evolution but to continue evolving and creating new types of entities more complex on each new generation, these same entities have the possibility to evolve not only inside the frame of their type but create entirely new groups.
-\cite{Standish2003}
+Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which
+the objective differs from the regular genetic algorithm one, in this case the
+final objective is not to reach a final state of the evolution but to continue
+evolving and creating new types of entities more complex on each new generation,
+these same entities have the possibility to evolve not only inside the frame of
+their type but create entirely new groups. \cite{Standish2003}
 
-Another explanation provided by T.
-Taylor et al.
-\cite{Taylor2016} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
+Another explanation provided by T. Taylor et al. \cite{Taylor2016} defines OEE
+has a system capable of creating novelty beyond a point where nothing changes on
+the current group of interest rather than just converging to a stable or
+quasi-stable state.
 
-For this project OEE is defined simply has a process of genetic evolution that encapsulates a group of similar processes and that is able to increase their number by the more complex the entities become.
+For this project OEE is defined simply has a process of genetic evolution that
+encapsulates a group of similar processes and that is able to increase their
+number by the more complex the entities become.
 
@@
 
-In this Section we present some of the different approaches to the procedural generation of content for the angry birds video game.
+In this Section we present some of the different approaches to the procedural
+generation of content for the angry birds video game.
 
-M.
-Kaidan et al.
-\cite{Kaidan2015} propose a model in which the generation of content is controlled by the skill of a player while actively playing the game, the moment the player finishes a certain level the algorithm obtains the score and generates the next level to be played.
+M. Kaidan et al. \cite{Kaidan2015} propose a model in which the generation of
+content is controlled by the skill of a player while actively playing the game,
+the moment the player finishes a certain level the algorithm obtains the score
+and generates the next level to be played.
 
-J.
-Renz et al.
-\cite{Renz} created an article in which the angry birds level generation contest mechanics of the IEEE Conference on Computational Intelligence and Games are based on, it explains some of the solving methods proposed by previous competitors.
+J. Renz et al. \cite{Renz} created an article in which the angry birds level
+generation contest mechanics of the IEEE Conference on Computational
+Intelligence and Games are based on, it explains some of the solving methods
+proposed by previous competitors.
 
-Y.
-Jiang et al.
-\cite{Jiang2017} proposed the use of predefined letter style patterns and combined the to create a small pool of word used to be combined in order to create levels with text on them, the participants would play the game and after that they would be asked if they liked the layout of the levels
+Y. Jiang et al. \cite{Jiang2017} proposed the use of predefined letter style
+patterns and combined the to create a small pool of word used to be combined in
+order to create levels with text on them, the participants would play the game
+and after that they would be asked if they liked the layout of the levels
 
@@
 
-In this Section we describe the approach that was used for this project, 
-The game contains a total of 11 pieces as shown on figure 2 that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:
+In this Section we describe the approach that was used for this project, The
+game contains a total of 11 pieces as shown on figure 2 that cannot be modified,
+it is not possible to add more or modify the existing ones, with this in mind
+the purpose is to create bundles of this same pieces in different locations and
+angles in order to create structures that can be used as building blocks for
+more complex levels, in order to do this a sequence of events needs to be done
+as follows:
 
@@
 \item Evaluate each member of the population
-\item If a member of the population has remaining pieces obtain the location and angle of the pieces, create a bundle and add it to the pool
+\item If a member of the population has remaining pieces obtain the location and
+angle of the pieces, create a bundle and add it to the pool
 \item Select the parents for the next generation
@@
 
-The Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure 3, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
+The Since the algorithm has to generate more complex structures the remaining
+pieces of a member of the population have to be used has a starting point, this
+new additions to the piece pool are added to the population by the mutation
+operation, the objective in the first phase of the project is to generate
+structures that are capable of maintaining their own balance as shown on figure
+3, since the objective of open-ended evolution for this project is to add new
+bundles to the pool of options the algorithm will first run a simulation with a
+group of pieces and after it the ones that were not destroyed by falling because
+of gravity will be saved and added to the pool of options.
 
@@
 
-In order to add a bundle of pieces as a new component first it has to be measured, an imaginary bounding box is defined by calculating the lengths of all the pieces, finding the borders of said pieces and find the points that could define a box around all of them, calculate the height and width then calculate the center point of said box and calculate the offsets from the center of the group to the center of each respective piece as shown on figure 4, this information is needed in order to add it as a new element so it can be used to place the pieces in their respective new positions when the files needed for the simulation are being created.
+In order to add a bundle of pieces as a new component first it has to be
+measured, an imaginary bounding box is defined by calculating the lengths of all
+the pieces, finding the borders of said pieces and find the points that could
+define a box around all of them, calculate the height and width then calculate
+the center point of said box and calculate the offsets from the center of the
+group to the center of each respective piece as shown on figure 4, this
+information is needed in order to add it as a new element so it can be used to
+place the pieces in their respective new positions when the files needed for the
+simulation are being created.
 
-The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure 5 where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population
+The way to represent the elements of a member of the population is by using the
+id of each piece and the new added ones has a pointer to the respective data
+that needs to be obtained, this way and individual can be represented as shown
+on figure 5 where each chromosome represents a certain item in the pool of
+pieces, the numbers for this elements are assigned in a first come first served
+basis, the numbers are infinitely incremented and this same pieces can be
+repeated on each individual of the population
 
@@
 
-Once the pieces have been added and the individuals are ready to be evaluated a simulation on the game environment is scheduled by order in the population, all the individuals have a maximum of ten seconds to maintain balance or reach absolute stability, if absolute stability is reached it means one of two things, first the generated structure is completely stable or second, the tower fell to either side and the pieces were destroyed or stopped moving by gravitational pull, when either of this happens by more than two seconds the simulation ends regardless of time remaining and the next individual is simulated.
+Once the pieces have been added and the individuals are ready to be evaluated a
+simulation on the game environment is scheduled by order in the population, all
+the individuals have a maximum of ten seconds to maintain balance or reach
+absolute stability, if absolute stability is reached it means one of two things,
+first the generated structure is completely stable or second, the tower fell to
+either side and the pieces were destroyed or stopped moving by gravitational
+pull, when either of this happens by more than two seconds the simulation ends
+regardless of time remaining and the next individual is simulated.
 
-The evaluation process for this project is still in the development stages, however in order to check that the evolution is working has it should a criteria has been temporarily made as follows, each individual in the population has 100 points so before the simulation starts each of them are viable candidates to be a elite member of the population regardless relative height or complexity, then the remaining of the process is separated in three phases has follows.
+The evaluation process for this project is still in the development stages,
+however in order to check that the evolution is working has it should a criteria
+has been temporarily made as follows, each individual in the population has 100
+points so before the simulation starts each of them are viable candidates to be
+a elite member of the population regardless relative height or complexity, then
+the remaining of the process is separated in three phases has follows.
 
-First, after each of the individual simulations are over the evaluation process takes place, in this phase the resulting level is checked for pieces, each one of them is counted and then the resulting number is compared to that of the initial quantity of pieces that were originally put in before the simulation in order to calculate the first element of the evaluation process, each piece represents a certain percentage of 100\% so the missing pieces are subtracted from the total.
+First, after each of the individual simulations are over the evaluation process
+takes place, in this phase the resulting level is checked for pieces, each one
+of them is counted and then the resulting number is compared to that of the
+initial quantity of pieces that were originally put in before the simulation in
+order to calculate the first element of the evaluation process, each piece
+represents a certain percentage of 100\% so the missing pieces are subtracted
+from the total.
 
-Second, after removing percentage according to the missing pieces an individual remaining pieces are checked for their positions in comparison to the original ones before the simulation, using the formula 1 each piece within the individual is evaluated according to the center point of the piece, if the piece moved more than a certain threshold half the percentage for one piece is removed from the remaining percentage, after this using the formula 2 the position of the piece is further checked this time by the difference in angle from the original one, in case the difference of angles is more than a certain threshold half a piece value is further removed from the total.
+Second, after removing percentage according to the missing pieces an individual
+remaining pieces are checked for their positions in comparison to the original
+ones before the simulation, using the formula 1 each piece within the individual
+is evaluated according to the center point of the piece, if the piece moved more
+than a certain threshold half the percentage for one piece is removed from the
+remaining percentage, after this using the formula 2 the position of the piece
+is further checked this time by the difference in angle from the original one,
+in case the difference of angles is more than a certain threshold half a piece
+value is further removed from the total.
 
@@
 
-Finally, the total height of the remaining group of pieces is calculated by combining the bonding boxes of all pieces, then the individuals are ordered by the obtained percentage and then further ordered by the total height, this way the most balanced ones will have the best probability to be selected together for a crossover operation to create the next generation.
+Finally, the total height of the remaining group of pieces is calculated by
+combining the bonding boxes of all pieces, then the individuals are ordered by
+the obtained percentage and then further ordered by the total height, this way
+the most balanced ones will have the best probability to be selected together
+for a crossover operation to create the next generation.
 
@@
 \section{Future work}
-Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure 7, using this rule different distribution groups or masks are created has shown on figure 8 in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure 9.
-Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure 8 there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also propose to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual
+Since there is a need to create complex structures than can cover a great
+section of the play map, a method to evaluate the distribution is needed, for
+this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
+guideline used while creating imagen in which the purpose is to create
+aesthetical pleasant images where the focus point or the most important area is
+at the center of the image as shown on figure 7, using this rule different
+distribution groups or masks are created has shown on figure 8 in order to use
+them before the simulation of an individual takes place in order to distribute
+the pieces in a way that can cover more area and create more balanced levels
+instead of using a tower like distribution as shown on figure 9. Using this same
+distribution a new evaluation will be added in which according to how much of
+the area is filled a score will be given and this score will be used as a new
+sorting value at the moment of selecting individuals for the crossover
+operation, since as shown on figure 8 there is a possibility that a huge mask is
+given to an individual it can be possible that the amount of pieces will not be
+able to cover the full area given, so in order to prevent this kind of problems
+we also propose to give each mask a value that refers to the minimum amount of
+pieces and height required to fill the most of the mask then check the amount of
+pieces and height before simulation for a single individual and then randomize
+which mask of the ones that can be used will be assigned to that individual
 
@@
 
-The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games
+The use of artificial intelligence in videogames is a common thing almost since
+before the first generation of videogames on 1972 as simply entities that would
+follow a set group of actions but as the generation kept advancing the need for
+more intelligent entities appeared, as of this generation some videogames use AI
+as ways to improve the interaction between man and game, but also using it in
+order to facilitate the way videogames are created, so for this project the
+focus of using evolutionary algorithms as great interest, as a starting point a
+rather simple game can be used as a workbench of the work but it also helps us
+define how much more can be done when all the required objects are obtained,
+improve on the same system and find ways for it to be used on different other
+games
 

### 2019-05-14 article_english.tex
Mini-intro reviewed

@@
 genetic algorithm, procedural generated content, open-ended evolution,
-evolutionary computa
+evolutionary computation
 \end{IEEEkeywords}
@@
 Procedural content generation is an interesting subject on the entertainment
-area, primarily in the video game industry because of the easines and quickness
-provided to generate content for diferent video game projects, in this project a
-evolutionary computation-based system is proposed to generate complex content
-for videogames based on an evolutionary algorithm and open-ended- evolution.
+industry, primarily in the video game development because of the easines and
+quickness provided to generate content for diferent video game projects [ref] .
+In this paper an evolutionary content generation system is proposed to generate
+levels for the popular Angry Birds video game
+\cite{RovioEntertainmentCorporation2009}, taking inspiration in concepts of
+open-ended evolution.
 
-For this project a procedural generation content system is proposed for the game
-angly birds, angry birds is a game developed by Rovio Entrtainment in which the
-objective is to destroy structures placed on the map as well as eliminating
-green pig-like entities in order to obtain the highest score possible, the game
-mechanics is to use a slingshot to shoot a certain number of birds with
-different abilities to destroy the structures and the objectives.
-\cite{RovioEntertainmentCorporation2009}
+% This paragraph is redundant only uncomment if space is abundant - M
 
-While it is possible to create a evolutionary agent to play the levels and
-obtain the best score the main objective of this project is to generate the
-levels can ca be played by the agents or physical players, the levels themselves
+%For this project a procedural generation content system is proposed for the game
+%angly birds, angry birds is a game developed by Rovio Entrtainment in which the
+%objective is to destroy structures placed on the map as well as eliminating
+%green pig-like entities in order to obtain the highest score possible, the game
+%mechanics is to use a slingshot to shoot a certain number of birds with
+%different abilities to destroy the structures and the objectives.
+
+% I don't think this paragraph adds much
+While it is possible to create an evolutionary agent to play the levels and
+obtain the best score,  the main objective of this project is to generate the
+levels can ca be played by software agents or real players, the levels themselves
 need to be complex in the sense that interesting structures can be created but
 it has to be possible to complete in some way.
+
+% What is the problem?
+% How we solve it? (summary)   
+% What is learned?
 
@@
 their works provide a great help on the development of the proposed system,
+
+% Jaime, remember there is no Background need it in this type of paper 
+% Maybe that will be the introduction - M
+
 Section 3, contains a quick overview of some aspects used by different authors
@@
 the basis of the development to the diferent menthods that have been used to
-progress on the different sections of the project, in Section 5 we explain the
+progress on the different sections of the project, 
+% Normaly there is no "Future Work" section is put together with Conclusions - MG
+in Section 5 we explain the
 future work of the project, where we are in the development phase and how the

### 2019-05-14 article_english.tex
Backgound checked, more writing needed

@@
 finally, the third one provides us with an overview of Open-Ended Evolution and
+% use just one form, I prefer with no first caps open-ended evolution and let's 
+% use an abbreviation OEE - MG  
 what it means to have an Open-Ended Evolutionary algorithm.
+
+% For this conference I think we do not need to define PCG, let's think 
+% every one knows what it is. - MG
 
@@
 
-Procedural content generation (PCG) denotes the way to automatically generate
+Procedural Content Generation (PCG) denotes the way to automatically generate
 content by algorithms instead of generating the same content by manual means
@@
 
+% Jaime, you must add references to EVERY THING READ alsewhere : 
+% We do not proposed this list, please add a reference. - MG       
 \begin{itemize}
@@
 \subsection{Genetic algorithm}
-Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic
+Is a method developed by John Holland on 1975 \cite{Holland1975} % Yes ! like this - MG
+the genetic
 algorithm (GA) is an optimization and search technique based on the principles
@@
 
+% Maybe this is well known, again our implementation is what we need to describe 
+% JJ, what you think?
+
 The main life cycle of a genetic algorithm shown of figure 1 is described as
@@
 \end{enumerate}
+
+% This section and the proposed approach should be in the fron lines - MG
+
+% The problem is that we just state what it is, but we do not link it
+% with our work. Why is important? What inpired our work? 
+% There is also Novelty Search - MG
+% Also it sounds like a copy-paste from Wikipedia please check and reference
+% accordingly - MG
 

### 2019-05-14 article_english.tex
Reading proposal

@@
 
+% Pleas explain in more detail this Composites in a section.
+
+% Please use the name Composite instead of Bundle, composition is well known in
+% object oriented design.
+
 \begin{enumerate}
@@
 
-The Since the algorithm has to generate more complex structures the remaining
+% This sentence needs more work -MG
+Since the algorithm has to generate more complex structures the remaining
 pieces of a member of the population have to be used has a starting point, this
+% we don't use member of the populations, use proposed solution, candidate solution
+% or individual of the population. - MG  
 new additions to the piece pool are added to the population by the mutation
@@
 
+% New pieces are added by mutation? 
+% Please give more details to all this - MG
+
 \begin{figure}[htbp]
@@
 \end{figure}
+
+% Here it's explained better, maybe this paragraph should be moved to
+% an earlier point - MG
+
+% Needs a few touches - MG
 

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
hard wrap

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+% The preceding line is only needed to identify funding in the first footnote.
+% If that is unneeded, please comment it out.
 \usepackage[style=ieee,backend=biber,style=numeric,sorting=none]{biblatex}
@@
 \and
-\IEEEauthorblockN{ Mario Garcia-Valdez}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\IEEEauthorblockN{ Mario Garcia-Valdez} \IEEEauthorblockA{\textit{Department of
+Computer Science} \\
 \textit{Tijuana Institute of Technology}\\
@@
 \and
-\IEEEauthorblockN{ Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\IEEEauthorblockN{ Given Name Surname} \IEEEauthorblockA{\textit{dept. name of
+organization (of Aff.)} \\
 \textit{name of organization (of Aff.)}\\
 City, Country \\
-email address}
-}
+email address}}
 
@@
 \begin{abstract}
-This project consisted in the generation of an evolutionary computation-based system capable of generate and evolve the structures of which one level of the Angry Birds game is composed, these structures are evaluated according to the stability of the structure as well as for the complexity of said structure.
+This project consisted in the generation of an evolutionary computation-based
+system capable of generate and evolve the structures of which one level of the
+Angry Birds game is composed, these structures are evaluated according to the
+stability of the structure as well as for the complexity of said structure.
 
-For this a level generation system was designed based on the data obtained from the game, said data consist in the number and type of pieces that appear and the applied gravity of the game, the individuals of the group are evaluated by a simulation of the generated level and then checking how the structures are affected by the gravity of the game.
+For this a level generation system was designed based on the data obtained from
+the game, said data consist in the number and type of pieces that appear and the
+applied gravity of the game, the individuals of the group are evaluated by a
+simulation of the generated level and then checking how the structures are
+affected by the gravity of the game.
 
-The evolutionary computation system as the main objective of generating structures based on the existent pieces of the game and evolving said pieces by combining them in a process that simulates the rules of the Open-Ended Evolution algorithm in which the evolution of this compounds is not inclined towards a numeric objective rather than to extend the diversity from which the pieces may be selected for a level.
+The evolutionary computation system as the main objective of generating
+structures based on the existent pieces of the game and evolving said pieces by
+combining them in a process that simulates the rules of the Open-Ended Evolution
+algorithm in which the evolution of this compounds is not inclined towards a
+numeric objective rather than to extend the diversity from which the pieces may
+be selected for a level.
 \end{abstract}
@@
 \section{Introduction}
-Procedural content generation is an interesting subject on the entertainment area, primarily in the video game industry because of the easines and quickness provided to generate content for diferent video game projects, in this project a evolutionary computation-based system is proposed to generate complex content for videogames based on an evolutionary algorithm and open-ended- evolution.
+Procedural content generation is an interesting subject on the entertainment
+area, primarily in the video game industry because of the easines and quickness
+provided to generate content for diferent video game projects, in this project a
+evolutionary computation-based system is proposed to generate complex content
+for videogames based on an evolutionary algorithm and open-ended- evolution.
 
-For this project a procedural generation content system is proposed for the game angry birds, angry birds is a game developed by Rovio Entrtainment in which the objective is to destroy structures placed on the map as well as eliminating green pig-like entities in order to obtain the highest score possible, the game uses a gravity and collition system that allows the structures to fall and be destroyed by means of damage as well as the use of three diferent construction materials \textit{ice}, \textit{wood} and \textit{stone} each one with different resistances ranging from fragile, normal and sturdy in that order, the game mechanic is to use a slingshot to shoot a certain number of birds with different abilities to destroy the structures and the objectives, it is possible to obtain a high score by doing the most destruction as possible with the least birds as you can.
-\cite{RovioEntertainmentCorporation2009}
+For this project a procedural generation content system is proposed for the game
+angry birds, angry birds is a game developed by Rovio Entrtainment in which the
+objective is to destroy structures placed on the map as well as eliminating
+green pig-like entities in order to obtain the highest score possible, the game
+uses a gravity and collition system that allows the structures to fall and be
+destroyed by means of damage as well as the use of three diferent construction
+materials \textit{ice}, \textit{wood} and \textit{stone} each one with different
+resistances ranging from fragile, normal and sturdy in that order, the game
+mechanic is to use a slingshot to shoot a certain number of birds with different
+abilities to destroy the structures and the objectives, it is possible to obtain
+a high score by doing the most destruction as possible with the least birds as
+you can. \cite{RovioEntertainmentCorporation2009}
 
-While it is possible to create a evolutionary agent to play the levels and obtain the best score the main objective of this project is to generate the levels that can be played by naive agents or physical players, the levels themselves need to be complex in the sense that interesting structures can be created but it has to be possible to complete in some way \cite{Stephenson,Stephenson2018}.
+While it is possible to create a evolutionary agent to play the levels and
+obtain the best score the main objective of this project is to generate the
+levels that can be played by naive agents or physical players, the levels
+themselves need to be complex in the sense that interesting structures can be
+created but it has to be possible to complete in some way
+\cite{Stephenson,Stephenson2018}.
 
-In Section 2, a background of the subjects used on this project will be presented, this subjects, while not all being used on by different authors on their works provide a great help on the development of the proposed system, Section 3, contains a quick overview of some aspects used by different authors in order to tackle this problem, their design and basic functionality, in Section 4 the description of the current state of the project is explained, from the basis of the development to the diferent menthods that have been used to progress on the different sections of the project, in Section 5 we explain the future work of the project, where we are in the development phase and how the future implementations are to further improve the project and finally, in Section 6 we present our conclusions
+In Section 2, a background of the subjects used on this project will be
+presented, this subjects, while not all being used on by different authors on
+their works provide a great help on the development of the proposed system,
+Section 3, contains a quick overview of some aspects used by different authors
+in order to tackle this problem, their design and basic functionality, in
+Section 4 the description of the current state of the project is explained, from
+the basis of the development to the diferent menthods that have been used to
+progress on the different sections of the project, in Section 5 we explain the
+future work of the project, where we are in the development phase and how the
+future implementations are to further improve the project and finally, in
+Section 6 we present our conclusions
 
@@
 \begin{itemize}
-    \item Level Design: This aspect involves only the design of specific sections of a game, primarily those in which the player is able to interact.
-    \item Audio: This aspect is focused on designing soundtracks that are able to react to a player specific action.
-    \item Visuals: This area is focused on creating or improving visual representations of objects on games such as giving raw designs of players faces of improving the images of other graphics.
-    \item Narrative: This aspect is focused on the generation of readable and coherent stories or plotlines of games.
-    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on which a game is based by trying to play as a human would in order to improve said mechanics.
+    \item Level Design: This aspect involves only the design of specific
+    sections of a game, primarily those in which the player is able to interact.
+    \item Audio: This aspect is focused on designing soundtracks that are able
+    to react to a player specific action.
+    \item Visuals: This area is focused on creating or improving visual
+    representations of objects on games such as giving raw designs of players
+    faces of improving the images of other graphics.
+    \item Narrative: This aspect is focused on the generation of readable and
+    coherent stories or plotlines of games.
+    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
+    which a game is based by trying to play as a human would in order to improve
+    said mechanics.
     \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
@@
 
-The main life cycle of a genetic algorithm shown of figure \ref{algorithm_model} is described as follows:
+The main life cycle of a genetic algorithm shown of figure \ref{algorithm_model}
+is described as follows:
 \begin{enumerate}
@@
 \subsection{Open-Ended Evolution}\label{AA}
-Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which the objective differs from the regular genetic algorithm one, in this case the final objective is not to reach a final state of the evolution but to continue evolving and creating new types of entities more complex on each new generation, these same entities have the possibility to evolve not only inside the frame of their type but create entirely new groups.
-\cite{Standish2003}
+Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which
+the objective differs from the regular genetic algorithm one, in this case the
+final objective is not to reach a final state of the evolution but to continue
+evolving and creating new types of entities more complex on each new generation,
+these same entities have the possibility to evolve not only inside the frame of
+their type but create entirely new groups. \cite{Standish2003}
 
-Another explanation provided by T.
-Taylor et al.
-\cite{Taylor2016,Taylor} defines OEE has a system capable of creating novelty beyond a point where nothing changes on the current group of interest rather than just converging to a stable or quasi-stable state.
+Another explanation provided by T. Taylor et al. \cite{Taylor2016,Taylor}
+defines OEE has a system capable of creating novelty beyond a point where
+nothing changes on the current group of interest rather than just converging to
+a stable or quasi-stable state.
 
-For this project OEE is defined simply has a process of genetic evolution that encapsulates a group of similar processes and that is able to increase their number by the more complex the entities become.
+For this project OEE is defined simply has a process of genetic evolution that
+encapsulates a group of similar processes and that is able to increase their
+number by the more complex the entities become.
 
@@
 
-In this Section we describe the approach that was used for this project, 
-The game contains a total of 11 pieces as shown on figure \ref{piece_list} that cannot be modified, it is not possible to add more or modify the existing ones, with this in mind the purpose is to create bundles of this same pieces in different locations and angles in order to create structures that can be used as building blocks for more complex levels, in order to do this a sequence of events needs to be done as follows:
+In this Section we describe the approach that was used for this project, The
+game contains a total of 11 pieces as shown on figure \ref{piece_list} that
+cannot be modified, it is not possible to add more or modify the existing ones,
+with this in mind the purpose is to create bundles of this same pieces in
+different locations and angles in order to create structures that can be used as
+building blocks for more complex levels, in order to do this a sequence of
+events needs to be done as follows:
 
@@
 
-The rules for the competition specify that a configuration file must be used to generate the levels of the game in a limited amount of time, the infornmation on the configuration file is first the number of \textbf{\textit{diferent}} levels that must be generated, the second value is the diferent materials \textit{not allowed} to be used, for instance a group of generated levels must not have circles which composition material is ice or stone moreover it des not have to integrate a triangle piece with ice, stone or wood material so this combinations must be removed from the pool of options, the third configuration value is the \textit{number of pigs} that must be placed in a level, and finally the \textit{limit} of time that the system has to create the required amount of levels.
+The rules for the competition specify that a configuration file must be used to
+generate the levels of the game in a limited amount of time, the infornmation on
+the configuration file is first the number of \textbf{\textit{diferent}} levels
+that must be generated, the second value is the diferent materials \textit{not
+allowed} to be used, for instance a group of generated levels must not have
+circles which composition material is ice or stone moreover it des not have to
+integrate a triangle piece with ice, stone or wood material so this combinations
+must be removed from the pool of options, the third configuration value is the
+\textit{number of pigs} that must be placed in a level, and finally the
+\textit{limit} of time that the system has to create the required amount of
+levels.
 
-After taking into account this restrictions the strcture of our current approach had to be changed, so this section will be divided in tow subsections, the first will explain the approach that was used and after that second will explain the modifications that had to be made in order to integrate the configuration files for the competition.
+After taking into account this restrictions the strcture of our current approach
+had to be changed, so this section will be divided in tow subsections, the first
+will explain the approach that was used and after that second will explain the
+modifications that had to be made in order to integrate the configuration files
+for the competition.
 
@@
 
-Since the algorithm has to generate more complex structures the remaining pieces of a member of the population have to be used has a starting point, this new additions to the piece pool are added to the population by the mutation operation, the objective in the first phase of the project is to generate structures that are capable of maintaining their own balance as shown on figure \ref{test_old}, since the objective of open-ended evolution for this project is to add new bundles to the pool of options the algorithm will first run a simulation with a group of pieces and after it the ones that were not destroyed by falling because of gravity will be saved and added to the pool of options.
+Since the algorithm has to generate more complex structures the remaining pieces
+of a member of the population have to be used has a starting point, this new
+additions to the piece pool are added to the population by the mutation
+operation, the objective in the first phase of the project is to generate
+structures that are capable of maintaining their own balance as shown on figure
+\ref{test_old}, since the objective of open-ended evolution for this project is
+to add new bundles to the pool of options the algorithm will first run a
+simulation with a group of pieces and after it the ones that were not destroyed
+by falling because of gravity will be saved and added to the pool of options.
 
@@
 
-In order to add a bundle of pieces as a new component first it has to be measured, an imaginary bounding box is defined by calculating the lengths of all the pieces, finding the borders of said pieces and find the points that could define a box around all of them, calculate the height and width then calculate the center point of said box and calculate the offsets from the center of the group to the center of each respective piece as shown on figure \ref{bounding_boc_calc}, this information is needed in order to add it as a new element so it can be used to place the pieces in their respective new positions when the files needed for the simulation are being created.
+In order to add a bundle of pieces as a new component first it has to be
+measured, an imaginary bounding box is defined by calculating the lengths of all
+the pieces, finding the borders of said pieces and find the points that could
+define a box around all of them, calculate the height and width then calculate
+the center point of said box and calculate the offsets from the center of the
+group to the center of each respective piece as shown on figure
+\ref{bounding_boc_calc}, this information is needed in order to add it as a new
+element so it can be used to place the pieces in their respective new positions
+when the files needed for the simulation are being created.
 
-The way to represent the elements of a member of the population is by using the id of each piece and the new added ones has a pointer to the respective data that needs to be obtained, this way and individual can be represented as shown on figure \ref{old_chrom} where each chromosome represents a certain item in the pool of pieces, the numbers for this elements are assigned in a first come first served basis, the numbers are infinitely incremented and this same pieces can be repeated on each individual of the population
+The way to represent the elements of a member of the population is by using the
+id of each piece and the new added ones has a pointer to the respective data
+that needs to be obtained, this way and individual can be represented as shown
+on figure \ref{old_chrom} where each chromosome represents a certain item in the
+pool of pieces, the numbers for this elements are assigned in a first come first
+served basis, the numbers are infinitely incremented and this same pieces can be
+repeated on each individual of the population
 
@@
 
-Since there is a need to create complex structures than can cover a great section of the play map, a method to evaluate the distribution is needed, for this instance we propose using the rule of thirds \cite{DarrenRowse} which is a guideline used while creating imagen in which the purpose is to create aesthetical pleasant images where the focus point or the most important area is at the center of the image as shown on figure \ref{rule_of_thirds}, using this rule different distribution groups or masks are created has shown on figure \ref{rule_of_thirds_applied} in order to use them before the simulation of an individual takes place in order to distribute the pieces in a way that can cover more area and create more balanced levels instead of using a tower like distribution as shown on figure \ref{results_old}.
+Since there is a need to create complex structures than can cover a great
+section of the play map, a method to evaluate the distribution is needed, for
+this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
+guideline used while creating imagen in which the purpose is to create
+aesthetical pleasant images where the focus point or the most important area is
+at the center of the image as shown on figure \ref{rule_of_thirds}, using this
+rule different distribution groups or masks are created has shown on figure
+\ref{rule_of_thirds_applied} in order to use them before the simulation of an
+individual takes place in order to distribute the pieces in a way that can cover
+more area and create more balanced levels instead of using a tower like
+distribution as shown on figure \ref{results_old}.
 
@@
 
-Using this same distribution a new evaluation will be added in which according to how much of the area is filled a score will be given and this score will be used as a new sorting value at the moment of selecting individuals for the crossover operation, since as shown on figure \ref{rule_of_thirds_masks} there is a possibility that a huge mask is given to an individual it can be possible that the amount of pieces will not be able to cover the full area given, so in order to prevent this kind of problems we also proposed to give each mask a value that refers to the minimum amount of pieces and height required to fill the most of the mask then check the amount of pieces and height before simulation for a single individual and then randomize which mask of the ones that can be used will be assigned to that individual, this way the results shown on figure \ref{rule_of_thirds_result} are obtained, this however gave us a new problem because as shown in the image and the previous image as well the were instances in which a certain combination of pieces could be to big for the area and this pieces resulted in a level that had structural flaws from the beginning which cold provoke the entire structure and immeadiately nearby others to fall at the beginning of the simulation however it was able to
+Using this same distribution a new evaluation will be added in which according
+to how much of the area is filled a score will be given and this score will be
+used as a new sorting value at the moment of selecting individuals for the
+crossover operation, since as shown on figure \ref{rule_of_thirds_masks} there
+is a possibility that a huge mask is given to an individual it can be possible
+that the amount of pieces will not be able to cover the full area given, so in
+order to prevent this kind of problems we also proposed to give each mask a
+value that refers to the minimum amount of pieces and height required to fill
+the most of the mask then check the amount of pieces and height before
+simulation for a single individual and then randomize which mask of the ones
+that can be used will be assigned to that individual, this way the results shown
+on figure \ref{rule_of_thirds_result} are obtained, this however gave us a new
+problem because as shown in the image and the previous image as well the were
+instances in which a certain combination of pieces could be to big for the area
+and this pieces resulted in a level that had structural flaws from the beginning
+which cold provoke the entire structure and immeadiately nearby others to fall
+at the beginning of the simulation however it was able to
 
@@
 
-The first differece that the new approach as is that the masks that are assigned to each individual are no longer pre-generated ones, this is because we decided that pre-generating them would not allow the generator to \textit{evolve} because the individuals would be limited to a certain number of possibles combinations which will in turn prevent diversity in the population, so in order to prevent this the modification to this section allows the individuals to generate a mask in which a number of columns is defines by default but the amount of pieces in each one is random, however the total of assigned pieces in all columns must be the same as the total pieces alloweed in each individual which is a number assigned at before beginning the system, an example of this can be seen in figure \ref{new_chrom} where the total of pieces in a individual is 18 and this pieces are distributed on all the columns available.
-This is further explained in this section.
+The first differece that the new approach as is that the masks that are assigned
+to each individual are no longer pre-generated ones, this is because we decided
+that pre-generating them would not allow the generator to \textit{evolve}
+because the individuals would be limited to a certain number of possibles
+combinations which will in turn prevent diversity in the population, so in order
+to prevent this the modification to this section allows the individuals to
+generate a mask in which a number of columns is defines by default but the
+amount of pieces in each one is random, however the total of assigned pieces in
+all columns must be the same as the total pieces alloweed in each individual
+which is a number assigned at before beginning the system, an example of this
+can be seen in figure \ref{new_chrom} where the total of pieces in a individual
+is 18 and this pieces are distributed on all the columns available. This is
+further explained in this section.
 
-The competition also requires that a generator gives a set output a file is used to simulate the ruleset provided at a competition, this \textit{text file (parameters.txt)} provides the specifications that must be met in the competition, the parameters in the file are as follows:
+The competition also requires that a generator gives a set output a file is used
+to simulate the ruleset provided at a competition, this \textit{text file
+(parameters.txt)} provides the specifications that must be met in the
+competition, the parameters in the file are as follows:
 
@@
     \item Total required levels
-    \item Restrictions to pieces or piece-material combinations that cannot be placed or used in the levels, in this case if the file specifies that a \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be able to verify that said combination is not used.
-    \item Total number of pigs, this value can be a single value or a range of values that represent how many pigs must be placed on a level.
+    \item Restrictions to pieces or piece-material combinations that cannot be
+    placed or used in the levels, in this case if the file specifies that a
+    \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be
+    able to verify that said combination is not used.
+    \item Total number of pigs, this value can be a single value or a range of
+    values that represent how many pigs must be placed on a level.
     \item The amount of time in which the system must give an output.
@@
 
-Using this as a base a new system diagram is proposed as shown of figure \ref{new_model} in which the file with parameters is integrated with the input data  the system requires, the way the individuals of the population are further presresented and the way the simulation phase is taken, the method to representate the individuals is proposed by dividing the individual on three layers represented as follows:
+Using this as a base a new system diagram is proposed as shown of figure
+\ref{new_model} in which the file with parameters is integrated with the input
+data  the system requires, the way the individuals of the population are further
+presresented and the way the simulation phase is taken, the method to
+representate the individuals is proposed by dividing the individual on three
+layers represented as follows:
 
 \begin{itemize}
-    \item Element layer: also known as pieces layer, this layer represent the elements assigned to a particular individual by an array of numbers from 0 to infinite where each number represents a reference to the class of a piece in the selection pool including the ones generated by the OOE algorithm, the representetion of this is was shown in figure \ref{old_chrom}.
-    \item  Mask layer: this layer is represented by a 7 digit array in which the value assigned in each column represents the amount of pieces from the element layer that will be assigned to said column, a representation of this is shown on figure \ref{mask_layer}.
-    \item Enemy layer: also known as pig layer, this layer is represented by two elments a single numeric value representing the total amount of pigs assigned to the level and an array of locations for the placement of this same pigs, a representation of it is shown on figure \ref{enemy_layer}.
+    \item Element layer: also known as pieces layer, this layer represent the
+    elements assigned to a particular individual by an array of numbers from 0
+    to infinite where each number represents a reference to the class of a piece
+    in the selection pool including the ones generated by the OOE algorithm, the
+    representetion of this is was shown in figure \ref{old_chrom}.
+    \item  Mask layer: this layer is represented by a 7 digit array in which the
+    value assigned in each column represents the amount of pieces from the
+    element layer that will be assigned to said column, a representation of this
+    is shown on figure \ref{mask_layer}.
+    \item Enemy layer: also known as pig layer, this layer is represented by two
+    elments a single numeric value representing the total amount of pigs
+    assigned to the level and an array of locations for the placement of this
+    same pigs, a representation of it is shown on figure \ref{enemy_layer}. 
 \end{itemize}
@@
 
-In order to select the parents of the next generation the parents are ordered by their fitness, then the system can choose between 2 options for the selection, tournament selection or roulette selection:
+In order to select the parents of the next generation the parents are ordered by
+their fitness, then the system can choose between 2 options for the selection,
+tournament selection or roulette selection:
 
 \begin{itemize}
-    \item Tournament selection: in order to select the parent by this method the system checks the amount of crossovers assigned, then calculates the ammount of parent required to compete in pairs, then by doing a descendent selection the slots for the tournament are filled and the winners are calculated in each group.
-    \item Roulette selection: this method of selection was first decided to be used directly by giving a proportional amount of chances to be selected according to the fitness of a individual, however since one of the objectives is to obtain variety of levels the roulette must first be ranked in order to ensure that low fitness individuals can be selected as parents.
+    \item Tournament selection: in order to select the parent by this method the
+    system checks the amount of crossovers assigned, then calculates the ammount
+    of parent required to compete in pairs, then by doing a descendent selection
+    the slots for the tournament are filled and the winners are calculated in
+    each group.
+    \item Roulette selection: this method of selection was first decided to be
+    used directly by giving a proportional amount of chances to be selected
+    according to the fitness of a individual, however since one of the
+    objectives is to obtain variety of levels the roulette must first be ranked
+    in order to ensure that low fitness individuals can be selected as parents.
 \end{itemize}
 
-As for the crossover operations the system currently uses two types, single point crossover and double point crossover, however this crossover operation is not only applied to the piece array of an individual, but it is also applied to the mask of said individual, this way the mask can ensure that some pieces of some childs in the population are now placed in the level, this can bring the possibility that a mask that uses less pieces that it normally as can obtain a better fitness than one that uses all of them.
-An example of this two crossover thypes cna be seen in figure \ref{crossover} in which the mask of an individual is combined with another and the resulting mask for the childs have different amount of pieces to be placed.
+As for the crossover operations the system currently uses two types, single
+point crossover and double point crossover, however this crossover operation is
+not only applied to the piece array of an individual, but it is also applied to
+the mask of said individual, this way the mask can ensure that some pieces of
+some childs in the population are now placed in the level, this can bring the
+possibility that a mask that uses less pieces that it normally as can obtain a
+better fitness than one that uses all of them. An example of this two crossover
+thypes cna be seen in figure \ref{crossover} in which the mask of an individual
+is combined with another and the resulting mask for the childs have different
+amount of pieces to be placed.
 
@@
 
-The mutation operations of the generator work with the pieces layer of an individual, the four types of mutations used are:
+The mutation operations of the generator work with the pieces layer of an
+individual, the four types of mutations used are:
 
@@
 
-This mutations do not have to be used all at once on a single individual but depending on the probabilities they can happen all at once, since most of the pieces on a individual are mostly the same type of material then at least the material mutation can occurr on all or most of the individuals to ensure that all levels will not have all the pieces with the same material which could render a level \textit{"boring"} by the fitness function.
+This mutations do not have to be used all at once on a single individual but
+depending on the probabilities they can happen all at once, since most of the
+pieces on a individual are mostly the same type of material then at least the
+material mutation can occurr on all or most of the individuals to ensure that
+all levels will not have all the pieces with the same material which could
+render a level \textit{"boring"} by the fitness function.
 
-Since this group of mutations further ensures diversity in the populations a different way to evaluate the individuals is needed, by using the previous proposed method as a base a way to evaluate the \textit{"diversity"} and \textit{"uniqueness"} of a individual, for this we first remove the \textit{x} and \textit{y} position as well as the \textit{angle} errors in order to add two new evaluation formulas as follows:
+Since this group of mutations further ensures diversity in the populations a
+different way to evaluate the individuals is needed, by using the previous
+proposed method as a base a way to evaluate the \textit{"diversity"} and
+\textit{"uniqueness"} of a individual, for this we first remove the \textit{x}
+and \textit{y} position as well as the \textit{angle} errors in order to add two
+new evaluation formulas as follows:
 
 \begin{itemize}
-    \item Hamming distance: a simle explanation for the \textit{Hamming distance} is that it is a calculation applied to a pair of strings where the obecive is to find the minimum required number of substitutions required in order to convert a string exactly the same as the other, its formula is shown in equation \ref{hamming_distance}, since the formula itself locates the minimum required number of substitutions then we compare the individual with the rest of the population trying to found the maximum number of substitutions required efectively using the formula to give a better fitness to those individuals that are different from the group.
-    \item Shannon entropy: the shannon entropy is used on information theory to calculate the disorder or uncertainty, in this case it will be used to determine if a level is \textit{"boring"} or \textit{"interesting"} based on the amount of entropy calculated according to the pieces used in a level where a low entropy is boring because if a determined level as a lot of repeated pieces then it will look simple, the formula used is shown in equation \ref{shannon_entropy} where the elements calculated are the pieces of a level and their appearance probability against all others.
+    \item Hamming distance: a simle explanation for the \textit{Hamming
+    distance} is that it is a calculation applied to a pair of strings where the
+    obecive is to find the minimum required number of substitutions required in
+    order to convert a string exactly the same as the other, its formula is
+    shown in equation \ref{hamming_distance}, since the formula itself locates
+    the minimum required number of substitutions then we compare the individual
+    with the rest of the population trying to found the maximum number of
+    substitutions required efectively using the formula to give a better fitness
+    to those individuals that are different from the group.
+    \item Shannon entropy: the shannon entropy is used on information theory to
+    calculate the disorder or uncertainty, in this case it will be used to
+    determine if a level is \textit{"boring"} or \textit{"interesting"} based on
+    the amount of entropy calculated according to the pieces used in a level
+    where a low entropy is boring because if a determined level as a lot of
+    repeated pieces then it will look simple, the formula used is shown in
+    equation \ref{shannon_entropy} where the elements calculated are the pieces
+    of a level and their appearance probability against all others.
 \end{itemize}
@@
 
-Using all this configurations the system is capable of creating levels, some of them playable as shown in figure \ref{result_1} however the levels that can be generated are far from optimized to be played on, this is an issue that must be changed in future instances but the generator itself is able to be used as a base for a more complex one, and as shown in the future work section this issues can be solved by different means.
+Using all this configurations the system is capable of creating levels, some of
+them playable as shown in figure \ref{result_1} however the levels that can be
+generated are far from optimized to be played on, this is an issue that must be
+changed in future instances but the generator itself is able to be used as a
+base for a more complex one, and as shown in the future work section this issues
+can be solved by different means.
 
@@
 
-The system as been able to generate levels that fulfill the requirements provided by the parameters file, however a way to evaluate that the levels generated are indeed \textit{"fun"}
- or \textit{"interesting"} is still needed, at this point we have two was to evaluate the results:
+The system as been able to generate levels that fulfill the requirements
+ provided by the parameters file, however a way to evaluate that the levels
+ generated are indeed \textit{"fun"} or \textit{"interesting"} is still needed,
+ at this point we have two was to evaluate the results:
  \begin{itemize}
-    \item User survey, in case a survey is used as an evaluation tool then first the system has to generate the levels and a group of people must participate by playing the levels and answering a set of questions afterwards, the questions themselves must try to capture the feeling of a person towards the game like questioning if a level was too easy or too dificult to solve, if the generated structures look interesting or if the level required them to strategize how to use the provided birds to solve the level, the survey must be applied to a equal quantity of people of three diferent game skill levels,\textit{"non video game players"}, \textit{"casual video game players"} and \textit{"avid video game players"}, this way we can evaluate a level or the entire system by knowing if all skill levels did not enjoyed a level because it was too simple or easy.
-    \item By using a naive agent, if a naive agent is used to play the levels we can obtain data of how the agent solves the levels placed before them, and the way to evaluate if the level is or not \textit{"interesting"} will be by checking how easily the aggent is able to solve a level, the point here is to have a level that cannot be solved by a single movement but to have one that a human player has to think a while to solve tryingto place the difficulty of a level just at the middle point between easy and hard difficulty levels.
+    \item User survey, in case a survey is used as an evaluation tool then first
+    the system has to generate the levels and a group of people must participate
+    by playing the levels and answering a set of questions afterwards, the
+    questions themselves must try to capture the feeling of a person towards the
+    game like questioning if a level was too easy or too dificult to solve, if
+    the generated structures look interesting or if the level required them to
+    strategize how to use the provided birds to solve the level, the survey must
+    be applied to a equal quantity of people of three diferent game skill
+    levels,\textit{"non video game players"}, \textit{"casual video game
+    players"} and \textit{"avid video game players"}, this way we can evaluate a
+    level or the entire system by knowing if all skill levels did not enjoyed a
+    level because it was too simple or easy.
+    \item By using a naive agent, if a naive agent is used to play the levels we
+    can obtain data of how the agent solves the levels placed before them, and
+    the way to evaluate if the level is or not \textit{"interesting"} will be by
+    checking how easily the aggent is able to solve a level, the point here is
+    to have a level that cannot be solved by a single movement but to have one
+    that a human player has to think a while to solve tryingto place the
+    difficulty of a level just at the middle point between easy and hard
+    difficulty levels.
 \end{itemize}
 
-Other aspects that the system need to improve is in the processing time required, since the current way to calculate the fitness and create the next generations of a population the system requires the system to execute simulations of the levels on every generation that passes therefore increasing the time it takes to complete an entire cycle of execution, so in order to change this we require to create a way to evaluate a level using only the information of the pieces, locations and pigs locations and using this data to predict the way a level will behave when placed in a real simulation environment therefore drastically reducing execution times.
+Other aspects that the system need to improve is in the processing time
+required, since the current way to calculate the fitness and create the next
+generations of a population the system requires the system to execute
+simulations of the levels on every generation that passes therefore increasing
+the time it takes to complete an entire cycle of execution, so in order to
+change this we require to create a way to evaluate a level using only the
+information of the pieces, locations and pigs locations and using this data to
+predict the way a level will behave when placed in a real simulation environment
+therefore drastically reducing execution times.
 
-Finally a different method to evaluate the individuals must be created, this is because the current evaluation method allows us to generate playable levels, this levels are far from ideal in the way that they only use a certain range of items present in the game therefore reducing the potential of a level, we expect to make the current fitness function work the most eficient that it can but another possible solution is found a good combination of formulas to generate the fitness function.
+Finally a different method to evaluate the individuals must be created, this is
+because the current evaluation method allows us to generate playable levels,
+this levels are far from ideal in the way that they only use a certain range of
+items present in the game therefore reducing the potential of a level, we expect
+to make the current fitness function work the most eficient that it can but
+another possible solution is found a good combination of formulas to generate
+the fitness function.
 
@@
 
-The use of artificial intelligence in videogames is a common thing almost since before the first generation of videogames on 1972 as simply entities that would follow a set group of actions but as the generation kept advancing the need for more intelligent entities appeared, as of this generation some videogames use AI as ways to improve the interaction between man and game, but also using it in order to facilitate the way videogames are created, so for this project the focus of using evolutionary algorithms as great interest, as a starting point a rather simple game can be used as a workbench of the work but it also helps us define how much more can be done when all the required objects are obtained, improve on the same system and find ways for it to be used on different other games.
+The use of artificial intelligence in videogames is a common thing almost since
+before the first generation of videogames on 1972 as simply entities that would
+follow a set group of actions but as the generation kept advancing the need for
+more intelligent entities appeared, as of this generation some videogames use AI
+as ways to improve the interaction between man and game, but also using it in
+order to facilitate the way videogames are created, so for this project the
+focus of using evolutionary algorithms as great interest, as a starting point a
+rather simple game can be used as a workbench of the work but it also helps us
+define how much more can be done when all the required objects are obtained,
+improve on the same system and find ways for it to be used on different other
+games.
 

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
abstract ieee doc

@@
 \author{\IEEEauthorblockN{ Jaime Salinas-Hernández}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
 \textit{Tijuana Institute of Technology}\\
@@
 \and
-\IEEEauthorblockN{ Mario Garcia-Valdez} \IEEEauthorblockA{\textit{Department of
-Computer Science} \\
+\IEEEauthorblockN{ Mario Garcia-Valdez} \IEEEauthorblockA{\textit{Department of Graduate Studies} \\
 \textit{Tijuana Institute of Technology}\\
 Tijuana, México \\
-mariosky@gmail.com}
+mario@tectijuana.edu.mx}
 \and
@@
 \begin{abstract}
+% We do not say this project, is more like: In this paoer an evolutionary ... 
+% is presented or In this paper we present a .... (in third or first person plural) - MG   
 This project consisted in the generation of an evolutionary computation-based
@@
 stability of the structure as well as for the complexity of said structure.
+% This is not true any more. Also the evaluation of the level is not the most
+% important aspect - MG
 
@@
 simulation of the generated level and then checking how the structures are
-affected by the gravity of the game.
+affected by the gravity of the game.  % This is not what the systems does any more
+% It seems like you are describing Laura's work - M
 
@@
 be selected for a level.
+
+% The abstract is not only for stating what whas done, it is also for 
+% telling readers, why they should care, what's novel, how good it is, how you tested.
+% Please get some inspirtation from other abstracts on the same subject,
+% this should be the last section we write. - M   
 \end{abstract}

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
More Comments

@@
 Procedural content generation is an interesting subject on the entertainment
-area, primarily in the video game industry because of the easines and quickness
-provided to generate content for diferent video game projects, in this project a
-evolutionary computation-based system is proposed to generate complex content
-for videogames based on an evolutionary algorithm and open-ended- evolution.
+industry, primarily in the video game development because of the easines and
+quickness provided to generate content for diferent video game projects [ref] .
+In this paper an evolutionary content generation system is proposed to generate
+levels for the popular Angry Birds video game
+\cite{RovioEntertainmentCorporation2009}, taking inspiration in concepts of
+open-ended evolution.
 
@@
 
+% What is the problem?
+% How we solve it? (summary)   
+% What is learned?
+
 In Section 2, a background of the subjects used on this project will be
@@
 their works provide a great help on the development of the proposed system,
+% Jaime, remember there is no Background need it in this type of paper 
+% Maybe that will be the introduction - MG
+
 Section 3, contains a quick overview of some aspects used by different authors
@@
 finally, the third one provides us with an overview of Open-Ended Evolution and
+% use just one form, I prefer with no first caps open-ended evolution and let's 
+% use an abbreviation OEE - MG
+
 what it means to have an Open-Ended Evolutionary algorithm.
+% For this conference I think we do not need to define PCG, let's think 
+% every one knows what it is. - MG
 
@@
 PCG as six focus areas listed as follows:
+% Jaime, you must add references to EVERY THING READ alsewhere : 
+% We do not proposed this list, please add a reference. - MG
 
@@
 \end{figure}
+% Maybe this is well known, again our implementation is what we need to describe 
+% JJ, what you think?
 
@@
 \end{figure}
+
+% Explain a bit about the competition, from the introduction
 
@@
 \subsection{Original approach}
-
+% This sentence needs more work -MG
 Since the algorithm has to generate more complex structures the remaining pieces
 of a member of the population have to be used has a starting point, this new
+% we don't use member of the populations, use proposed solution, candidate solution
+% or individual of the population. - MG
+
 additions to the piece pool are added to the population by the mutation
@@
 \end{figure}
+% Here it's explained better, maybe this paragraph should be moved to
+% an earlier point - MG
 
+% Needs a few touches - MG
 In order to add a bundle of pieces as a new component first it has to be

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to article 13/5/2019 23:14

@@
     said mechanics.
-    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
+    \item Game Design: This aspect is focused on generating the rulesets and 
+    mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
+    % The references are in this last item of the list JS
 \end{itemize}
@@
 \end{figure}
+
 % Maybe this is well known, again our implementation is what we need to describe 
@@
 
-\section{Current approach}
+\section{Approach}
 
-In this Section we describe the approach that was used for this project, The
+In this Section we describe the first approach that was used for this project, the
 game contains a total of 11 pieces as shown on figure \ref{piece_list} that
 cannot be modified, it is not possible to add more or modify the existing ones,
-with this in mind the purpose is to create bundles of this same pieces in
+with this in mind the purpose is to create composites of this same pieces in
 different locations and angles in order to create structures that can be used as
-building blocks for more complex levels, in order to do this a sequence of
+building blocks for more complex levels.
+
+Since there is no way to \textit{add} a composite to the pool of pieces of the 
+game then a way to combine both groups is needed, in order to do this first the 
+original 11 pieces of the game will be converted into composites, since the easiest
+way to read the data to create composites is by using lists then a \textit{composite} 
+of one element will be created for each piece, after this in order to add a 
+composite of pieces as a new component first a group of existing composites is 
+selected and placed in a imaginary enviroment then as a unique group they are 
+measured, an imaginary bounding box is defined by calculating the lengths of all
+the pieces, finding the borders of said pieces and then find the points that could
+define a box around all of them, then use this defined box to calculate the 
+height and width of the new composite and then calculate from 
+the center point of said box the offsets from the center of the
+group to the center of each respective piece as shown on figure
+\ref{bounding_boc_calc}, this information is needed in order to add it as a new
+composite so it can be used to place the pieces in their respective new positions
+when the files needed for the simulation are being created.
+
+So using the composite generator the order of this sequence of
 events needs to be done as follows:
@@
 % Pleas explain in more detail this Composites in a section.  
+% Here it's explained better, maybe this paragraph should be moved to
+% an earlier point - MG
 
+% Needs a few touches - MG
 % Please use the name Composite instead of Bundle, composition is well known in
@@
 \begin{enumerate}
+\item Gnerate composited to add to the pool of options
 \item Generate the first generation of the population
@@
 \item If a member of the population has remaining pieces obtain the location and
-angle of the pieces, create a bundle and add it to the pool
+angle of the pieces, create a composite and add it to the pool
 \item Select the parents for the next generation
@@
 
-The rules for the competition specify that a configuration file must be used to
+The Angry Birds level generation track is a competition where the objective is 
+to generate levels that are \textit{fun} and \textit{enjoyable} however they 
+also have to be challenging but imposible however the rules for the competition 
+specify that a configuration file must be used to
 generate the levels of the game in a limited amount of time, the infornmation on
@@
 \ref{test_old}, since the objective of open-ended evolution for this project is
-to add new bundles to the pool of options the algorithm will first run a
+to add new composites to the pool of options the algorithm will first run a
 simulation with a group of pieces and after it the ones that were not destroyed
@@
 \end{figure}
-% Here it's explained better, maybe this paragraph should be moved to
-% an earlier point - MG
-
-% Needs a few touches - MG
-In order to add a bundle of pieces as a new component first it has to be
-measured, an imaginary bounding box is defined by calculating the lengths of all
-the pieces, finding the borders of said pieces and find the points that could
-define a box around all of them, calculate the height and width then calculate
-the center point of said box and calculate the offsets from the center of the
-group to the center of each respective piece as shown on figure
-\ref{bounding_boc_calc}, this information is needed in order to add it as a new
-element so it can be used to place the pieces in their respective new positions
-when the files needed for the simulation are being created.
 
@@
 
-\section{Future work}
+\section{Conclusions and future work}
 
@@
 
-\section{Conclusions}
-
-The use of artificial intelligence in videogames is a common thing almost since
-before the first generation of videogames on 1972 as simply entities that would
-follow a set group of actions but as the generation kept advancing the need for
-more intelligent entities appeared, as of this generation some videogames use AI
-as ways to improve the interaction between man and game, but also using it in
-order to facilitate the way videogames are created, so for this project the
-focus of using evolutionary algorithms as great interest, as a starting point a
-rather simple game can be used as a workbench of the work but it also helps us
-define how much more can be done when all the required objects are obtained,
-improve on the same system and find ways for it to be used on different other
-games.
-
 \printbibliography

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to article 15/5/2019 00:44

@@
 industry, primarily in the video game development because of the easines and
-quickness provided to generate content for diferent video game projects [ref] .
+quickness provided to generate content for different video game projects [ref] .
 In this paper an evolutionary content generation system is proposed to generate
@@
 uses a gravity and collition system that allows the structures to fall and be
-destroyed by means of damage as well as the use of three diferent construction
+destroyed by means of damage as well as the use of three different construction
 materials \textit{ice}, \textit{wood} and \textit{stone} each one with different
@@
 % What is the problem?
+Procedural content generation provides a peculir case of study because of the way
+content has to be made for a each particular type of game, in this particular case 
+the restrictions that the game and the competition track have provide an interesting 
+challenge for a evolutionary algorithm because we have to tanke into account the 
+different pieces that can be used, their interactions with one another because of 
+gravity and the possible effects the trajectory of a shot from a player can affect 
+all of this.
+
 % How we solve it? (summary)   
+In order to tackle this case of study we proposed to use a genetic algorithm capable 
+of creating content, more specifically levels for the angry birds video game in which
+the generated levels satisfy the objectives of being \textit{interesting} and 
+\textit{playable}.
+
 % What is learned?
+After concluding this paper we expect to identify the places were a evolutionary 
+algorithm can be used alongside procedural content generation applied to video games
+in order to be able to clarify in which areas a evolutionary algorithm can used 
+to further improve video game development cycles.
 
-In Section 2, a background of the subjects used on this project will be
-presented, this subjects, while not all being used on by different authors on
-their works provide a great help on the development of the proposed system,
-% Jaime, remember there is no Background need it in this type of paper 
-% Maybe that will be the introduction - MG
-
-Section 3, contains a quick overview of some aspects used by different authors
-in order to tackle this problem, their design and basic functionality, in
-Section 4 the description of the current state of the project is explained, from
-the basis of the development to the diferent menthods that have been used to
-progress on the different sections of the project, 
-% Normaly there is no "Future Work" section is put together with Conclusions - MG
-in Section 5 we explain the
-future work of the project, where we are in the development phase and how the
-future implementations are to further improve the project and finally, in
-Section 6 we present our conclusions
-
-\section{Background}
-
-In this Section we provide a quick overview of the literature about the areas
-that provide the basis to the development of the current project, this section
-is divided in three parts, the fisrt one gives us an explanation of what
-procedural content generation entails, the second one provides an explanation on
-genetic algorithms and how can they be used to solve optimization problems, and
-finally, the third one provides us with an overview of Open-Ended Evolution and
-% use just one form, I prefer with no first caps open-ended evolution and let's 
-% use an abbreviation OEE - MG
-
-what it means to have an Open-Ended Evolutionary algorithm.
-% For this conference I think we do not need to define PCG, let's think 
-% every one knows what it is. - MG
-
-\subsection{Procedural content generation}
-
-Procedural content generation (PCG) denotes the way to automatically generate
+As mentioned above in this paper we use procedural content generation (PCG) 
+which denotes the way to automatically generate
 content by algorithms instead of generating the same content by manual means
@@
 
-\subsection{Genetic algorithm}
-Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic
+Furthermore we use genetic algorithms which is a method developed by 
+John Holland on 1975 \cite{Holland1975} the genetic
 algorithm (GA) is an optimization and search technique based on the principles
@@
 doing genetic operations as selection, crossover and mutation on each member of
-the population in order to generate the members of the population for the next
+the population in order to generate children for the next
 generation that would be closer to the best solution of the problem than their
@@
 
-% This section and the proposed approach should be in the fron lines - MG
-
-% The problem is that we just state what it is, but we do not link it
-% with our work. Why is important? What inpired our work? 
-% There is also Novelty Search - MG
-% Also it sounds like a copy-paste from Wikipedia please check and reference
-% accordingly - MG
-
-\subsection{Open-Ended Evolution}\label{AA}
-Open-ended evolution (OEE) is a variant of genetic evolution algorithm in which
+And finally we use our own interpretation of an Open-ended evolution (OEE) 
+algorithm which is a variant of genetic evolution algorithm where
 the objective differs from the regular genetic algorithm one, in this case the
@@
 number by the more complex the entities become.
+
+%In Section 2, a background of the subjects used on this project will be
+%presented, this subjects, while not all being used on by different authors on
+%their works provide a great help on the development of the proposed system,
+% Jaime, remember there is no Background need it in this type of paper 
+% Maybe that will be the introduction - MG
+
+Section 2, contains a quick overview of some aspects used by different authors
+in order to tackle this problem, their design and basic functionality, in
+Section 3 the description of the current state of the project is explained, from
+the basis of the development, modification to the original proposed method as 
+well as different approaches that were taken to solve the problem.
+% to the different methods that have been used to
+%progress on the different sections of the project, 
+% Normaly there is no "Future Work" section is put together with Conclusions - MG
+finally in Section 4 we provide our conclusions about the development of this
+paper as well as improvements that can help to refine the proposed work.
+
+%we explain the future work of the project, where we are in the development phase and how the
+%future implementations are to further improve the project and finally, in
+%Section 6 we present our conclusions
+
+%\section{Background}
+%
+%In this Section we provide a quick overview of the literature about the areas
+%that provide the basis to the development of the current project, this section
+%is divided in three parts, the fisrt one gives us an explanation of what
+%procedural content generation entails, the second one provides an explanation on
+%genetic algorithms and how can they be used to solve optimization problems, and
+%finally, the third one provides us with an overview of open-ended evolution and
+% use just one form, I prefer with no first caps open-ended evolution and let's 
+% use an abbreviation OEE - MG
+
+%what it means to have an open-ended evolution algorithm.
+% For this conference I think we do not need to define PCG, let's think 
+% every one knows what it is. - MG
+
+%\subsection{Procedural content generation}
+
+%Procedural content generation (PCG)
+
+%\subsection{Genetic algorithm}
+
+% This section and the proposed approach should be in the fron lines - MG
+
+% The problem is that we just state what it is, but we do not link it
+% with our work. Why is important? What inpired our work? 
+% There is also Novelty Search - MG
+% Also it sounds like a copy-paste from Wikipedia please check and reference
+% accordingly - MG
+
+%\subsection{Open-Ended Evolution}\label{AA}
 
@@
 
+%                                                                           /|\
+% Combined a few other things to give a litte more detail to this sections   |
+%                                                                           \|/
+
 \begin{enumerate}
@@
 generate the levels of the game in a limited amount of time, the infornmation on
-the configuration file is first the number of \textbf{\textit{diferent}} levels
-that must be generated, the second value is the diferent materials \textit{not
+the configuration file is first the number of \textbf{\textit{different}} levels
+that must be generated, the second value is the different materials \textit{not
 allowed} to be used, for instance a group of generated levels must not have
@@
     strategize how to use the provided birds to solve the level, the survey must
-    be applied to a equal quantity of people of three diferent game skill
+    be applied to a equal quantity of people of three different game skill
     levels,\textit{"non video game players"}, \textit{"casual video game

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to article 15/5/2019 00:45
Update to article 15/5/2019 01:23

@@
 
-\title{Procedural generation of levels fot he angry birds videogame using
+\title{Procedural generation of levels for the angry birds videogame using
 evolutionary computation\\
@@
 This project consisted in the generation of an evolutionary computation-based
-system capable of generate and evolve the structures of which one level of the
+system capable to generate and evolve the structures of which one level of the
 Angry Birds game is composed, these structures are evaluated according to the
@@
 
-The evolutionary computation system as the main objective of generating
+The evolutionary computation system has the main objective of generating
 structures based on the existent pieces of the game and evolving said pieces by
@@
 Procedural content generation is an interesting subject on the entertainment
-industry, primarily in the video game development because of the easines and
+industry, primarily in the video game development because of the easiness and
 quickness provided to generate content for different video game projects [ref] .
@@
 For this project a procedural generation content system is proposed for the game
-angry birds, angry birds is a game developed by Rovio Entrtainment in which the
+angry birds, angry birds is a game developed by Rovio Entertainment in which the
 objective is to destroy structures placed on the map as well as eliminating
@@
 to reduce the development cycles, and the productions cost. PCG as six focus
-areas listed below
-
-PCG as six focus areas listed as follows:
+areas listed below:
 % Jaime, you must add references to EVERY THING READ alsewhere : 
@@
     \item Visuals: This area is focused on creating or improving visual
-    representations of objects on games such as giving raw designs of players
-    faces of improving the images of other graphics.
+    representations of objects on games, such as giving raw designs of players
+    faces or improving the images of other graphics.
     \item Narrative: This aspect is focused on the generation of readable and
@@
 the population in order to generate children for the next
-generation that would be closer to the best solution of the problem than their
-parents, the cycles in this method where the operations are made are called
-generations and by moving over this the population “evolves” o in other words,
+generation that would be closer to the best solution of the problem, 
+the cycles in this method where the operations are made are called
+generations and by moving over this the population “evolves” or in other words,
 they get closer to the best possible solution  to a specific problem.
@@
 
-The main life cycle of a genetic algorithm shown of figure \ref{algorithm_model}
+The main life cycle of a genetic algorithm shown on figure \ref{algorithm_model}
 is described as follows:
@@
 For this project OEE is defined simply has a process of genetic evolution that
-encapsulates a group of similar processes and that is able to increase their
-number by the more complex the entities become.
+encapsulates a group of similar processes and that is able to increase complexity
+ of the original entities.
+
+% I tried to mix the two sections together while expanding the first part of 
+% the introduction JS
 
@@
 Y. Jiang et al. \cite{Jiang2017} proposed the use of predefined letter style
-patterns and combined the to create a small pool of word used to be combined in
+patterns and combined to create a small pool of words and letters used to be combined in
 order to create levels with text on them, the participants would play the game
-and after that they would be asked if they liked the layout of the levels
+and after that they would be asked if they liked the layout of the levels.
 
@@
 
-In this Section we describe the first approach that was used for this project, the
-game contains a total of 11 pieces as shown on figure \ref{piece_list} that
+In this Section we describe the approaches that were used for this project, first 
+explaining some information of how techniques like OOE were implemented with the paper.
+
+The game contains a total of 11 pieces as shown on figure \ref{piece_list} that
 cannot be modified, it is not possible to add more or modify the existing ones,
@@
 measured, an imaginary bounding box is defined by calculating the lengths of all
-the pieces, finding the borders of said pieces and then find the points that could
+the pieces, finding the borders of said pieces and then finding the points that could
 define a box around all of them, then use this defined box to calculate the 
@@
 \begin{enumerate}
-\item Gnerate composited to add to the pool of options
-\item Generate the first generation of the population
-\item Run a Simulation
-\item Evaluate each member of the population
+\item Gnerate composited to add to the pool of options.
+\item Generate the first generation of the population.
+\item Run a Simulation.
+\item Evaluate each member of the population.
 \item If a member of the population has remaining pieces obtain the location and
-angle of the pieces, create a composite and add it to the pool
-\item Select the parents for the next generation
-\item Do the crossover and mutation operations
-\item Repeat the cycle
+angle of the pieces, create a composite and add it to the pool.
+\item Select the parents for the next generation.
+\item Do the crossover and mutation operations.
+\item Repeat the cycle.
 \end{enumerate}
@@
 specify that a configuration file must be used to
-generate the levels of the game in a limited amount of time, the infornmation on
+generate the levels of the game in a limited amount of time, the information on
 the configuration file is first the number of \textbf{\textit{different}} levels
@@
 allowed} to be used, for instance a group of generated levels must not have
-circles which composition material is ice or stone moreover it des not have to
+circles which composition material is ice or stone moreover it does not have to
 integrate a triangle piece with ice, stone or wood material so this combinations
@@
 
-After taking into account this restrictions the strcture of our current approach
-had to be changed, so this section will be divided in tow subsections, the first
-will explain the approach that was used and after that second will explain the
+After taking into account this restrictions the structure of our current approach
+had to be changed, so this section will be divided in two subsections, the first
+will explain the approach that was used and after that the second will explain the
 modifications that had to be made in order to integrate the configuration files
@@
 pool of pieces, the numbers for this elements are assigned in a first come first
-served basis, the numbers are infinitely incremented and this same pieces can be
-repeated on each individual of the population
+served basis, the numbers are infinitely incremented and the same pieces can be
+repeated on each individual of the population.
 
@@
 points so before the simulation starts each of them are viable candidates to be
-a elite member of the population regardless relative height or complexity, then
+an elite member of the population regardless relative height or complexity, then
 the remaining of the process is separated in three phases has follows.
@@
 than a certain threshold half the percentage for one piece is removed from the
-remaining percentage, after this using the formula 2 the position of the piece
-is further checked this time by the difference in angle from the original one,
+remaining percentage, after this using formula 2 the position of the piece
+is further checked, this time by the difference in angle from the original one,
 in case the difference of angles is more than a certain threshold half a piece
@@
             0 & if $ -5 \le r \le 5 $, \\
-            \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 or r > 5 $.
+            \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
             \IEEEstrut
@@
 this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
-guideline used while creating imagen in which the purpose is to create
+guideline used while creating images, the purpose is to create
 aesthetical pleasant images where the focus point or the most important area is
@@
 rule different distribution groups or masks are created has shown on figure
-\ref{rule_of_thirds_applied} in order to use them before the simulation of an
-individual takes place in order to distribute the pieces in a way that can cover
+\ref{rule_of_thirds_masks} in order to use them before the simulation of an
+individual by placing the pieces in order to distribute them in a way that can cover
 more area and create more balanced levels instead of using a tower like
@@
     \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
-    \caption{Rule of thirds applied to an individual.}
+    \caption{Masks created using the rule of thirds.}
     \label{rule_of_thirds_masks}
@@
 that the amount of pieces will not be able to cover the full area given, so in
-order to prevent this kind of problems we also proposed to give each mask a
+order to prevent this kind of problem we also proposed to give each mask a
 value that refers to the minimum amount of pieces and height required to fill
-the most of the mask then check the amount of pieces and height before
+the most of the mask, then check the amount of pieces and height before
 simulation for a single individual and then randomize which mask of the ones
@@
 on figure \ref{rule_of_thirds_result} are obtained, this however gave us a new
-problem because as shown in the image and the previous image as well the were
+problem because as shown in the figure and on figure \ref{rule_of_thirds_applied} as well, the were
 instances in which a certain combination of pieces could be to big for the area
@@
 which cold provoke the entire structure and immeadiately nearby others to fall
-at the beginning of the simulation however it was able to
+at the beginning of the simulation however this allowed us to realize that predefined 
+composites could provide problems to the generated structures therefore this approach 
+was not the best for this problem.
 
@@
 
-The first differece that the new approach as is that the masks that are assigned
+The first differece that the new approach has is that the masks that are assigned
 to each individual are no longer pre-generated ones, this is because we decided
@@
 amount of pieces in each one is random, however the total of assigned pieces in
-all columns must be the same as the total pieces alloweed in each individual
-which is a number assigned at before beginning the system, an example of this
+all columns must be the same as the total pieces allowed in each individual
+which is a number assigned before beginning the system, an example of this
 can be seen in figure \ref{new_chrom} where the total of pieces in a individual
@@
 
-The competition also requires that a generator gives a set output a file is used
-to simulate the ruleset provided at a competition, this \textit{text file
+The competition also requires that a generator follows a certain ruleset this is 
+emulated by providing a file to the system to simulate the ruleset provided at the 
+competition, this \textit{text file
 (parameters.txt)} provides the specifications that must be met in the
@@
 \begin{itemize}
-    \item Total required levels
+    \item Total required levels.
     \item Restrictions to pieces or piece-material combinations that cannot be
     placed or used in the levels, in this case if the file specifies that a
-    \textit{CIRCLE} made out of \textit{ICE} cannotplaced the system must be
+    \textit{CIRCLE} made out of \textit{ICE} cannot be placed, so the system must be
     able to verify that said combination is not used.
@@
 \begin{itemize}
-    \item Element layer: also known as pieces layer, this layer represent the
+    \item Element layer: also known as pieces layer, this layer represents the
     elements assigned to a particular individual by an array of numbers from 0
-    to infinite where each number represents a reference to the class of a piece
+    to infinite, where each number represents a reference to the class of a piece
     in the selection pool including the ones generated by the OOE algorithm, the
@@
     \item Enemy layer: also known as pig layer, this layer is represented by two
-    elments a single numeric value representing the total amount of pigs
+    elements a single numeric value representing the total amount of pigs
     assigned to the level and an array of locations for the placement of this
@@
 better fitness than one that uses all of them. An example of this two crossover
-thypes cna be seen in figure \ref{crossover} in which the mask of an individual
+types can be seen in figure \ref{crossover} in which the mask of an individual
 is combined with another and the resulting mask for the childs have different
@@
     distance} is that it is a calculation applied to a pair of strings where the
-    obecive is to find the minimum required number of substitutions required in
+    objective is to find the minimum required number of substitutions required in
     order to convert a string exactly the same as the other, its formula is
     shown in equation \ref{hamming_distance}, since the formula itself locates
-    the minimum required number of substitutions then we compare the individual
-    with the rest of the population trying to found the maximum number of
+    the minimum number of substitutions then we compare the individual
+    with the rest of the population trying to find the maximum number of
     substitutions required efectively using the formula to give a better fitness

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5/2019 12:06

@@
 % is presented or In this paper we present a .... (in third or first person plural) - MG   
-This project consisted in the generation of an evolutionary computation-based
-system capable to generate and evolve the structures of which one level of the
-Angry Birds game is composed, these structures are evaluated according to the
-stability of the structure as well as for the complexity of said structure.
-% This is not true any more. Also the evaluation of the level is not the most
-% important aspect - MG
-
-For this a level generation system was designed based on the data obtained from
-the game, said data consist in the number and type of pieces that appear and the
-applied gravity of the game, the individuals of the group are evaluated by a
-simulation of the generated level and then checking how the structures are
-affected by the gravity of the game.  % This is not what the systems does any more
-% It seems like you are describing Laura's work - M
-
-The evolutionary computation system has the main objective of generating
-structures based on the existent pieces of the game and evolving said pieces by
-combining them in a process that simulates the rules of the Open-Ended Evolution
-algorithm in which the evolution of this compounds is not inclined towards a
-numeric objective rather than to extend the diversity from which the pieces may
-be selected for a level.
+In this paper an evolutionary computation-based system is proposed to generate 
+levels for the angry birds video game, the levels themselves are composed of a 
+set of birds that the player can use, a set amount of pigs that must be destroyed 
+in order to progress to the next level and a given number of pieces that conform 
+structures that may or may not protect the pigs from the player, this level 
+generation system can create composites of pieces in order to create structures 
+that can be used in the game this is based on our own interpretation of a open-ended 
+evolutionary algorithm in which the evolution of the elements is not guided towards 
+a single objective but rather is free to evolve and generate novelty or diversity 
+in this case diversity of structures which the system can later select composites 
+from in order to decide what will confomr a level, this data is saved in groups that represent a population 
+that can evolve by an evolutionary algorithm in order to create more complex levels.
+ This elements of a population are then evaluated by how complex they become and how 
+ different they are from the rest of the group in order to create a variety of possible 
+ levels to be played.
 
@@
 raw images and designs used by other personnel to improve it and use it in order
-to reduce the development cycles, and the productions cost. PCG as six focus
-areas listed below:
-% Jaime, you must add references to EVERY THING READ alsewhere : 
-% We do not proposed this list, please add a reference. - MG
-
-\begin{itemize}
-    \item Level Design: This aspect involves only the design of specific
-    sections of a game, primarily those in which the player is able to interact.
-    \item Audio: This aspect is focused on designing soundtracks that are able
-    to react to a player specific action.
-    \item Visuals: This area is focused on creating or improving visual
-    representations of objects on games, such as giving raw designs of players
-    faces or improving the images of other graphics.
-    \item Narrative: This aspect is focused on the generation of readable and
-    coherent stories or plotlines of games.
-    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
-    which a game is based by trying to play as a human would in order to improve
-    said mechanics.
-    \item Game Design: This aspect is focused on generating the rulesets and 
-    mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
-    % The references are in this last item of the list JS
-\end{itemize}
-
-Furthermore we use genetic algorithms which is a method developed by 
-John Holland on 1975 \cite{Holland1975} the genetic
-algorithm (GA) is an optimization and search technique based on the principles
-of genetic and natural selection, it allows a population composed of many
-individuals, which by themselves represent a possible solution to the problem,
-to evolve under specific selection rules in order to obtain the maximum fitness.
-
-In other words a genetic algorithm is a method to solve optimization problems by
-creating a population that will represent a possible solution and repeatedly
-doing genetic operations as selection, crossover and mutation on each member of
-the population in order to generate children for the next
-generation that would be closer to the best solution of the problem, 
-the cycles in this method where the operations are made are called
-generations and by moving over this the population “evolves” or in other words,
-they get closer to the best possible solution  to a specific problem.
-
-\begin{figure}[htbp]
-    \centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
-    \caption{Life cycle of a genetic algorithm.}
-    \label{algorithm_model}
-\end{figure}
-
-% Maybe this is well known, again our implementation is what we need to describe 
-% JJ, what you think?
-
-The main life cycle of a genetic algorithm shown on figure \ref{algorithm_model}
-is described as follows:
-\begin{enumerate}
-    \item Initialize a random n population of values suitable for the solution.
-    \item Evaluate the fitness of each individual (solution) in the population.
-    \item Check if the stopping criteria has been met.
-    \item If not.
-    \begin{enumerate}
-        \item Introduce new individuals to the population by crossover
-        operations.
-        \item Mutate a random value of the new individuals.
-        \item Select new cross over individuals according to their fitness for
-        the next generation.
-    \end{enumerate}
-    \item Loop from step 2 until an end condition is satisfied.
-    \item Select the best individual of the population as the solution for the
-    problem
-\end{enumerate}
+to reduce the development cycles, and the productions cost. 
+PCG as various focus areas that resolve around a video game, however in this paper 
+the main focus is the \textit{Level design} area which as the objective to design 
+the different areas of a game in wich a player can interact with, since in the 
+angry birds video game a level is represented by a scene then the system will 
+have to create the entities (birds and pigs) and objects (pieces) in it in order 
+to create a playable level.
 

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5/2019 12:07
Update to inidividual representation (end of document)  14/5/2019 12:51

@@
 the main focus is the \textit{Level design} area which as the objective to design 
-the different areas of a game in wich a player can interact with, since in the 
+the different areas of a game in which a player can interact with, since in the 
 angry birds video game a level is represented by a scene then the system will 
@@
 
+Finally figure \ref{layer12_combine} and figure \ref{layer123_combine} represent 
+the way all the layers of an individual al combined to create a level after all 
+the selection, combination and mutation operations, first in figure \ref{layer12_combine}
+the composites layer is obtained from an individual, by a background process the 
+width and height of all composites are obtained, then using the mask from the same 
+individual the composites are placed in the order they are in their respective list 
+(left to right in the level) in case a mask is not able to accommodate all the 
+composites the remaining ones are not placed nor taken into account on the evaluation 
+process, in the opposite case that there are not enough composites to fill a mask 
+then the remaining areas are not taken into account as well, then in figure \ref{layer123_combine} 
+the previous combination of layers is evaluated by cheking which placed composites 
+can hold a pig in the center or on the top of it, then the pigs are placed in the 
+same oreder the composites are placed (left to right) in the locations where one 
+is able to be placed.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/layer12_combine.png}}
+    \caption{Combination of composites layer and mask layer.}
+    \label{layer12_combine}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=80mm]{Images/layer123_combine.png}}
+    \caption{Combination of figure \ref{layer12_combine} layers with pig layer.}
+    \label{layer123_combine}
+\end{figure}
+
 Using all this configurations the system is capable of creating levels, some of

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
abstract

@@
 In this paper an evolutionary computation-based system is proposed to generate 
-levels for the angry birds video game, the levels themselves are composed of a 
-set of birds that the player can use, a set amount of pigs that must be destroyed 
+levels for the Angry Birds video game, the levels themselves are composed of a 
+set of birds that the player can use, a certain amount of pigs that must be destroyed 
 in order to progress to the next level and a given number of pieces that conform 
-structures that may or may not protect the pigs from the player, this level 
-generation system can create composites of pieces in order to create structures 
-that can be used in the game this is based on our own interpretation of a open-ended 
-evolutionary algorithm in which the evolution of the elements is not guided towards 
-a single objective but rather is free to evolve and generate novelty or diversity 
-in this case diversity of structures which the system can later select composites 
-from in order to decide what will confomr a level, this data is saved in groups that represent a population 
-that can evolve by an evolutionary algorithm in order to create more complex levels.
- This elements of a population are then evaluated by how complex they become and how 
- different they are from the rest of the group in order to create a variety of possible 
- levels to be played.
+structures that may or may not protect the pigs from the player. The focus in this stage
+is the generation of diverse structures that can be played in the game having the
+additional characteristics of being interesting and playable. We propose a 
+multi-layered search, first contructing composite structures from basic components, to then
+build more complex structures building from these components, following an open-ended 
+evolution approach; in which the evolution of structures is not guided towards 
+a single objective but rather is free to evolve and generate novelty or diversity. 
+The objective is then that the proposed levels are evaluated by how complex they become and how 
+different they are from the rest of the group.
+%The experiments conducted show  
+% We found that in the experiments conducted, levels generated where ...
 
@@
 % What is learned?
-After concluding this paper we expect to identify the places were a evolutionary 
-algorithm can be used alongside procedural content generation applied to video games
-in order to be able to clarify in which areas a evolutionary algorithm can used 
-to further improve video game development cycles.
+%We identify the places were an evolutionary algorithm can be used alongside
+%procedural content generation applied to video games in order to be able to
+%clarify in which areas an evolutionary algorithm can used to further improve
+%video game development cycles.
+
+% En este trabajo se generan estructuras con mayor diversidad y por lo tanto 
+% resultan ser interesantes.
 

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Introduction edited

@@
 Procedural content generation is an interesting subject on the entertainment
-industry, primarily in the video game development because of the easiness and
-quickness provided to generate content for different video game projects [ref] .
+industry, primarily in video game development because of the savings in 
+time and human resources when generating content for different video game projects.
 In this paper an evolutionary content generation system is proposed to generate
-levels for the popular Angry Birds video game
-\cite{RovioEntertainmentCorporation2009}, taking inspiration in concepts of
-open-ended evolution.
-
-For this project a procedural generation content system is proposed for the game
-angry birds, angry birds is a game developed by Rovio Entertainment in which the
-objective is to destroy structures placed on the map as well as eliminating
+levels for the popular Angry Birds video game \cite{RovioEntertainmentCorporation2009},
+taking inspiration in concepts of open-ended evolution. Angry birds is a game 
+developed by Rovio Entertainment in which the objective is to destroy structures
+placed on the map as well as eliminating
 green pig-like entities in order to obtain the highest score possible, the game
@@
 destroyed by means of damage as well as the use of three different construction
-materials \textit{ice}, \textit{wood} and \textit{stone} each one with different
-resistances ranging from fragile, normal and sturdy in that order, the game
+materials \textit{ice}, \textit{wood} and \textit{stone} each one with a different
+resistance, ranging from fragile, normal and sturdy in that order. The game
 mechanic is to use a slingshot to shoot a certain number of birds with different
-abilities to destroy the structures and the objectives, it is possible to obtain
-a high score by doing the most destruction as possible with the least birds as
-you can. \cite{RovioEntertainmentCorporation2009}
+abilities, to destroy both the structures and the objectives. A high score 
+is achived by doing the most destruction with the least birds possible 
+\cite{RovioEntertainmentCorporation2009}.
 
-While it is possible to create a evolutionary agent to play the levels and
-obtain the best score the main objective of this project is to generate the
-levels that can be played by naive agents or physical players, the levels
+%While it is possible to create an evolutionary agent to play the levels and
+%obtain the best score 
+The main objective of this project is to generate levels that can be played
+by naïve or inteligent agents as well as physical players. The levels
 themselves need to be complex in the sense that interesting structures can be
-created but it has to be possible to complete in some way
+created, but at the same time, it is possible to complete in some way
 \cite{Stephenson,Stephenson2018}.
@@
 % What is the problem?
-Procedural content generation provides a peculir case of study because of the way
-content has to be made for a each particular type of game, in this particular case 
-the restrictions that the game and the competition track have provide an interesting 
-challenge for a evolutionary algorithm because we have to tanke into account the 
-different pieces that can be used, their interactions with one another because of 
-gravity and the possible effects the trajectory of a shot from a player can affect 
-all of this.
-
+Procedural content generation provides a peculiar case of study because of the way
+% Is there a reference? - MG
+content has to be made for a each particular type of game. In this use case 
+we have those restrictions dictated by the game, and also 
+those imposed by a competition track \cite{Renz}.% Reference the paper of the competition  have provide an interesting 
+The challenge for the participating algorithms is to be flexible on the  
+pieces that can be used and the runing time of the algorithm, as they are determined at runtime. 
+%their interactions with one another because of 
+%gravity and the possible effects the trajectory of a shot from a player can affect 
+%all of this.
 % How we solve it? (summary)   
-In order to tackle this case of study we proposed to use a genetic algorithm capable 
-of creating content, more specifically levels for the angry birds video game in which
-the generated levels satisfy the objectives of being \textit{interesting} and 
+In order to tackle this case study, we proposed the use a genetic algorithm capable 
+of creating game levels having the objective of being both \textit{interesting} and 
 \textit{playable}.
@@
 
-As mentioned above in this paper we use procedural content generation (PCG) 
-which denotes the way to automatically generate
-content by algorithms instead of generating the same content by manual means
-such as with different personnel.
+% Not important - MG
+%As mentioned above in this paper we use procedural content generation (PCG) 
+%which denotes the way to automatically generate
+%content by algorithms instead of generating the same content by manual means
+%such as with different personnel.
 
-In the videogame industry many developers use a PCG style software that produces
-raw images and designs used by other personnel to improve it and use it in order
-to reduce the development cycles, and the productions cost. 
-PCG as various focus areas that resolve around a video game, however in this paper 
-the main focus is the \textit{Level design} area which as the objective to design 
-the different areas of a game in which a player can interact with, since in the 
-angry birds video game a level is represented by a scene then the system will 
-have to create the entities (birds and pigs) and objects (pieces) in it in order 
-to create a playable level.
+%In the videogame industry many developers use a PCG style software that produces
+%raw images and designs used by other personnel to improve it and use it in order
+%to reduce the development cycles, and the productions cost. 
+%PCG as various focus areas that resolve around a video game, however in this paper 
+%the main focus is the \textit{Level design} area which as the objective to design 
+%the different areas of a game in which a player can interact with, since in the 
+%angry birds video game a level is represented by a scene then the system will 
+%have to create the entities (birds and pigs) and objects (pieces) in it in order 
+%to create a playable level.
 
-And finally we use our own interpretation of an Open-ended evolution (OEE) 
-algorithm which is a variant of genetic evolution algorithm where
-the objective differs from the regular genetic algorithm one, in this case the
-final objective is not to reach a final state of the evolution but to continue
-evolving and creating new types of entities more complex on each new generation,
-these same entities have the possibility to evolve not only inside the frame of
-their type but create entirely new groups. \cite{Standish2003}
-
-Another explanation provided by T. Taylor et al. \cite{Taylor2016,Taylor}
-defines OEE has a system capable of creating novelty beyond a point where
+We propose a basic Open-Ended Evolution (OEE) algorithm, a variant of genetic evolution algorithm where
+the objective differs from that of a regular genetic algorithm,  in this case the
+final objective is not to reach a final state of the evolution (an optimal solution) but to continue
+evolving and creating new types of entities, perhaps more complex on each new generation.
+Solutuion entities have the possibility to evolve not only inside the frame of
+their type, but  they can create entirely new groups \cite{Standish2003}. T. Taylor et al. \cite{Taylor2016,Taylor}
+defines OEE as a system capable of creating novelty beyond a point where
 nothing changes on the current group of interest rather than just converging to
@@
 
-For this project OEE is defined simply has a process of genetic evolution that
-encapsulates a group of similar processes and that is able to increase complexity
- of the original entities.
+For this project, OEE is defined simply as a genetic evolution process with
+different clasess of objects, with compositional and taxonomic relationships between them.
+Objects of each class can evolve in parallel or as in this case, independenly of each other.   
+The idea is based on the object oriented model, in which complex behavior can be model 
+using these principles.
 
@@
 Section 3 the description of the current state of the project is explained, from
+%% The following sentence is not clear.
 the basis of the development, modification to the original proposed method as 

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5 15:16

@@
 \and
-\IEEEauthorblockN{ Given Name Surname} \IEEEauthorblockA{\textit{dept. name of
-organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}}
+\IEEEauthorblockN{ JJ Merelo} \IEEEauthorblockA{\textit{Department of Graduate Studies} \\
+\textit{Universidad de Granada}\\
+Granada, Spain\\
+jmerelo@ugr.es}}
 
@@
 The objective is then that the proposed levels are evaluated by how complex they become and how 
-different they are from the rest of the group.
+different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
+to have a level of uniqueness because on most of the cases the way they are presented on screen
+is a way a normal human would have trouble to create but at the same time are interesting to see.
+% Maybe like this ? JSH
 %The experiments conducted show  
@@
 \textit{playable}.
+
+% What is learned?
+In this work we found that an evolutionary algorithm can be used to create 
+this type of content not only because it is able to create levels that are interesting 
+and diverse but because an evolutionary algorithm is capable of creating things a 
+normal human could have trouble imagining of.
 

### 2019-05-15 IEEE_ConferenceOnGames/article_english.tex
Update to article  14/5/2019 17:52

@@
 industry, primarily in video game development because of the savings in 
-time and human resources when generating content for different video game projects.
+time and human resources when generating content for different video game projects \cite{Yannakakis2017,YannakakisContentGeneration}.
 In this paper an evolutionary content generation system is proposed to generate
-levels for the popular Angry Birds video game \cite{RovioEntertainmentCorporation2009},
+levels for the popular Angry Birds video game,
 taking inspiration in concepts of open-ended evolution. Angry birds is a game 
@@
 % This sentence needs more work -MG
-Since the algorithm has to generate more complex structures the remaining pieces
-of a member of the population have to be used has a starting point, this new
+During the original phase of the design of the system, it was decided that the way 
+the composites were going to evolve was by first placing only base pieces on a level 
+then after a simulation the remaining pieces
+of a member of the population were going to be used has a new composite if after a 
+simulation a group was still standing and grouped on a single point, their individual 
+offsets from the center of the group was calculated and then using this information a new 
+composite could be added to the pool of options, this new
 % we don't use member of the populations, use proposed solution, candidate solution
 % or individual of the population. - MG  
-
-additions to the piece pool are added to the population by the mutation
-operation, the objective in the first phase of the project is to generate
-structures that are capable of maintaining their own balance as shown on figure
+additions to the composite pool could then be added to the population by the mutation
+operation when a new member of the population was being created, the objective 
+in this first phase of the project was to generate
+structures that were capable of maintaining their own balance as shown on figure
 \ref{test_old}, since the objective of open-ended evolution for this project is
-to add new composites to the pool of options the algorithm will first run a
+to add new composites to the pool of options, then the algorithm will first run a
 simulation with a group of pieces and after it the ones that were not destroyed
@@
 
-The way to represent the elements of a member of the population is by using the
-id of each piece and the new added ones has a pointer to the respective data
+Since there has to be a way to represent the struccture of a level in a a way that
+both the algorithm as well as the game are able to interpret it \cite{togelius2016Representationsforsearch-basedmethods}, 
+then the way to represent the elements of a member of the population in thos work 
+is by using the id of each piece and the new added ones has a pointer to the respective data
 that needs to be obtained, this way and individual can be represented as shown

### 2019-05-15 IEEE_ConferenceOnGames/article_english.tex
soa

--- 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
@@
 % What is the problem?
-Procedural content generation provides a peculiar case of study because of the way
+Procedural content generation provides a peculiar case of study because of the
+way
 % Is there a reference? - MG
-content has to be made for a each particular type of game. In this use case 
-we have those restrictions dictated by the game, and also 
-those imposed by a competition track \cite{Renz}.% Reference the paper of the competition  have provide an interesting 
-The challenge for the participating algorithms is to be flexible on the  
-pieces that can be used and the runing time of the algorithm, as they are determined at runtime. 
-%their interactions with one another because of 
-%gravity and the possible effects the trajectory of a shot from a player can affect 
-%all of this.
-% How we solve it? (summary)   
-In order to tackle this case study, we proposed the use a genetic algorithm capable 
-of creating game levels having the objective of being both \textit{interesting} and 
-\textit{playable}.
+content has to be made for a each particular type of game. In this use case we
+have those restrictions dictated by the game, and also those imposed by a
+competition track \cite{Renz}.% Reference the paper of the competition  have
+provide an interesting The challenge for the participating algorithms is to be
+flexible on the pieces that can be used and the runing time of the algorithm, as
+they are determined at runtime. 
+%their interactions with one another because of gravity and the possible effects
+%the trajectory of a shot from a player can affect all of this. How we solve it?
+%(summary)   
+In order to tackle this case study, we proposed the use a genetic algorithm
+capable of creating game levels having the objective of being both
+\textit{interesting} and \textit{playable}.
 
@@
 
-% Not important - MG
-%As mentioned above in this paper we use procedural content generation (PCG) 
-%which denotes the way to automatically generate
-%content by algorithms instead of generating the same content by manual means
-%such as with different personnel.
+We propose a basic Open-Ended Evolution (OEE) algorithm, a variant of genetic
+evolution algorithm where the objective differs from that of a regular genetic
+algorithm,  in this case the final objective is not to reach a final state of
+the evolution (an optimal solution) but to continue evolving and creating new
+types of entities, perhaps more complex on each new generation. Solutuion
+entities have the possibility to evolve not only inside the frame of their type,
+but  they can create entirely new groups \cite{Standish2003}. Taylor et al.
+\cite{Taylor2016,Taylor} defines OEE as a system capable of creating novelty
+beyond a point where nothing changes on the current group of interest rather
+than just converging to a stable or quasi-stable state.For this project, OEE is
+defined simply as a genetic evolution process with different clasess of objects,
+with compositional and taxonomic relationships between them. Objects of each
+class can evolve in parallel or as in this case, independenly of each other. The
+idea is based on the object oriented model, in which complex behavior can be
+model using these principles. The rest of the paper is as follows.
 
-%In the videogame industry many developers use a PCG style software that produces
-%raw images and designs used by other personnel to improve it and use it in order
-%to reduce the development cycles, and the productions cost. 
-%PCG as various focus areas that resolve around a video game, however in this paper 
-%the main focus is the \textit{Level design} area which as the objective to design 
-%the different areas of a game in which a player can interact with, since in the 
-%angry birds video game a level is represented by a scene then the system will 
-%have to create the entities (birds and pigs) and objects (pieces) in it in order 
-%to create a playable level.
-
-We propose a basic Open-Ended Evolution (OEE) algorithm, a variant of genetic evolution algorithm where
-the objective differs from that of a regular genetic algorithm,  in this case the
-final objective is not to reach a final state of the evolution (an optimal solution) but to continue
-evolving and creating new types of entities, perhaps more complex on each new generation.
-Solutuion entities have the possibility to evolve not only inside the frame of
-their type, but  they can create entirely new groups \cite{Standish2003}. T. Taylor et al. \cite{Taylor2016,Taylor}
-defines OEE as a system capable of creating novelty beyond a point where
-nothing changes on the current group of interest rather than just converging to
-a stable or quasi-stable state.
-
-For this project, OEE is defined simply as a genetic evolution process with
-different clasess of objects, with compositional and taxonomic relationships between them.
-Objects of each class can evolve in parallel or as in this case, independenly of each other.   
-The idea is based on the object oriented model, in which complex behavior can be model 
-using these principles.
-
-% I tried to mix the two sections together while expanding the first part of 
-% the introduction JS
-
-%In Section 2, a background of the subjects used on this project will be
-%presented, this subjects, while not all being used on by different authors on
-%their works provide a great help on the development of the proposed system,
-% Jaime, remember there is no Background need it in this type of paper 
-% Maybe that will be the introduction - MG
+%% TO DO: This needs to be adjusted to the final version. We need to use
+% \ref for the numbers - MG
 
@@
 
-\section{Overview of existing work}
-
-In this Section we present some of the different approaches to the procedural
-generation of content for the angry birds video game.
-
-M. Kaidan et al. \cite{Kaidan2015} propose a model in which the generation of
-content is controlled by the skill of a player while actively playing the game,
-the moment the player finishes a certain level the algorithm obtains the score
-and generates the next level to be played.
-
-J. Renz et al. \cite{Renz} created an article in which the angry birds level
-generation contest mechanics of the IEEE Conference on Computational
-Intelligence and Games are based on, it explains some of the solving methods
-proposed by previous competitors.
-
-Y. Jiang et al. \cite{Jiang2017} proposed the use of predefined letter style
-patterns and combined to create a small pool of words and letters used to be combined in
-order to create levels with text on them, the participants would play the game
-and after that they would be asked if they liked the layout of the levels.
+\section{State of the art}
+\label{SoA}
+In this Section we present PCG works relevant to the Level generation for the
+Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized an AI
+competition with the aim of developing intelligent agents that could play new
+Angry Birds levels better than the best human players. The competition was then
+collocated in other AI conferences. In order to train and test these agents,
+more novel and some times difficult levels must be generated. A related
+competition was then proposed by Stephenson et al. \cite{Stephenson} this time
+with the goal of developing a level generator for the game. Several generators
+have been proposed in the following years of competition. M. Kaidan et al.
+\cite{Kaidan2015} propose a model in which the generation of content is
+controlled by the skill of a player while actively playing the game, the moment
+the player finishes a certain level the algorithm obtains the score and
+generates the next level to be played. Y. Jiang et al. \cite{Jiang2017} proposed
+the use of predefined letter style patterns and combined to create a small pool
+of words and letters used to be combined in order to create levels with text on
+them, the participants would play the game and after that they would be asked if
+they liked the layout of the levels. A search based approach has been also used
+in several works, recently a
 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
new document
more approach

--- 2019-05-15 IEEE_ConferenceOnGames/article_english.tex
@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote.
-% If that is unneeded, please comment it out.
-\usepackage[style=ieee,backend=biber,style=numeric,sorting=none]{biblatex}
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor}
-\addbibresource{References/article_references.bib}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
     they liked the layout of the levels. A search based approach has been also used
-in several works, recently a
+    in several works. 
+    %%%
+    % TO DO: Laura´s work here 
+    %%%
 
-\section{Approach}
+    \section{Proposed Method}
 
-In this Section we describe the approaches that were used for this project, first 
-explaining some information of how techniques like OOE were implemented with the paper.
+    In this Section we describe the approach used in this work, explaining first,
+    the restrictions of the game.
+    The game contains a total of 11 block shapes as shown in Figure \ref{piece_list}.
+    These basic blocks cannot be modified, it is not possible to add more or modify the existing ones,
+    with this in mind the purpose is to create composites of these blocks in
+    different locations and angles in order to create structures that can be used as
+    building blocks for more complex structures.
 
-The game contains a total of 11 pieces as shown on figure \ref{piece_list} that
-cannot be modified, it is not possible to add more or modify the existing ones,
-with this in mind the purpose is to create composites of this same pieces in
-different locations and angles in order to create structures that can be used as
-building blocks for more complex levels.
+    Since there is no way to \textit{add} a new composite to the pool of blocks,
+    then a way to combine both is needed, in order to do this first the original
+    11 pieces of the game will be converted into composites of a single element.
+    A composite is defined as a lists of blocks, then a \textit{composite} of
+    one element will be created for each piece. Composites are the first layer
+    the building blocks for the structures to come. A composite could include
+    different types of blocks, rotaded at a certain angle and compose a basic
+    structure. An ideal composite could support other composites on top with out
+    falling apart, but this is not required. A composite is measured using
+    maginary bounding box, defined by calculating the lengths of all the pieces,
+    finding the borders of said pieces and then finding the points that could
+    define a box around all of them, then use this defined box to calculate the
+    height and width of the new composite and then calculate from the center
+    point of said box the offsets from the center of the group to the center of
+    each respective piece as shown on figure \ref{bounding_boc_calc}, this
+    information is needed in order to add it as a new composite so it can be
+    used to place the pieces in their respective new positions when the files
+    needed for the simulation are being created. This is similar to creating a
+    group of elements in a drawing application.
 
-Since there is no way to \textit{add} a composite to the pool of pieces of the 
-game then a way to combine both groups is needed, in order to do this first the 
-original 11 pieces of the game will be converted into composites, since the easiest
-way to read the data to create composites is by using lists then a \textit{composite} 
-of one element will be created for each piece, after this in order to add a 
-composite of pieces as a new component first a group of existing composites is 
-selected and placed in a imaginary enviroment then as a unique group they are 
-measured, an imaginary bounding box is defined by calculating the lengths of all
-the pieces, finding the borders of said pieces and then finding the points that could
-define a box around all of them, then use this defined box to calculate the 
-height and width of the new composite and then calculate from 
-the center point of said box the offsets from the center of the
-group to the center of each respective piece as shown on figure
-\ref{bounding_boc_calc}, this information is needed in order to add it as a new
-composite so it can be used to place the pieces in their respective new positions
-when the files needed for the simulation are being created.
+    %% 
+    Good composites can be found using an evolutionary approach proposed earlier 
+    by Calle and Merelo, where basic structures are generated by searching a space
+    of falling blocks and selecting those that remain standing. This algorithm is 
+    not capable of creating complex strucures, but it can generate very novel basic
+    structures. We can see that the evolution at this level can benefit from having
+    more freedom in how basic structures are built. We do not want to form piles
+    or sequences of blocks, this will be done at a higher level in the composite hirarchy.
 
-So using the composite generator the order of this sequence of
-events needs to be done as follows:
+    At his level the composite generator has the following steps, for more details refer to the paper:
 
@@
     \begin{enumerate}
-\item Gnerate composited to add to the pool of options.
-\item Generate the first generation of the population.
+    \item Generate the first generation of the population, consisting of randomly generated list of blocks.
     \item Run a Simulation.
-\item Evaluate each member of the population.
+    \item Evaluate each individual of the population.
     \item If a member of the population has remaining pieces obtain the location and
-angle of the pieces, create a composite and add it to the pool.
-\item Select the parents for the next generation.
-\item Do the crossover and mutation operations.
+    angle of the pieces, assign a fitness.
+    \item Do the selection, crossover and mutation operations.
     \item Repeat the cycle.
+    \item From the best individuals select composites. Several algorithms could be proposed for this step, for instance selcting clusters of blocks.
     \end{enumerate}
+
+    Another option is to just manually generate interesting composites to be used by the algorithm.
+    We could say that the previous approach is an option for a procedural generation of composites.
 
@@
     to generate levels that are \textit{fun} and \textit{enjoyable} however they 
-also have to be challenging but imposible however the rules for the competition 
+    also have to be challenging but not imposible. However the rules for the competition 
     specify that a configuration file must be used to
@@
     allowed} to be used, for instance a group of generated levels must not have
-circles which composition material is ice or stone moreover it does not have to
+    circles which composition material is ice or stone, moreover it does not have to
     integrate a triangle piece with ice, stone or wood material so this combinations
@@
     % This sentence needs more work -MG
+
     During the original phase of the design of the system, it was decided that the way 
-the composites were going to evolve was by first placing only base pieces on a level 
+    composites were going to evolve was by first placing only base pieces on a level 
     then after a simulation the remaining pieces
-of a member of the population were going to be used has a new composite if after a 
+    of a member of the population were going to be used as a new composite if after a 
     simulation a group was still standing and grouped on a single point, their individual 
@@
 
-Since there has to be a way to represent the struccture of a level in a a way that
+    Since there has to be a way to represent the structure of a level in a a way that
     both the algorithm as well as the game are able to interpret it \cite{togelius2016Representationsforsearch-basedmethods}, 
@@
 
-\printbibliography
-\newrefcontext[sorting=ydnt]
+\bibliographystyle{IEEEtran}
+\bibliography{References/article_references.bib}
 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
first part of approach

@@
 
+    \subsection{Composite Generation}
+
     Since there is no way to \textit{add} a new composite to the pool of blocks,
@@
 
-    At his level the composite generator has the following steps, for more details refer to the paper:
+    At this level the composite generator has the following steps:
 
@@
     \begin{enumerate}
-    \item Generate the first generation of the population, consisting of randomly generated list of blocks.
+    \item Generate the first generation of the population, consisting of
+    randomly generated list of blocks.
     \item Run a Simulation.
     \item Evaluate each individual of the population.
-    \item If a member of the population has remaining pieces obtain the location and
-    angle of the pieces, assign a fitness.
+    \item If a member of the population has remaining pieces obtain the location
+    and angle of the pieces, assign a fitness.
     \item Do the selection, crossover and mutation operations.
     \item Repeat the cycle.
-    \item From the best individuals select composites. Several algorithms could be proposed for this step, for instance selcting clusters of blocks.
+    \item From the best individuals select composites. Several algorithms could
+    be proposed for this step, for instance selcting clusters of blocks.
     \end{enumerate}
@@
     generate the levels of the game in a limited amount of time, the information on
-    the configuration file is first the number of \textbf{\textit{different}} levels
+    the configuration file is first the number of \textit{different} levels
     that must be generated, the second value is the different materials \textit{not
@@
 
-    After taking into account this restrictions the structure of our current approach
-    had to be changed, so this section will be divided in two subsections, the first
-    will explain the approach that was used and after that the second will explain the
-    modifications that had to be made in order to integrate the configuration files
-    for the competition.
+    %After taking into account this restrictions the structure of our current approach
+    %had to be changed, so this section will be divided in two subsections, the first
+    %will explain the approach that was used and after that the second will explain the
+    %modifications that had to be made in order to integrate the configuration files
+    %for the competition.
 
-    \subsection{Original approach}
+    In our original approach, composites could added to the structure generator
+    algorithm at runtime as a mutation of an individual. The structure generator
+    is explained in the next section.
+
+    % Lets check this, I think is not needed. 
+    %The objective in this first phase of the project was to
+    %generate structures that were capable of maintaining their own balance as
+    %shown on figure \ref{test_old}, since the objective of open-ended evolution
+    %for this project is to add new composites to the pool of options,
+
+    In our current approach the composite generator is only
+    run once at the beginning, as a setup process.
+
+    \subsection{Structure Evolution}
     % This sentence needs more work -MG
 
-    During the original phase of the design of the system, it was decided that the way 
-    composites were going to evolve was by first placing only base pieces on a level 
-    then after a simulation the remaining pieces
-    of a member of the population were going to be used as a new composite if after a 
-    simulation a group was still standing and grouped on a single point, their individual 
-    offsets from the center of the group was calculated and then using this information a new 
-    composite could be added to the pool of options, this new
+    %During the original phase of the design of the system, it was decided that the way 
+    %composites were going to evolve was by first placing only base pieces on a level 
+    %then after a simulation the remaining pieces
+    %of a member of the population were going to be used as a new composite if after a 
+    %simulation a group was still standing and grouped on a single point, their individual 
+    %offsets from the center of the group was calculated and then using this information a new 
+    %composite could be added to the pool of options, this new
     % we don't use member of the populations, use proposed solution, candidate solution
     % or individual of the population. - MG  
-    additions to the composite pool could then be added to the population by the mutation
-    operation when a new member of the population was being created, the objective 
-    in this first phase of the project was to generate
-    structures that were capable of maintaining their own balance as shown on figure
-    \ref{test_old}, since the objective of open-ended evolution for this project is
-    to add new composites to the pool of options, then the algorithm will first run a
-    simulation with a group of pieces and after it the ones that were not destroyed
-    by falling because of gravity will be saved and added to the pool of options.
+    %additions to the composite pool could then be added to the population by the mutation
+    %operation when a new member of the population was being created, the objective 
+    %in this first phase of the project was to generate
+    %structures that were capable of maintaining their own balance as shown on figure
+    %\ref{test_old}, since the objective of open-ended evolution for this project is
+    %to add new composites to the pool of options, then the algorithm will first run a
+    %simulation with a group of pieces and after it the ones that were not destroyed
+    %by falling because of gravity will be saved and added to the pool of options.
 
@@
 
-    Since there has to be a way to represent the structure of a level in a a way that
-    both the algorithm as well as the game are able to interpret it \cite{togelius2016Representationsforsearch-basedmethods}, 
-    then the way to represent the elements of a member of the population in thos work 
-    is by using the id of each piece and the new added ones has a pointer to the respective data
-    that needs to be obtained, this way and individual can be represented as shown
-    on figure \ref{old_chrom} where each chromosome represents a certain item in the
-    pool of pieces, the numbers for this elements are assigned in a first come first
-    served basis, the numbers are infinitely incremented and the same pieces can be
-    repeated on each individual of the population.
+    Structures are the next evolutionary layer, at a higher level of composition.
+    Structures are compositions of composites. A level can be seen as a collection 
+    of structures and each structure is a pile of composite blocks. This approach 
+    was proposed by \cite{ }. This way of constructing levels has the advantage of
+    limiting the search space, to structures that have a better chance to be 
+    standing after the simulation ends. There is no warranty that piles of 
+    composite blocks will maintain balance, so again we must search for those 
+    structures.
+
+    Structures are represented in a way similar to Togelius et al.
+    \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
+    an id assigned to it. A structure is then a list of ids, refering to
+    composite blocks, the first 11 are basic composite and generated composites 
+    are assigned a higher number.  This way and individual can be
+    represented as shown on figure \ref{old_chrom} where each chromosome
+    represents a certain item in the list of blocks, the numbers for this
+    elements are assigned in a first come first served basis, the numbers are
+    infinitely incremented and the same blocks can be repeated in a structure.
 
@@
 
-    Once the pieces have been added and the individuals are ready to be evaluated a
-    simulation on the game environment is scheduled by order in the population, all
-    the individuals have a maximum of ten seconds to maintain balance or reach
-    absolute stability, if absolute stability is reached it means one of two things,
-    first the generated structure is completely stable or second, the tower fell to
-    either side and the pieces were destroyed or stopped moving by gravitational
-    pull, when either of this happens by more than two seconds the simulation ends
-    regardless of time remaining and the next individual is simulated.
+    These structures represent individuals in the evolutionary algorithm. Once
+    an individual is created it is ready to be evaluated in a simulation on the
+    game environment. Using a similar approach as the composite generator, all
+    individuals have a maximum of ten seconds to maintain balance or reach
+    absolute stability, if absolute stability is reached it means one of two
+    things, first the generated structure is completely stable or second, the
+    tower fell to either side and the pieces were destroyed or stopped moving by
+    gravitational pull, when either of this happens by more than two seconds the
+    simulation ends regardless of time remaining and the next individual is
+    simulated.
 
     The evaluation process for this project is still in the development stages,
-    however in order to check that the evolution is working has it should a criteria
-    has been temporarily made as follows, each individual in the population has 100
-    points so before the simulation starts each of them are viable candidates to be
-    an elite member of the population regardless relative height or complexity, then
-    the remaining of the process is separated in three phases has follows.
+    and in our experience is one one of the more difficult components in this
+    kind of systems. In this stage of the evolution, we first need to assign a
+    good fitness to those structures that keep their balance and not fall apart.
+    There are other variables we take in to account, but they will be explained
+    later. In this initial stage, each individual in the population has 100
+    points so before the simulation starts each of them are viable candidates to
+    be an elite member of the population regardless of their relative height or
+    complexity, then the remaining of the process is separated in three phases
+    has follows. This is the same approach used in the composite generator.
 
@@
 
-    Second, after removing percentage according to the missing pieces an individual
+    Second, after removing a percentage according to the missing pieces an individual
     remaining pieces are checked for their positions in comparison to the original

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
added references and changed how we solve it?

@@
     %(summary)   
-    In order to tackle this case study, we proposed the use a genetic algorithm
-    capable of creating game levels having the objective of being both
-    \textit{interesting} and \textit{playable}.
+    In order to tackle this case study, we proposed the use a genetic algorithm capable 
+    of creating game levels having the objective of being both \textit{interesting} and 
+    \textit{playable}, the way to test our candidate solutions will be by using a open-source
+    software called Science Birds \cite{sciencebirds} which uses the same resources used on the
+    original angry birds game.
 
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[width=80mm]{Images/new_model.png}}
+    \centerline{\includegraphics[width=80mm]{Images/new_model_v2.png}}
     \caption{New system diagram based on the parameter file and the new chromosome representation.}

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
more

--- 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
@@
     be an elite member of the population regardless of their relative height or
-    complexity, then the remaining of the process is separated in three phases
-    has follows. This is the same approach used in the composite generator.
+    complexity.
 
     First, after each of the individual simulations are over the evaluation process
-    takes place, in this phase the resulting level is checked for pieces, each one
+    takes place, in this phase the resulting level is checked for those blocks that
+    survived, that is they where not destroyed by falling. Each one
     of them is counted and then the resulting number is compared to that of the
-    initial quantity of pieces that were originally put in before the simulation in
-    order to calculate the first element of the evaluation process, each piece
-    represents a certain percentage of 100\% so the missing pieces are subtracted
-    from the total.
+    initial quantity of pieces that were originally put in before the simulation,
+    each block represents a certain percentage of 100\% so the missing pieces 
+    are subtracted from the total. In this moment, each block is counted as if 
+    it was not a member of a composite, this is becuse after the simulation there is
+    only data about each individual block.
 
-    Second, after removing a percentage according to the missing pieces an individual
-    remaining pieces are checked for their positions in comparison to the original
-    ones before the simulation, using the formula 1 each piece within the individual
-    is evaluated according to the center point of the piece, if the piece moved more
-    than a certain threshold half the percentage for one piece is removed from the
-    remaining percentage, after this using formula 2 the position of the piece
-    is further checked, this time by the difference in angle from the original one,
-    in case the difference of angles is more than a certain threshold half a piece
-    value is further removed from the total.
+    %Second, after removing a percentage according to the missing pieces an individual
+    %remaining pieces are checked for their positions in comparison to the original
+    %ones before the simulation, using the formula 1 each piece within the individual
+    %is evaluated according to the center point of the piece, if the piece moved more
+    %than a certain threshold half the percentage for one piece is removed from the
+    %remaining percentage, after this using formula 2 the position of the piece
+    %is further checked, this time by the difference in angle from the original one,
+    %in case the difference of angles is more than a certain threshold half a piece
+    %value is further removed from the total.
 
-    \begin{equation}
-        \begin{aligned}
-        error_{xy} = \left\{ \,
-            \begin{IEEEeqnarraybox}[][c]{l?s}
-                \IEEEstrut
-                0.1 & if $ 0.08 > d $, \\
-                \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
-                \IEEEstrut
-            \end{IEEEeqnarraybox}
-        \right. \\
-        where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
-        \end{aligned}
-        \label{error_xy}
-    \end{equation}
+    %\begin{equation}
+    %    \begin{aligned}
+    %    error_{xy} = \left\{ \,
+    %        \begin{IEEEeqnarraybox}[][c]{l?s}
+    %            \IEEEstrut
+    %            0.1 & if $ 0.08 > d $, \\
+    %            \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
+    %            \IEEEstrut
+    %        \end{IEEEeqnarraybox}
+    %    \right. \\
+    %    where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
+    %    \end{aligned}
+    %    \label{error_xy}
+    %\end{equation}
 
-    \begin{equation}
-        \begin{aligned}
-        error_{r} = \left\{ \,
-            \begin{IEEEeqnarraybox}[][c]{l?s}
-                \IEEEstrut
-                0 & if $ -5 \le r \le 5 $, \\
-                \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
-                \IEEEstrut
-            \end{IEEEeqnarraybox}
-        \right. \\
-        where: r= |rotation_0| - |rotation_f|   
-        \end{aligned}
-        \label{error_angle}
-    \end{equation}
+   % \begin{equation}
+   %     \begin{aligned}
+   %     error_{r} = \left\{ \,
+   %         \begin{IEEEeqnarraybox}[][c]{l?s}
+   %             \IEEEstrut
+   %             0 & if $ -5 \le r \le 5 $, \\
+   %             \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
+   %             \IEEEstrut
+   %         \end{IEEEeqnarraybox}
+   %     \right. \\
+   %     where: r= |rotation_0| - |rotation_f|   
+   %     \end{aligned}
+   %     \label{error_angle}
+   % \end{equation}
 
-    Finally, the total height of the remaining group of pieces is calculated by
-    combining the bonding boxes of all pieces, then the individuals are ordered by
-    the obtained percentage and then further ordered by the total height, this way
-    the most balanced ones will have the best probability to be selected together
-    for a crossover operation to create the next generation.
+  % Finally, the total height of the remaining group of pieces is calculated by
+  %  combining the bonding boxes of all pieces, then the individuals are ordered by
+  %  the obtained percentage and then further ordered by the total height, this way
+  %  the most balanced ones will have the best probability to be selected together
+  %  for a crossover operation to create the next generation.
 
-    \begin{figure}[htbp]
-    \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
-    \caption{Result samples of current system.}
-    \label{results_old}
-    \end{figure}
+ %   \begin{figure}[htbp]
+ %   \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
+ %   \caption{Result samples of current system.}
+ %   \label{results_old}
+ %   \end{figure}
 
-    Since there is a need to create complex structures than can cover a great
-    section of the play map, a method to evaluate the distribution is needed, for
-    this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
-    guideline used while creating images, the purpose is to create
-    aesthetical pleasant images where the focus point or the most important area is
-    at the center of the image as shown on figure \ref{rule_of_thirds}, using this
-    rule different distribution groups or masks are created has shown on figure
-    \ref{rule_of_thirds_masks} in order to use them before the simulation of an
-    individual by placing the pieces in order to distribute them in a way that can cover
-    more area and create more balanced levels instead of using a tower like
-    distribution as shown on figure \ref{results_old}.
+ %   Since there is a need to create complex structures than can cover a great
+ %   section of the play map, a method to evaluate the distribution is needed, for
+ %   this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
+ %   guideline used while creating images, the purpose is to create
+ %   aesthetical pleasant images where the focus point or the most important area is
+ %   at the center of the image as shown on figure \ref{rule_of_thirds}, using this
+ %   rule different distribution groups or masks are created has shown on figure
+ %   \ref{rule_of_thirds_masks} in order to use them before the simulation of an
+ %   individual by placing the pieces in order to distribute them in a way that can cover
+ %   more area and create more balanced levels instead of using a tower like
+ %   distribution as shown on figure \ref{results_old}.
 
-    \begin{figure}[htbp]
-        \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
-        \caption{Rule of thirds example.}
-        \label{rule_of_thirds}
-    \end{figure}
+ %   \begin{figure}[htbp]
+ %       \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
+ %       \caption{Rule of thirds example.}
+ %       \label{rule_of_thirds}
+ %   \end{figure}
 
-    \begin{figure}[htbp]
-        \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
-        \caption{Masks created using the rule of thirds.}
-        \label{rule_of_thirds_masks}
-    \end{figure}
+ %   \begin{figure}[htbp]
+ %       \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
+ %       \caption{Masks created using the rule of thirds.}
+ %       \label{rule_of_thirds_masks}
+ %   \end{figure}
 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
a

@@
     they liked the layout of the levels. A search based approach has been also used
-    in several works. 
+    in several works. Laura Calle \cite{lauracalle} proposed a method in which the 
+    pieces in the game are arranged in groups using the gravity of the game to 
+    create structures that are later evolved into more complex levels, this method 
+    was used as a base to work with since it used a modified version of the angry 
+    birds game that was able to obtain the data of a level after a simulation.
     %%%

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Section explanation modification

@@
     %% The following sentence is not clear.
-    the basis of the development, modification to the original proposed method as 
-    well as different approaches that were taken to solve the problem.
+    the way the candidate solutions are represented, to the way the mutations are applied 
+    to them, as well as the way we use our fitness fucntion to determine the playability
+    and complexity of the generated levels, 
+    %the basis of the development, modification to the original proposed method as 
+    %well as different approaches that were taken to solve the problem.
     % to the different methods that have been used to
@@
     paper as well as improvements that can help to refine the proposed work.
+
+    %Maybe like this? JSH
 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Removed blank cite
Error on abstract

@@
     additional characteristics of being interesting and playable. We propose a 
-    multi-layered search, first contructing composite structures from basic components, to then
+    multi-layered search, first constructing composite structures from basic components, to then
     build more complex structures building from these components, following an open-ended 
@@
     Structures are compositions of composites. A level can be seen as a collection 
-    of structures and each structure is a pile of composite blocks. This approach 
-    was proposed by \cite{ }. This way of constructing levels has the advantage of
+    of structures and each structure is a pile of composite blocks. This way of 
+    constructing levels has the advantage of
     limiting the search space, to structures that have a better chance to be 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
more work

--- 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
@@
     they liked the layout of the levels. A search based approach has been also used
-    in several works. Laura Calle \cite{lauracalle} proposed a method in which the 
-    pieces in the game are arranged in groups using the gravity of the game to 
-    create structures that are later evolved into more complex levels, this method 
-    was used as a base to work with since it used a modified version of the angry 
-    birds game that was able to obtain the data of a level after a simulation.
+    in several works. 
     %%%
@@
 
-    %Second, after removing a percentage according to the missing pieces an individual
-    %remaining pieces are checked for their positions in comparison to the original
-    %ones before the simulation, using the formula 1 each piece within the individual
-    %is evaluated according to the center point of the piece, if the piece moved more
-    %than a certain threshold half the percentage for one piece is removed from the
-    %remaining percentage, after this using formula 2 the position of the piece
-    %is further checked, this time by the difference in angle from the original one,
-    %in case the difference of angles is more than a certain threshold half a piece
-    %value is further removed from the total.
+    \subsection{Structure Positioning}
 
-    %\begin{equation}
-    %    \begin{aligned}
-    %    error_{xy} = \left\{ \,
-    %        \begin{IEEEeqnarraybox}[][c]{l?s}
-    %            \IEEEstrut
-    %            0.1 & if $ 0.08 > d $, \\
-    %            \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
-    %            \IEEEstrut
-    %        \end{IEEEeqnarraybox}
-    %    \right. \\
-    %    where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
-    %    \end{aligned}
-    %    \label{error_xy}
-    %\end{equation}
-
-   % \begin{equation}
-   %     \begin{aligned}
-   %     error_{r} = \left\{ \,
-   %         \begin{IEEEeqnarraybox}[][c]{l?s}
-   %             \IEEEstrut
-   %             0 & if $ -5 \le r \le 5 $, \\
-   %             \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
-   %             \IEEEstrut
-   %         \end{IEEEeqnarraybox}
-   %     \right. \\
-   %     where: r= |rotation_0| - |rotation_f|   
-   %     \end{aligned}
-   %     \label{error_angle}
-   % \end{equation}
-
-  % Finally, the total height of the remaining group of pieces is calculated by
-  %  combining the bonding boxes of all pieces, then the individuals are ordered by
-  %  the obtained percentage and then further ordered by the total height, this way
-  %  the most balanced ones will have the best probability to be selected together
-  %  for a crossover operation to create the next generation.
-
- %   \begin{figure}[htbp]
- %   \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
- %   \caption{Result samples of current system.}
- %   \label{results_old}
- %   \end{figure}
-
- %   Since there is a need to create complex structures than can cover a great
- %   section of the play map, a method to evaluate the distribution is needed, for
- %   this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
- %   guideline used while creating images, the purpose is to create
- %   aesthetical pleasant images where the focus point or the most important area is
- %   at the center of the image as shown on figure \ref{rule_of_thirds}, using this
- %   rule different distribution groups or masks are created has shown on figure
- %   \ref{rule_of_thirds_masks} in order to use them before the simulation of an
- %   individual by placing the pieces in order to distribute them in a way that can cover
- %   more area and create more balanced levels instead of using a tower like
- %   distribution as shown on figure \ref{results_old}.
-
- %   \begin{figure}[htbp]
- %       \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
- %       \caption{Rule of thirds example.}
- %       \label{rule_of_thirds}
- %   \end{figure}
-
- %   \begin{figure}[htbp]
- %       \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
- %       \caption{Masks created using the rule of thirds.}
- %       \label{rule_of_thirds_masks}
- %   \end{figure}
-
-    Using this same distribution a new evaluation will be added in which according
-    to how much of the area is filled a score will be given and this score will be
-    used as a new sorting value at the moment of selecting individuals for the
-    crossover operation, since as shown on figure \ref{rule_of_thirds_masks} there
-    is a possibility that a huge mask is given to an individual it can be possible
-    that the amount of pieces will not be able to cover the full area given, so in
-    order to prevent this kind of problem we also proposed to give each mask a
-    value that refers to the minimum amount of pieces and height required to fill
-    the most of the mask, then check the amount of pieces and height before
-    simulation for a single individual and then randomize which mask of the ones
-    that can be used will be assigned to that individual, this way the results shown
-    on figure \ref{rule_of_thirds_result} are obtained, this however gave us a new
-    problem because as shown in the figure and on figure \ref{rule_of_thirds_applied} as well, the were
-    instances in which a certain combination of pieces could be to big for the area
-    and this pieces resulted in a level that had structural flaws from the beginning
-    which cold provoke the entire structure and immeadiately nearby others to fall
-    at the beginning of the simulation however this allowed us to realize that predefined 
-    composites could provide problems to the generated structures therefore this approach 
-    was not the best for this problem.
+     The positioning of structures in the map is important in order to generate
+     levels that are fun and aesthetic. For this we need a method to indcate the
+     positioning of each structure. We propose the use of a mask where the
+     positioning of each pile and the number of blocks it contains is specefied.
+     Again these masks could be manually created, for instance using the rule of
+     thirds \cite{DarrenRowse} which is a guideline used while creating images,
+     the purpose is to create aesthetical pleasant images where the focus point
+     or the most important area is at the center of the image as shown on figure
+     \ref{rule_of_thirds}, using this rule different distribution groups or
+     masks are created has shown on figure \ref{rule_of_thirds_masks} in order
+     to use them before the simulation of an individual by placing the pieces in
+     order to distribute them in a way that can cover more area and create more
+     balanced levels instead of using a tower like distribution as shown on
+     figure \ref{results_old}. There is an option in the system to generate in a
+     first step a collection of masks, following this rules, but this qpproach
+     has a drawback. Pre-generating masks would not allow the generator to
+     \textit{evolve} because the individuals would be limited to a certain
+     number of possibles combinations which will in turn prevent diversity in
+     the population, so in order to prevent this we proposed an approach that
+     allows the individuals to generate a mask in which a number of columns is
+     defined by default but the amount of pieces in each one is random, however
+     the total amount of assigned blockes in all columns must be the same as the
+     total pieces allowed in each individual. The number of maximum blocks is as
+     a parameter. An example of this can be seen in figure \ref{new_chrom} where
+     the total of pieces in a individual is 18 and this pieces are distributed
+     on all the columns available.
 
     \begin{figure}[htbp]
-        \centerline{\includegraphics[width=80mm]{Images/chromosome_thirds.png}}
-        \caption{Rule of thirds applied to an individual.}
-        \label{rule_of_thirds_applied}
+        \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
+        \caption{Rule of thirds example.}
+        \label{rule_of_thirds}
+    \end{figure}
+
+    \begin{figure}[htbp]
+        \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
+        \caption{Masks created using the rule of thirds.}
+        \label{rule_of_thirds_masks}
     \end{figure}
@@
 
-    \subsection{New approach}
+   % The competition also requires that a generator follows a certain ruleset this is 
+   % emulated by providing a file to the system to simulate the ruleset provided at the 
+   % competition, this \textit{text file
+   % (parameters.txt)} provides the specifications that must be met in the
+   % competition, the parameters in the file are as follows:
 
-    The first differece that the new approach has is that the masks that are assigned
-    to each individual are no longer pre-generated ones, this is because we decided
-    that pre-generating them would not allow the generator to \textit{evolve}
-    because the individuals would be limited to a certain number of possibles
-    combinations which will in turn prevent diversity in the population, so in order
-    to prevent this the modification to this section allows the individuals to
-    generate a mask in which a number of columns is defines by default but the
-    amount of pieces in each one is random, however the total of assigned pieces in
-    all columns must be the same as the total pieces allowed in each individual
-    which is a number assigned before beginning the system, an example of this
-    can be seen in figure \ref{new_chrom} where the total of pieces in a individual
-    is 18 and this pieces are distributed on all the columns available. This is
-    further explained in this section.
-
-    The competition also requires that a generator follows a certain ruleset this is 
-    emulated by providing a file to the system to simulate the ruleset provided at the 
-    competition, this \textit{text file
-    (parameters.txt)} provides the specifications that must be met in the
-    competition, the parameters in the file are as follows:
-
-    \begin{itemize}
-        \item Total required levels.
-        \item Restrictions to pieces or piece-material combinations that cannot be
-        placed or used in the levels, in this case if the file specifies that a
-        \textit{CIRCLE} made out of \textit{ICE} cannot be placed, so the system must be
-        able to verify that said combination is not used.
-        \item Total number of pigs, this value can be a single value or a range of
-        values that represent how many pigs must be placed on a level.
-        \item The amount of time in which the system must give an output.
-    \end{itemize}
+   % \begin{itemize}
+   %     \item Total required levels.
+   %     \item Restrictions to pieces or piece-material combinations that cannot be
+   %     placed or used in the levels, in this case if the file specifies that a
+   %     \textit{CIRCLE} made out of \textit{ICE} cannot be placed, so the system must be
+   %     able to verify that said combination is not used.
+   %     \item Total number of pigs, this value can be a single value or a range of
+   %     values that represent how many pigs must be placed on a level.
+   %     \item The amount of time in which the system must give an output.
+   % \end{itemize}
 
@@
 
-    Using this as a base a new system diagram is proposed as shown of figure
-    \ref{new_model} in which the file with parameters is integrated with the input
-    data  the system requires, the way the individuals of the population are further
-    presresented and the way the simulation phase is taken, the method to
-    representate the individuals is proposed by dividing the individual on three
-    layers represented as follows:
+    A diagram showng the main components and data flow of the proposed system
+    is shown in Figure \ref{new_model} in which the parameter file of the competition 
+    is integrated as an input. The layers of the system is exaplained next:
 
     \begin{itemize}
-        \item Element layer: also known as pieces layer, this layer represents the
-        elements assigned to a particular individual by an array of numbers from 0
-        to infinite, where each number represents a reference to the class of a piece
-        in the selection pool including the ones generated by the OOE algorithm, the
-        representetion of this is was shown in figure \ref{old_chrom}.
-        \item  Mask layer: this layer is represented by a 7 digit array in which the
-        value assigned in each column represents the amount of pieces from the
-        element layer that will be assigned to said column, a representation of this
-        is shown on figure \ref{mask_layer}.
-        \item Enemy layer: also known as pig layer, this layer is represented by two
-        elements a single numeric value representing the total amount of pigs
-        assigned to the level and an array of locations for the placement of this
-        same pigs, a representation of it is shown on figure \ref{enemy_layer}. 
+        \item Composite Generator:  This layer represents the composite blocks
+        assigned to a particular individual as list of integer numbers, where
+        each number represents a reference to a composite object including the
+        ones generated by the OOE algorithm, the representetion of this is was
+        shown in figure \ref{old_chrom}.
+        \item Structure layer: Individuals are represented by a list of seven
+        integers, representing a mask in which integers assigned in each column
+        represents the amount of composite blocks from the element layer that
+        will be assigned to said column, a representation of this is shown on
+        figure \ref{mask_layer}.
+        \item Enemy layer: also known as pig layer, this layer is represented by
+        two elements a single numeric value representing the total amount of
+        pigs assigned to the level and an array of locations for the placement
+        of this same pigs, a representation of it is shown on figure
+        \ref{enemy_layer}. 
     \end{itemize}
@@
         \centerline{\includegraphics[width=80mm]{Images/enemy_layer.png}}
-        \caption{Amount of pigs in a level, their location relative to the mask layer (green) and fenotype representation.}
+        \caption{Amount of pigs in a level, their location relative to the mask layer
+         (green) and fenotype representation.}
         \label{enemy_layer}
@@
 
+    \subsection{Evolution of Levels}
+
     In order to select the parents of the next generation the parents are ordered by
-    their fitness, then the system can choose between 2 options for the selection,
-    tournament selection or roulette selection:
+    their fitness. There are two types of selection:
 
     \begin{itemize}
+    % This needs more work.    
         \item Tournament selection: in order to select the parent by this method the

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Modification to conclusions

--- 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
@@
 
+    We were able to fulfill our objective of generating levels that could be played, 
+    however as seen in our figures the current state of this system is still in development 
+    phase, and some modifications must be applied in order to optimize some aspects of it, 
+    by using a different way of generating individual we were able to reduce the process 
+    time requierd on a full system execution however we require to search for a way to 
+    avoid using the software to evaluate the individuals, this way we expect to reduce 
+    drastically the time required to process the data of the levels.
+
     Finally a different method to evaluate the individuals must be created, this is

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
first  complete pass

--- 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
@@
 
+    Once structures are able to stand, there are other aspects we need to take
+    in to account to evaluate their fitness. In this case we propose the use to
+    reward both the \textit{"diversity"} and \textit{"uniqueness"} of a
+    individual defining a fitness function considering:
+
+    \begin{itemize}
+        \item Hamming distance: a simle explanation for the \textit{Hamming
+        distance} is that it is a calculation applied to a pair of strings where the
+        objective is to find the minimum required number of substitutions required in
+        order to convert a string exactly the same as the other, its formula is
+        shown in equation \ref{hamming_distance}, since the formula itself locates
+        the minimum number of substitutions then we compare the individual
+        with the rest of the population trying to find the maximum number of
+        substitutions required efectively using the formula to give a better fitness
+        to those individuals that are different from the group.
+        \item Shannon entropy: the shannon entropy is used on information theory to
+        calculate the disorder or uncertainty, in this case it will be used to
+        determine if a level is \textit{"boring"} or \textit{"interesting"} based on
+        the amount of entropy calculated according to the pieces used in a level
+        where a low entropy is boring because if a determined level as a lot of
+        repeated pieces then it will look simple, the formula used is shown in
+        equation \ref{shannon_entropy} where the elements calculated are the pieces
+        of a level and their appearance probability against all others.
+    \end{itemize}
+
+    \begin{equation}
+        \begin{aligned}
+        d = min \left\{ \ d(x,y): x,y \in C, if \: x \neq y, 1 \: else \: 0 \: \right\} \
+        \end{aligned}
+        \label{hamming_distance}
+    \end{equation}
+
+    \begin{equation}
+        \begin{aligned}
+        S = - \Sigma_i P_i \log P_i
+        \end{aligned}
+        \label{shannon_entropy}
+    \end{equation}
+
     In order to select the parents of the next generation the parents are ordered by
@@
     The mutation operations of the generator work with the pieces layer of an
-    individual, the four types of mutations used are:
+    individual, the four types of mutations are:
 
@@
 
-    This mutations do not have to be used all at once on a single individual but
-    depending on the probabilities they can happen all at once, since most of the
-    pieces on a individual are mostly the same type of material then at least the
-    material mutation can occurr on all or most of the individuals to ensure that
-    all levels will not have all the pieces with the same material which could
-    render a level \textit{"boring"} by the fitness function.
-
-    Since this group of mutations further ensures diversity in the populations a
-    different way to evaluate the individuals is needed, by using the previous
-    proposed method as a base a way to evaluate the \textit{"diversity"} and
-    \textit{"uniqueness"} of a individual, for this we first remove the \textit{x}
-    and \textit{y} position as well as the \textit{angle} errors in order to add two
-    new evaluation formulas as follows:
-
-    \begin{itemize}
-        \item Hamming distance: a simle explanation for the \textit{Hamming
-        distance} is that it is a calculation applied to a pair of strings where the
-        objective is to find the minimum required number of substitutions required in
-        order to convert a string exactly the same as the other, its formula is
-        shown in equation \ref{hamming_distance}, since the formula itself locates
-        the minimum number of substitutions then we compare the individual
-        with the rest of the population trying to find the maximum number of
-        substitutions required efectively using the formula to give a better fitness
-        to those individuals that are different from the group.
-        \item Shannon entropy: the shannon entropy is used on information theory to
-        calculate the disorder or uncertainty, in this case it will be used to
-        determine if a level is \textit{"boring"} or \textit{"interesting"} based on
-        the amount of entropy calculated according to the pieces used in a level
-        where a low entropy is boring because if a determined level as a lot of
-        repeated pieces then it will look simple, the formula used is shown in
-        equation \ref{shannon_entropy} where the elements calculated are the pieces
-        of a level and their appearance probability against all others.
-    \end{itemize}
-
-    \begin{equation}
-        \begin{aligned}
-        d = min \left\{ \ d(x,y): x,y \in C, if \: x \neq y, 1 \: else \: 0 \: \right\} \
-        \end{aligned}
-        \label{hamming_distance}
-    \end{equation}
-
-    \begin{equation}
-        \begin{aligned}
-        S = - \Sigma_i P_i \log P_i
-        \end{aligned}
-        \label{shannon_entropy}
-    \end{equation}
+    This mutations do not have to be used all at othe same time on a single
+    individual but depending on the probabilities they can happen all at once,
+    since most of the pieces on a individual are mostly the same type of
+    material then at least the material mutation can occurr on all or most of
+    the individuals to ensure that all levels will not have all the pieces with
+    the same material which could render a level \textit{"boring"} by the
+    fitness function.
 
@@
 
-    The system as been able to generate levels that fulfill the requirements
+     The system has been able to generate levels that fulfill the requirements
      provided by the parameters file, however a way to evaluate that the levels
-     generated are indeed \textit{"fun"} or \textit{"interesting"} is still needed,
-     at this point we have two was to evaluate the results:
+     generated are indeed \textit{"fun"} or \textit{"interesting"} is still
+     needed, at this point we could evaluate the levels by appling an aproach
+     used in previous competitions:
      \begin{itemize}

### 2019-05-15 NOTarticle_english.tex

--- 2019-05-14 article_english.tex
@@
 
-\title{Procedural generation of levels fot he angry birds videogame using
+\title{Procedural generation of levels for the Angry Birds videogame using
 evolutionary computation\\
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{3\textsuperscript{rd} Juan-J. Merelo-Guervós}
+\IEEEauthorblockA{\textit{Dept. Computer Technology and Architecture} \\
+\textit{University of Granada\\
+Granada, Spain \\
+jmerelo@ugr.es}
 }

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Spell check

--- 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
@@
 \begin{abstract}
-    % We do not say this project, is more like: In this paoer an evolutionary ... 
-    % is presented or In this paper we present a .... (in third or first person plural) - MG   
-    In this paper an evolutionary computation-based system is proposed to generate 
-    levels for the Angry Birds video game, the levels themselves are composed of a 
+    In this paper we propose an evolutionary computation-based system to generate 
+    levels for the Angry Birds video game. The levels themselves are composed of a 
     set of birds that the player can use, a certain amount of pigs that must be destroyed 
     in order to progress to the next level and a given number of pieces that conform 
-    structures that may or may not protect the pigs from the player. The focus in this stage
+    structures that may or may not protect the pigs from the player. The focus in this stage of the work
     is the generation of diverse structures that can be played in the game having the
@@
     build more complex structures building from these components, following an open-ended 
-    evolution approach; in which the evolution of structures is not guided towards 
-    a single objective but rather is free to evolve and generate novelty or diversity. 
+    evolution approach in which the evolution of structures is not guided towards 
+    a single objective but is rather free to evolve and generate novelty or diversity. 
     The objective is then that the proposed levels are evaluated by how complex they become and how 
     different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
-    to have a level of uniqueness because on most of the cases the way they are presented on screen
+    to be unique since, on most cases, the way they are presented on screen
     is a way a normal human would have trouble to create but at the same time are interesting to see.
@@
     % this should be the last section we write. - M
+    % Another revision to English would be good.
     \end{abstract}
@@
     \begin{IEEEkeywords}
-    genetic algorithm, procedural generated content, open-ended evolution,
+    Genetic algorithm, procedural generated content, open-ended evolution,
     evolutionary computation
@@
     green pig-like entities in order to obtain the highest score possible, the game
-    uses a gravity and collition system that allows the structures to fall and be
+    uses a gravity and collision system that allows the structures to fall and be
     destroyed by means of damage as well as the use of three different construction
@@
     abilities, to destroy both the structures and the objectives. A high score 
-    is achived by doing the most destruction with the least birds possible 
+    is achieved by doing the most destruction with the least birds possible 
     \cite{RovioEntertainmentCorporation2009}.
@@
     The main objective of this project is to generate levels that can be played
-    by naïve or inteligent agents as well as physical players. The levels
+    by naïve or intelligent agents as well as physical players. The levels
     themselves need to be complex in the sense that interesting structures can be
@@
     provide an interesting The challenge for the participating algorithms is to be
-    flexible on the pieces that can be used and the runing time of the algorithm, as
+    flexible on the pieces that can be used and the running time of the algorithm, as
     they are determined at runtime. 
@@
     the evolution (an optimal solution) but to continue evolving and creating new
-    types of entities, perhaps more complex on each new generation. Solutuion
+    types of entities, perhaps more complex on each new generation. Solution
     entities have the possibility to evolve not only inside the frame of their type,
@@
     than just converging to a stable or quasi-stable state.For this project, OEE is
-    defined simply as a genetic evolution process with different clasess of objects,
+    defined simply as a genetic evolution process with different classes of objects,
     with compositional and taxonomic relationships between them. Objects of each
-    class can evolve in parallel or as in this case, independenly of each other. The
+    class can evolve in parallel or as in this case, independently of each other. The
     idea is based on the object oriented model, in which complex behavior can be
@@
     the way the candidate solutions are represented, to the way the mutations are applied 
-    to them, as well as the way we use our fitness fucntion to determine the playability
+    to them, as well as the way we use our fitness function to determine the playability
     and complexity of the generated levels, 
@@
     with the goal of developing a level generator for the game. Several generators
-    have been proposed in the following years of competition. M. Kaidan et al.
+    have been proposed in the following years of competition. M. Katina et al.
     \cite{Kaidan2015} propose a model in which the generation of content is
@@
     the building blocks for the structures to come. A composite could include
-    different types of blocks, rotaded at a certain angle and compose a basic
+    different types of blocks, rotated at a certain angle and compose a basic
     structure. An ideal composite could support other composites on top with out
     falling apart, but this is not required. A composite is measured using
-    maginary bounding box, defined by calculating the lengths of all the pieces,
+    imaginary bounding box, defined by calculating the lengths of all the pieces,
     finding the borders of said pieces and then finding the points that could
@@
     of falling blocks and selecting those that remain standing. This algorithm is 
-    not capable of creating complex strucures, but it can generate very novel basic
+    not capable of creating complex structures, but it can generate very novel basic
     structures. We can see that the evolution at this level can benefit from having
     more freedom in how basic structures are built. We do not want to form piles
-    or sequences of blocks, this will be done at a higher level in the composite hirarchy.
+    or sequences of blocks, this will be done at a higher level in the composite hierarchy.
 
@@
     \item From the best individuals select composites. Several algorithms could
-    be proposed for this step, for instance selcting clusters of blocks.
+    be proposed for this step, for instance selecting clusters of blocks.
     \end{enumerate}
@@
     to generate levels that are \textit{fun} and \textit{enjoyable} however they 
-    also have to be challenging but not imposible. However the rules for the competition 
+    also have to be challenging but not impossible. However the rules for the competition 
     specify that a configuration file must be used to
@@
     \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
-    an id assigned to it. A structure is then a list of ids, refering to
+    an id assigned to it. A structure is then a list of ids, referring to
     composite blocks, the first 11 are basic composite and generated composites 
@@
     are subtracted from the total. In this moment, each block is counted as if 
-    it was not a member of a composite, this is becuse after the simulation there is
+    it was not a member of a composite, this is because after the simulation there is
     only data about each individual block.
@@
      The positioning of structures in the map is important in order to generate
-     levels that are fun and aesthetic. For this we need a method to indcate the
+     levels that are fun and aesthetic. For this we need a method to indicate the
      positioning of each structure. We propose the use of a mask where the
-     positioning of each pile and the number of blocks it contains is specefied.
+     positioning of each pile and the number of blocks it contains is specified.
      Again these masks could be manually created, for instance using the rule of
      thirds \cite{DarrenRowse} which is a guideline used while creating images,
-     the purpose is to create aesthetical pleasant images where the focus point
+     the purpose is to create aesthetic pleasant images where the focus point
      or the most important area is at the center of the image as shown on figure
@@
      figure \ref{results_old}. There is an option in the system to generate in a
-     first step a collection of masks, following this rules, but this qpproach
+     first step a collection of masks, following this rules, but this approach
      has a drawback. Pre-generating masks would not allow the generator to
@@
      defined by default but the amount of pieces in each one is random, however
-     the total amount of assigned blockes in all columns must be the same as the
+     the total amount of assigned blocks in all columns must be the same as the
      total pieces allowed in each individual. The number of maximum blocks is as
@@
 
-    A diagram showng the main components and data flow of the proposed system
+    A diagram shows the main components and data flow of the proposed system
     is shown in Figure \ref{new_model} in which the parameter file of the competition 
-    is integrated as an input. The layers of the system is exaplained next:
+    is integrated as an input. The layers of the system is explained next:
 
@@
         each number represents a reference to a composite object including the
-        ones generated by the OOE algorithm, the representetion of this is was
+        ones generated by the OEE algorithm, the representation of this is was
         shown in figure \ref{old_chrom}.
@@
         \centerline{\includegraphics[width=80mm]{Images/mask_layer.png}}
-        \caption{Mask array with column and fenotype representation.}
+        \caption{Mask array with column and phenotype representation.}
         \label{mask_layer}
@@
         \caption{Amount of pigs in a level, their location relative to the mask layer
-         (green) and fenotype representation.}
+         (green) and phenotype representation.}
         \label{enemy_layer}
@@
     \begin{itemize}
-        \item Hamming distance: a simle explanation for the \textit{Hamming
+        \item Hamming distance: a simple explanation for the \textit{Hamming
         distance} is that it is a calculation applied to a pair of strings where the
@@
         with the rest of the population trying to find the maximum number of
-        substitutions required efectively using the formula to give a better fitness
+        substitutions required effectively using the formula to give a better fitness
         to those individuals that are different from the group.
-        \item Shannon entropy: the shannon entropy is used on information theory to
+        \item Shannon entropy: the Shannon entropy is used on information theory to
         calculate the disorder or uncertainty, in this case it will be used to
@@
         \item Tournament selection: in order to select the parent by this method the
-        system checks the amount of crossovers assigned, then calculates the ammount
+        system checks the amount of crossovers assigned, then calculates the amount
         of parent required to compete in pairs, then by doing a descendent selection
@@
     the mask of said individual, this way the mask can ensure that some pieces of
-    some childs in the population are now placed in the level, this can bring the
+    some children in the population are now placed in the level, this can bring the
     possibility that a mask that uses less pieces that it normally as can obtain a
@@
     types can be seen in figure \ref{crossover} in which the mask of an individual
-    is combined with another and the resulting mask for the childs have different
+    is combined with another and the resulting mask for the children have different
     amount of pieces to be placed.
@@
         \centerline{\includegraphics[width=80mm]{Images/crossover.png}}
-        \caption{Single point crossover(up) and double point crossover(bottom) aplied to an individual mask.}
+        \caption{Single point crossover(up) and double point crossover(bottom) applied to an individual mask.}
         \label{crossover}
@@
 
-    This mutations do not have to be used all at othe same time on a single
+    This mutations do not have to be used all at the same time on a single
     individual but depending on the probabilities they can happen all at once,
     since most of the pieces on a individual are mostly the same type of
-    material then at least the material mutation can occurr on all or most of
+    material then at least the material mutation can occur on all or most of
     the individuals to ensure that all levels will not have all the pieces with
@@
     then the remaining areas are not taken into account as well, then in figure \ref{layer123_combine} 
-    the previous combination of layers is evaluated by cheking which placed composites 
+    the previous combination of layers is evaluated by checking which placed composites 
     can hold a pig in the center or on the top of it, then the pigs are placed in the 
-    same oreder the composites are placed (left to right) in the locations where one 
+    same order the composites are placed (left to right) in the locations where one 
     is able to be placed.
@@
      generated are indeed \textit{"fun"} or \textit{"interesting"} is still
-     needed, at this point we could evaluate the levels by appling an aproach
+     needed, at this point we could evaluate the levels by applying an approach
      used in previous competitions:
@@
         questions themselves must try to capture the feeling of a person towards the
-        game like questioning if a level was too easy or too dificult to solve, if
+        game like questioning if a level was too easy or too difficult to solve, if
         the generated structures look interesting or if the level required them to
@@
         the way to evaluate if the level is or not \textit{"interesting"} will be by
-        checking how easily the aggent is able to solve a level, the point here is
+        checking how easily the agent is able to solve a level, the point here is
         to have a level that cannot be solved by a single movement but to have one
-        that a human player has to think a while to solve tryingto place the
+        that a human player has to think a while to solve trying to place the
         difficulty of a level just at the middle point between easy and hard
@@
 
+    We were able to fulfill our objective of generating levels that could be played, 
+    however as seen in our figures the current state of this system is still in development 
+    phase, and some modifications must be applied in order to optimize some aspects of it, 
+    by using a different way of generating individual we were able to reduce the process 
+    time required on a full system execution however we require to search for a way to 
+    avoid using the software to evaluate the individuals, this way we expect to reduce 
+    drastically the time required to process the data of the levels.
+
     Finally a different method to evaluate the individuals must be created, this is
@@
     items present in the game therefore reducing the potential of a level, we expect
-    to make the current fitness function work the most eficient that it can but
+    to make the current fitness function work the most efficient that it can but
     another possible solution is found a good combination of formulas to generate

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Fixes to refs and graphics
spaces deleted

@@
     is a way a normal human would have trouble to create but at the same time are interesting to see.
-    % Maybe like this ? JSH
-    %The experiments conducted show  
-    % We found that in the experiments conducted, levels generated where ...
-
-    % The abstract is not only for stating what whas done, it is also for 
-    % telling readers, why they should care, what's novel, how good it is, how you tested.
-    % Please get some inspirtation from other abstracts on the same subject,
-    % this should be the last section we write. - M
     % Another revision to English would be good.
@@
     Procedural content generation is an interesting subject on the entertainment
-    industry, primarily in video game development because of the savings in 
-    time and human resources when generating content for different video game projects \cite{Yannakakis2017,YannakakisContentGeneration}.
-    In this paper an evolutionary content generation system is proposed to generate
-    levels for the popular Angry Birds video game,
-    taking inspiration in concepts of open-ended evolution. Angry birds is a game 
-    developed by Rovio Entertainment in which the objective is to destroy structures
-    placed on the map as well as eliminating
-    green pig-like entities in order to obtain the highest score possible, the game
-    uses a gravity and collision system that allows the structures to fall and be
-    destroyed by means of damage as well as the use of three different construction
-    materials \textit{ice}, \textit{wood} and \textit{stone} each one with a different
-    resistance, ranging from fragile, normal and sturdy in that order. The game
-    mechanic is to use a slingshot to shoot a certain number of birds with different
-    abilities, to destroy both the structures and the objectives. A high score 
-    is achieved by doing the most destruction with the least birds possible 
+    industry, primarily in video game development because of the savings in time
+    and human resources when generating content for different video game
+    projects \cite{Yannakakis2017,YannakakisContentGeneration}. In this paper an
+    evolutionary content generation system is proposed to generate levels for
+    the popular Angry Birds video game, taking inspiration in concepts of
+    open-ended evolution. Angry birds is a game developed by Rovio Entertainment
+    in which the objective is to destroy structures placed on the map as well as
+    eliminating green pig-like entities in order to obtain the highest score
+    possible, the game uses a gravity and collision system that allows the
+    structures to fall and be destroyed by means of damage as well as the use of
+    three different construction materials \textit{ice}, \textit{wood} and
+    \textit{stone} each one with a different resistance, ranging from fragile,
+    normal and sturdy in that order. The game mechanic is to use a slingshot to
+    shoot a certain number of birds with different abilities, to destroy both
+    the structures and the objectives. A high score is achieved by doing the
+    most destruction with the least birds possible 
     \cite{RovioEntertainmentCorporation2009}.
-
-    %While it is possible to create an evolutionary agent to play the levels and
-    %obtain the best score 
     The main objective of this project is to generate levels that can be played
@@
     \cite{Stephenson,Stephenson2018}.
-
     % What is the problem?
     Procedural content generation provides a peculiar case of study because of the
-    way
-    % Is there a reference? - MG
+    way % Is there a reference? - MG
     content has to be made for a each particular type of game. In this use case we
     have those restrictions dictated by the game, and also those imposed by a
-    competition track \cite{Renz}.% Reference the paper of the competition  have
+    competition track \cite{Renz}.
     provide an interesting The challenge for the participating algorithms is to be
@@
     they are determined at runtime.   
-    %their interactions with one another because of gravity and the possible effects
-    %the trajectory of a shot from a player can affect all of this. How we solve it?
-    %(summary)   
     In order to tackle this case study, we proposed the use a genetic algorithm capable 
@@
     original angry birds game.
-
     % What is learned?
@@
     normal human could have trouble imagining of.
-
     % What is learned?
-    %We identify the places were an evolutionary algorithm can be used alongside
-    %procedural content generation applied to video games in order to be able to
-    %clarify in which areas an evolutionary algorithm can used to further improve
-    %video game development cycles.
-
     % En este trabajo se generan estructuras con mayor diversidad y por lo tanto 
     % resultan ser interesantes.
-
     We propose a basic Open-Ended Evolution (OEE) algorithm, a variant of genetic
@@
     and complexity of the generated levels, 
-    %the basis of the development, modification to the original proposed method as 
-    %well as different approaches that were taken to solve the problem.
-    % to the different methods that have been used to
-    %progress on the different sections of the project, 
-    % Normaly there is no "Future Work" section is put together with Conclusions - MG
     finally in Section 4 we provide our conclusions about the development of this
     paper as well as improvements that can help to refine the proposed work.
-
-    %Maybe like this? JSH
-
-    %we explain the future work of the project, where we are in the development phase and how the
-    %future implementations are to further improve the project and finally, in
-    %Section 6 we present our conclusions
-
-    %\section{Background}
-    %
-    %In this Section we provide a quick overview of the literature about the areas
-    %that provide the basis to the development of the current project, this section
-    %is divided in three parts, the fisrt one gives us an explanation of what
-    %procedural content generation entails, the second one provides an explanation on
-    %genetic algorithms and how can they be used to solve optimization problems, and
-    %finally, the third one provides us with an overview of open-ended evolution and
-    % use just one form, I prefer with no first caps open-ended evolution and let's 
-    % use an abbreviation OEE - MG
-
-    %what it means to have an open-ended evolution algorithm.
-    % For this conference I think we do not need to define PCG, let's think 
-    % every one knows what it is. - MG
-
-    %\subsection{Procedural content generation}
-
-    %Procedural content generation (PCG)
-
-    %\subsection{Genetic algorithm}
-
-    % This section and the proposed approach should be in the fron lines - MG
-
-    % The problem is that we just state what it is, but we do not link it
-    % with our work. Why is important? What inpired our work? 
-    % There is also Novelty Search - MG
-    % Also it sounds like a copy-paste from Wikipedia please check and reference
-    % accordingly - MG
-
-    %\subsection{Open-Ended Evolution}\label{AA}
 
@@
     At this level the composite generator has the following steps:
-
-    % Pleas explain in more detail this Composites in a section.  
-    % Here it's explained better, maybe this paragraph should be moved to
-    % an earlier point - MG
-
-    % Needs a few touches - MG
-    % Please use the name Composite instead of Bundle, composition is well known in
-    % object oriented design.
-
-    %                                                                           /|\
-    % Combined a few other things to give a litte more detail to this sections   |
-    %                                                                           \|/
-
     \begin{enumerate}
@@
     \end{figure}
-
     % Explain a bit about the competition, from the introduction
-
     The Angry Birds level generation track is a competition where the objective is 
@@
 
-    %After taking into account this restrictions the structure of our current approach
-    %had to be changed, so this section will be divided in two subsections, the first
-    %will explain the approach that was used and after that the second will explain the
-    %modifications that had to be made in order to integrate the configuration files
-    %for the competition.
-
     In our original approach, composites could added to the structure generator
@@
     is explained in the next section.
-
-    % Lets check this, I think is not needed. 
-    %The objective in this first phase of the project was to
-    %generate structures that were capable of maintaining their own balance as
-    %shown on figure \ref{test_old}, since the objective of open-ended evolution
-    %for this project is to add new composites to the pool of options,
-
     In our current approach the composite generator is only
@@
     \subsection{Structure Evolution}
-    % This sentence needs more work -MG
-
-    %During the original phase of the design of the system, it was decided that the way 
-    %composites were going to evolve was by first placing only base pieces on a level 
-    %then after a simulation the remaining pieces
-    %of a member of the population were going to be used as a new composite if after a 
-    %simulation a group was still standing and grouped on a single point, their individual 
-    %offsets from the center of the group was calculated and then using this information a new 
-    %composite could be added to the pool of options, this new
-    % we don't use member of the populations, use proposed solution, candidate solution
-    % or individual of the population. - MG  
-    %additions to the composite pool could then be added to the population by the mutation
-    %operation when a new member of the population was being created, the objective 
-    %in this first phase of the project was to generate
-    %structures that were capable of maintaining their own balance as shown on figure
-    %\ref{test_old}, since the objective of open-ended evolution for this project is
-    %to add new composites to the pool of options, then the algorithm will first run a
-    %simulation with a group of pieces and after it the ones that were not destroyed
-    %by falling because of gravity will be saved and added to the pool of options.
-
-    % New pieces are added by mutation? 
-    % Please give more details to all this - MG
 
@@
      \begin{figure}[htbp]
+        \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
+        \caption{Result samples of current system.}
+        \label{results_old}
+    \end{figure}
+
+    \begin{figure}[htbp]
         \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
@@
     \end{figure}
-
-   % The competition also requires that a generator follows a certain ruleset this is 
-   % emulated by providing a file to the system to simulate the ruleset provided at the 
-   % competition, this \textit{text file
-   % (parameters.txt)} provides the specifications that must be met in the
-   % competition, the parameters in the file are as follows:
-
-   % \begin{itemize}
-   %     \item Total required levels.
-   %     \item Restrictions to pieces or piece-material combinations that cannot be
-   %     placed or used in the levels, in this case if the file specifies that a
-   %     \textit{CIRCLE} made out of \textit{ICE} cannot be placed, so the system must be
-   %     able to verify that said combination is not used.
-   %     \item Total number of pigs, this value can be a single value or a range of
-   %     values that represent how many pigs must be placed on a level.
-   %     \item The amount of time in which the system must give an output.
-   % \end{itemize}
 

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
about to start second edit
Change to explanations
Section description on "Introduction" section & section description on section 3

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 
-    Section 2, contains a quick overview of some aspects used by different authors
+    Section \ref{SoA}, contains a quick overview of some aspects used by different authors
     in order to tackle this problem, their design and basic functionality, in
-    Section 3 the description of the current state of the project is explained, from
-    %% The following sentence is not clear.
-    the way the candidate solutions are represented, to the way the mutations are applied 
-    to them, as well as the way we use our fitness function to determine the playability
-    and complexity of the generated levels, 
-    finally in Section 4 we provide our conclusions about the development of this
+    Section \ref{prop_method} the description of the current state of the project is explained, how
+    %% The following sentence is not clear.  % Maybe this modofocation is more understandable ? JSH
+    the candidate solutions are represented and the way we defined our fitness 
+    function to determine the playability and complexity of the generated levels, 
+    finally in Section \ref{conclusion} we provide our conclusions about the development of this
     paper as well as improvements that can help to refine the proposed work.
@@
     \section{Proposed Method}
+    \label{prop_method}
 
-    In this Section we describe the approach used in this work, explaining first,
-    the restrictions of the game.
+    % Is this explanation undertandable ? JSH
+    In this section we describe the approach used in this work, explaining first,
+    the restrictions of the game, then giving a quick overview of how we create new 
+    composites to be used by the algorithm, then explaining how the candidate solutions 
+    are represented and how this are modified and evolved by the algorithm, and finally 
+    we present our method to evaluate the candidate solutions.
+
     The game contains a total of 11 block shapes as shown in Figure \ref{piece_list}.
@@
     \section{Conclusions and future work}
+    \label{conclusion}
 

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
Intro

@@
 levels for the Angry Birds video game. The levels themselves are composed of a
-    set of birds that the player can use, a certain amount of pigs that must be destroyed 
-    in order to progress to the next level and a given number of pieces that conform 
-    structures that may or may not protect the pigs from the player. The focus in this stage of the work
-    is the generation of diverse structures that can be played in the game having the
-    additional characteristics of being interesting and playable. We propose a 
-    multi-layered search, first constructing composite structures from basic components, to then
-    build more complex structures building from these components, following an open-ended 
-    evolution approach in which the evolution of structures is not guided towards 
-    a single objective but is rather free to evolve and generate novelty or diversity. 
-    The objective is then that the proposed levels are evaluated by how complex they become and how 
-    different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
-    to be unique since, on most cases, the way they are presented on screen
-    is a way a normal human would have trouble to create but at the same time are interesting to see.
+set of birds that the player can use, a certain amount of pigs that must be
+destroyed in order to progress to the next level and a given number of pieces
+that conform structures that may or may not protect the pigs from the player.
+The focus in this stage of the work is the generation of diverse structures that
+can be played in the game having the additional characteristics of being
+interesting and playable. We propose a multi-layered search, first constructing
+composite structures from basic components, to then build more complex
+structures building from these components, following an open-ended evolution
+approach in which the evolution of structures is not guided towards a single
+objective but is rather free to evolve and generate novelty or diversity. The
+objective is then that the proposed levels are evaluated by how complex they
+become and how different they are from the rest of the group. The experiments
+conducted show that a evolutionary approach allows the generated levels to be
+unique since, on most cases, the way they are presented on screen is a way a
+normal human would have trouble to create but at the same time are interesting
+to see.
 % Another revision to English would be good.
@@
 \section{Introduction}
-    Procedural content generation is an interesting subject on the entertainment
-    industry, primarily in video game development because of the savings in time
-    and human resources when generating content for different video game
-    projects \cite{Yannakakis2017,YannakakisContentGeneration}. In this paper an
-    evolutionary content generation system is proposed to generate levels for
-    the popular Angry Birds video game, taking inspiration in concepts of
-    open-ended evolution. Angry birds is a game developed by Rovio Entertainment
-    in which the objective is to destroy structures placed on the map as well as
-    eliminating green pig-like entities in order to obtain the highest score
-    possible, the game uses a gravity and collision system that allows the
-    structures to fall and be destroyed by means of damage as well as the use of
-    three different construction materials \textit{ice}, \textit{wood} and
-    \textit{stone} each one with a different resistance, ranging from fragile,
-    normal and sturdy in that order. The game mechanic is to use a slingshot to
-    shoot a certain number of birds with different abilities, to destroy both
-    the structures and the objectives. A high score is achieved by doing the
-    most destruction with the least birds possible 
-    \cite{RovioEntertainmentCorporation2009}.
-    The main objective of this project is to generate levels that can be played
-    by naïve or intelligent agents as well as physical players. The levels
-    themselves need to be complex in the sense that interesting structures can be
-    created, but at the same time, it is possible to complete in some way
-    \cite{Stephenson,Stephenson2018}.
+The video game industry is always looking for content creators to satisfy
+the demand for high-quality content. Current development teams include game
+designers,  artists, animators,  writers, level designers, among others.
+Procedural Content Generation (PCG) is often applied to generate many
+aspects of the game, from maps, levels or characters, to narrative and game
+design. PCG techniques can lower the cost in both time and human resources
+when generating content for different video game projects, without
+compromising qualitiy \cite{Yannakakis2017,YannakakisContentGeneration}. In
+this paper, we introduce an evolutionary content generation system, to
+generate fun and exciting levels for the popular Angry Birds video game. We
+follow an Open-Ended Evolution (OEE) approach.  OOE is a type of genetic
+evolution algorithm with a different objective. In this case, the goal is
+not to reach a final state of in the evolution, for instance, to reach an
+optimal solution in a search space. An OEE aims to continue evolving and
+creating new types of entities, perhaps more complex or novel on each new
+generation. Entities evolve not only inside the frame of their species, but
+they can also create entirely new species \cite{Standish2003}. Taylor et al.
+\cite{Taylor2016, Taylor} define OEE as a system capable of creating novelty
+beyond a point where nothing changes on the current group of interest rather
+than just converging to a stable or quasi-stable state. For this project,
+OEE is defined simply as a genetic algorithm with different classes of
+objects, with compositional and taxonomic relationships between them.
+Objects in a class can evolve in parallel or as in this case, independently
+of each other. The object-oriented model follows this principles to model
+complex behavior and structure \cite{levesque1986knowledge}.
+
+The case study for this paper is to follow the rules of a level generation
+competition for the Angry Birds video game developed by Rovio Entertainment.
+We briefly explain the game.  The objective is to destroy structures placed
+on a map as well as eliminating green pig-like characters. In order to
+obtain the highest score possible, the game uses a gravity and collision
+system that allows the structures to fall and be destroyed by means of
+damage. The structures have  three different construction materials
+\textit{ice}, \textit{wood} and \textit{stone}, each one with a different
+resistance, ranging from fragile, normal and sturdy in that order. The game
+mechanic is to use a slingshot to shoot a certain number of birds with
+different abilities, to destroy both the structures and the objectives. A
+high score is achieved by causing the most destruction throwing the least
+birds possible \cite{RovioEntertainmentCorporation2009}. The main objective
+of this work is to generate levels that can be played by naïve or
+intelligent agents as well as human players. The levels themselves need to
+be complex in the sense that interesting structures can be created, but at
+the same time, remaining possible to complete in some way \cite{Stephenson,
+Stephenson2018}.
 % What is the problem?
-    Procedural content generation provides a peculiar case of study because of the
-    way % Is there a reference? - MG
-    content has to be made for a each particular type of game. In this use case we
-    have those restrictions dictated by the game, and also those imposed by a
-    competition track \cite{Renz}.
-    provide an interesting The challenge for the participating algorithms is to be
-    flexible on the pieces that can be used and the running time of the algorithm, as
-    they are determined at runtime.   
-    In order to tackle this case study, we proposed the use a genetic algorithm capable 
-    of creating game levels having the objective of being both \textit{interesting} and 
-    \textit{playable}, the way to test our candidate solutions will be by using a open-source
-    software called Science Birds \cite{sciencebirds} which uses the same resources used on the
-    original angry birds game.
+
+One peculiarity of PCG is the richness of problems and domains in which it can
+be applied.  This is because each type of game dictates different restrictions
+and mechanics. In this case, we have additional restrictions, dictated by the
+competition track \cite{Renz}. This case study provides an interesting challenge
+for the participating algorithms. The proposed PCG algorithm has to be flexible
+on the pieces it can use, and also consider the running time, as both are
+determined at runtime. The aim is to develop a software capable of creating game
+levels having the objective of being both \textit{interesting} and
+\textit{playable}. Candidate solutions, in this case, Levels of the game, will
+be evaluated by using the open-source software Science Birds \cite{sciencebirds}
+which uses the same resources used on the original angry birds game. Using this
+software for the evaluation is an additional restriction because we are limited
+to the data collected during the simulation.  
 % What is learned?
-    In this work we found that an evolutionary algorithm can be used to create 
-    this type of content not only because it is able to create levels that are interesting 
-    and diverse but because an evolutionary algorithm is capable of creating things a 
-    normal human could have trouble imagining of.
-    % What is learned?
-    % En este trabajo se generan estructuras con mayor diversidad y por lo tanto 
-    % resultan ser interesantes.
-    We propose a basic Open-Ended Evolution (OEE) algorithm, a variant of genetic
-    evolution algorithm where the objective differs from that of a regular genetic
-    algorithm,  in this case the final objective is not to reach a final state of
-    the evolution (an optimal solution) but to continue evolving and creating new
-    types of entities, perhaps more complex on each new generation. Solution
-    entities have the possibility to evolve not only inside the frame of their type,
-    but  they can create entirely new groups \cite{Standish2003}. Taylor et al.
-    \cite{Taylor2016,Taylor} defines OEE as a system capable of creating novelty
-    beyond a point where nothing changes on the current group of interest rather
-    than just converging to a stable or quasi-stable state.For this project, OEE is
-    defined simply as a genetic evolution process with different classes of objects,
-    with compositional and taxonomic relationships between them. Objects of each
-    class can evolve in parallel or as in this case, independently of each other. The
-    idea is based on the object oriented model, in which complex behavior can be
-    model using these principles. The rest of the paper is as follows.
-
-    %% TO DO: This needs to be adjusted to the final version. We need to use
-    % \ref for the numbers - MG
-
-    Section \ref{SoA}, contains a quick overview of some aspects used by different authors
-    in order to tackle this problem, their design and basic functionality, in
-    Section \ref{prop_method} the description of the current state of the project is explained, how
-    %% The following sentence is not clear.  % Maybe this modofocation is more understandable ? JSH
-    the candidate solutions are represented and the way we defined our fitness 
-    function to determine the playability and complexity of the generated levels, 
-    finally in Section \ref{conclusion} we provide our conclusions about the development of this
-    paper as well as improvements that can help to refine the proposed work.
+In this work, we found that an evolutionary algorithm can be used to create this
+type of content, because it is not only able to create levels that are
+interesting and diverse but also capable of producing levels an average human
+could have trouble imagining. The rest of the paper is as follows. Section
+\ref{SoA}, contains a quick overview of some aspects used by different authors
+to tackle this problem, their design, and basic functionality. In Section
+\ref{prop_method} we describe our current proposal.  How we modeled the
+candidate solutions and the way we defined our fitness function to determine the
+playability and complexity of the generated levels. Finally, in Section
+\ref{conclusion}, we provide our conclusions as well as improvements that can
+help to refine the proposed work.
 

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
SoA

@@
 \label{SoA}
-    In this Section we present PCG works relevant to the Level generation for the
-    Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized an AI
-    competition with the aim of developing intelligent agents that could play new
-    Angry Birds levels better than the best human players. The competition was then
-    collocated in other AI conferences. In order to train and test these agents,
-    more novel and some times difficult levels must be generated. A related
-    competition was then proposed by Stephenson et al. \cite{Stephenson} this time
-    with the goal of developing a level generator for the game. Several generators
-    have been proposed in the following years of competition. M. Katina et al.
-    \cite{Kaidan2015} propose a model in which the generation of content is
-    controlled by the skill of a player while actively playing the game, the moment
-    the player finishes a certain level the algorithm obtains the score and
-    generates the next level to be played. Y. Jiang et al. \cite{Jiang2017} proposed
-    the use of predefined letter style patterns and combined to create a small pool
-    of words and letters used to be combined in order to create levels with text on
-    them, the participants would play the game and after that they would be asked if
-    they liked the layout of the levels. A search based approach has been also used
-    in several works. Laura Calle \cite{lauracalle} proposed a method in which the 
-    pieces in the game are arranged in groups using the gravity of the game to 
-    create structures that are later evolved into more complex levels, this method 
-    was used as a base to work with since it used a modified version of the angry 
-    birds game that was able to obtain the data of a level after a simulation.
+In this Section, we present PCG works relevant to the level generation for
+the Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized
+an AI competition to develop intelligent agents that could play new  Angry
+Birds levels better than the best human players. The competition was then
+collocated in other AI conferences. To better train and test agents, more
+novel and some times, challenging levels must be generated. Stephenson et
+al. proposed a related competition this time with the goal of developing a
+level generator for the game. Researchers have proposed several generators
+in the following years of competition. M. Katina et al.  \cite{Kaidan2015}
+propose a model in which the algorithm controls the generation of content by
+using the skill of a player, while she is actively playing the game. The
+moment the player finishes a certain level, the algorithm obtains the score
+and generates the next level to play. Y. Jiang et al. \cite{Jiang2017}
+proposed the use of predefined letter patterns and combined them to create a
+small pool of words and letters used to create levels with text on them.
+Users would play the game, and after that,   asked them if they liked the
+layout of the Levels.  Several researchers follow a search-based approach.
+Calle et al. \cite{lauracalle} propose a free-search method to generate
+levels.  For this, lists of blocks are placed in the game by the algorithm,
+and those maintaining their positions against gravity are selected to build
+structures. The resulting structures continue evolving into more complex
+levels. That work is the basis of our current proposal, and since we are
+using a modified version of the Angry Birds game, that can obtain data of a
+level after a simulation.
     %%%

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
abstract

@@
 \begin{abstract}
-In this paper we propose an evolutionary computation-based system to generate
-levels for the Angry Birds video game. The levels themselves are composed of a
-set of birds that the player can use, a certain amount of pigs that must be
-destroyed in order to progress to the next level and a given number of pieces
-that conform structures that may or may not protect the pigs from the player.
-The focus in this stage of the work is the generation of diverse structures that
-can be played in the game having the additional characteristics of being
-interesting and playable. We propose a multi-layered search, first constructing
-composite structures from basic components, to then build more complex
-structures building from these components, following an open-ended evolution
-approach in which the evolution of structures is not guided towards a single
-objective but is rather free to evolve and generate novelty or diversity. The
-objective is then that the proposed levels are evaluated by how complex they
-become and how different they are from the rest of the group. The experiments
-conducted show that a evolutionary approach allows the generated levels to be
-unique since, on most cases, the way they are presented on screen is a way a
-normal human would have trouble to create but at the same time are interesting
-to see.
+In this paper, we propose an evolutionary algorithm that follows an
+open-ended evolution approach to generate levels for the Angry Birds video
+game. The levels themselves are composed of a set of birds that the player
+can use, a certain amount of pigs that they must destroy, and a given number
+of pieces that conform structures that may or may not protect the pigs from
+birds. The current goal is the generation of diverse structures playable in
+the game, having the additional characteristics of being fun and enjoyable.
+We propose a multi-layered search, first constructing composite structures
+from basic blocks, to then build more complex structures building from these
+composites, following an open-ended evolution approach in which the
+evolution of structures is not guided towards a single objective but is
+rather free to evolve and generate novelty or diversity. The fitness
+function we use to evaluate the proposed levels considers how complex they
+have become and how different they are from the rest of the group. The
+experiments conducted show that an evolutionary approach allows the
+generated levels to be novel and interesting to play.
 % Another revision to English would be good.
+% Done - Mario
 \end{abstract}
@@
     \label{prop_method}  
+    % Is this explanation undertandable ? JSH
+    In this Section, we describe the approach used in this work, explaining
+first, the restrictions of the game, then giving a quick overview of how we
+create new composites to be used by the algorithm, then we define how candidate
+solutions are to be represented by the algorithm. We then describe our method to
+evaluate candidate solutions. Finally, we present details of the evolutionary
+algorithm.
 
-    % Is this explanation undertandable ? JSH
-    In this section we describe the approach used in this work, explaining first,
-    the restrictions of the game, then giving a quick overview of how we create new 
-    composites to be used by the algorithm, then explaining how the candidate solutions 
-    are represented and how this are modified and evolved by the algorithm, and finally 
-    we present our method to evaluate the candidate solutions.
-
-    The game contains a total of 11 block shapes as shown in Figure \ref{piece_list}.
-    These basic blocks cannot be modified, it is not possible to add more or modify the existing ones,
-    with this in mind the purpose is to create composites of these blocks in
-    different locations and angles in order to create structures that can be used as
-    building blocks for more complex structures.
+The game contains a total of 11 block shapes, shown in Figure
+\ref{piece_list}. These basic blocks cannot be modified, and we can not add
+more. With this in mind, we propose to create additional elements by creating
+composites of these blocks. Atomic blocks can be positioned in different
+locations and at certain angles, inside the composite. The resulting composites
+are themselves the new building blocks of more complex structures.
 
@@
 
-    Since there is no way to \textit{add} a new composite to the pool of blocks,
-    then a way to combine both is needed, in order to do this first the original
-    11 pieces of the game will be converted into composites of a single element.
-    A composite is defined as a lists of blocks, then a \textit{composite} of
-    one element will be created for each piece. Composites are the first layer
-    the building blocks for the structures to come. A composite could include
-    different types of blocks, rotated at a certain angle and compose a basic
-    structure. An ideal composite could support other composites on top with out
-    falling apart, but this is not required. A composite is measured using
-    imaginary bounding box, defined by calculating the lengths of all the pieces,
-    finding the borders of said pieces and then finding the points that could
-    define a box around all of them, then use this defined box to calculate the
-    height and width of the new composite and then calculate from the center
-    point of said box the offsets from the center of the group to the center of
-    each respective piece as shown on figure \ref{bounding_boc_calc}, this
-    information is needed in order to add it as a new composite so it can be
-    used to place the pieces in their respective new positions when the files
-    needed for the simulation are being created. This is similar to creating a
-    group of elements in a drawing application.
+Since there is no way to \textit{add} a new composite to the pool of blocks, we
+first need a way to combine them. To do this, first, the original 11 blocks of
+the game need to be converted into composites of a single element.  We define a
+composite as a list of blocks; then  \textit{composite} with a single block,
+will be created for each original block. Composites are the first layer, the
+building blocks for the structures to come. A composite could include different
+types of blocks, rotated at a certain angle and compose a basic structure. An
+ideal composite could support other composites on top without falling apart, but
+this is not required. A composite is measured using an imaginary bounding box,
+defined by calculating the lengths of all the pieces, finding the borders of
+said pieces and then finding the points to define a box around all of them. We
+then use this defined box to calculate the height and width of the new
+composite. Then we derive from the center point of the said box, the offsets for
+each block in the composite, as shown in figure \ref{bounding_boc_calc}. We need
+this information to treat each composite as if it was a single block; this will
+enable the placements of the composites in their respective new position when we
+create the files needed for the simulation. This process is similar to creating
+a group of elements in a drawing application.
 
     %% 
-    Good composites can be found using an evolutionary approach proposed earlier 
-    by Calle and Merelo, where basic structures are generated by searching a space
-    of falling blocks and selecting those that remain standing. This algorithm is 
-    not capable of creating complex structures, but it can generate very novel basic
-    structures. We can see that the evolution at this level can benefit from having
-    more freedom in how basic structures are built. We do not want to form piles
-    or sequences of blocks, this will be done at a higher level in the composite hierarchy.
-
+Suitable composites can be found using an evolutionary approach proposed
+earlier by Calle and Merelo, where basic structures are generated by freely
+searching a space of falling blocks and selecting those that remain
+standing. This algorithm is not capable of creating complex structures, but
+it can produce original basic structures. We can see that evolution at this
+level can benefit from having more freedom when building basic structures.
+At this time, we do not want to form piles or sequences of blocks, this will
+be done later, at a higher level in the composite hierarchy.    
 At this level the composite generator has the following steps:
@@
 
-    Another option is to just manually generate interesting composites to be used by the algorithm.
-    We could say that the previous approach is an option for a procedural generation of composites.
+Another valid option is to generate interesting composites manually.  The
+algorithm can later use the composites. We could say that the approach we
+explained earlier, is an optional procedural generation of composites.
 
@@
 \centerline{\includegraphics[width=80mm]{Images/list_pieces.png}}
-    \caption{List of pieces in the angry birds game.}
+\caption{List of blocks in the angry birds game.}
 \label{piece_list}
@@
     % Explain a bit about the competition, from the introduction
-    The Angry Birds level generation track is a competition where the objective is 
-    to generate levels that are \textit{fun} and \textit{enjoyable} however they 
-    also have to be challenging but not impossible. However the rules for the competition 
-    specify that a configuration file must be used to
-    generate the levels of the game in a limited amount of time, the information on
-    the configuration file is first the number of \textit{different} levels
-    that must be generated, the second value is the different materials \textit{not
-    allowed} to be used, for instance a group of generated levels must not have
-    circles which composition material is ice or stone, moreover it does not have to
-    integrate a triangle piece with ice, stone or wood material so this combinations
-    must be removed from the pool of options, the third configuration value is the
-    \textit{number of pigs} that must be placed in a level, and finally the
-    \textit{limit} of time that the system has to create the required amount of
-    levels.
-
-    In our original approach, composites could added to the structure generator
-    algorithm at runtime as a mutation of an individual. The structure generator
-    is explained in the next section.
-    In our current approach the composite generator is only
-    run once at the beginning, as a setup process.
+The Angry Birds level generation track is a competition where the objective
+is to generate levels that are \textit{fun} and \textit{enjoyable}. However,
+they also have to be challenging but not impossible. The rules for the
+competition specify that a configuration file must be used to generate the
+levels of the game in a limited amount of time. The file contains several
+restrictions; we explain each one next. The number of \textit{different}
+levels that must be generated. The materials that are \textit{not allowed}.
+For instance, a group of generated levels must not have circles which
+composition material is ice or stone. Moreover, a material with a veto,  can
+not integrate others. The third configuration value is the \textit{number of
+pigs} that we must place in a level. Finally, the \textit{limit} of time
+that the system has to generate the required amount of levels.
 

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
Expands graphics, we can have 8 pages

@@
      figure \ref{results_old}. There is an option in the system to generate in a
+     %           xxxxxxxxxxx This is missing and I have no idea where it is - JJ
      first step a collection of masks, following this rules, but this approach
@@
     \end{figure}
-
+    %
     \begin{figure}[htbp]
@@
     \end{figure}
-
+    %
+    %
     \begin{figure}[htbp]
@@
     \end{figure}
-
-    \begin{figure}[htbp]
-    \centerline{\includegraphics[width=80mm]{Images/new_model_v2.png}}
+    %
+    \begin{figure*}[htbp]
+    \centerline{\includegraphics[width=160mm]{Images/new_model_v2.png}}
     \caption{New system diagram based on the parameter file and the new chromosome representation.}
     \label{new_model}
-    \end{figure}
+    \end{figure*}
 
@@
 
-    \begin{figure}[htbp]
-        \centerline{\includegraphics[width=80mm]{Images/Result_n2.png}}
+    \begin{figure*}[htbp]
+        \centerline{\includegraphics[width=160mm]{Images/Result_n2.png}}
         \caption{Example of resulting level with current system.}
         \label{result_1}
-    \end{figure}
+    \end{figure*}
 

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
A few corrections

@@
 The Angry Birds level generation track is a competition where the objective
-is to generate levels that are \textit{fun} and \textit{enjoyable}. However,
-they also have to be challenging but not impossible. The rules for the
+is to generate levels that are \textit{fun} and \textit{enjoyable}; they also have to be challenging but not impossible. The rules for the
 competition specify that a configuration file must be used to generate the
 levels of the game in a limited amount of time. The file contains several
-restrictions; we explain each one next. The number of \textit{different}
-levels that must be generated. The materials that are \textit{not allowed}.
-For instance, a group of generated levels must not have circles which
-composition material is ice or stone. Moreover, a material with a veto,  can
-not integrate others. The third configuration value is the \textit{number of
-pigs} that we must place in a level. Finally, the \textit{limit} of time
+restrictions; namely:\begin{itemize}
+\item   The number of \textit{different}
+levels that must be generated. 
+\item The materials that are \textit{not allowed}.
+
+For instance, a group of generated levels must not have spheres composed of  is ice or stone. Moreover, a banned material can
+not integrate others. 
+\item The third configuration value is the \textit{number of
+pigs} that we must place in a level. 
+\item Finally, the \textit{limit} of time
 that the system has to generate the required amount of levels.
+\end{itemize}
+
+We will present next a system for evolving structures that respects those restrictions.
 
@@
     \centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
-    \caption{Structure at beginning and end of a simulation.}
+    \caption{Structure at the beginning and end of a simulation.}
     \label{test_old}
     \end{figure}
-
+    %
     Structures are the next evolutionary layer, at a higher level of composition.
@@
     constructing levels has the advantage of
-    limiting the search space, to structures that have a better chance to be 
+    limiting the search space to structures that have a better chance to be 
     standing after the simulation ends. There is no warranty that piles of 
-    composite blocks will maintain balance, so again we must search for those 
+    composite blocks will keep the balance, so again we must search for those 
     structures.
@@
     \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
-    an id assigned to it. A structure is then a list of ids, referring to
-    composite blocks, the first 11 are basic composite and generated composites 
+    an ID assigned to it. A structure is created from a list of IDs, every one of them referring to
+    composite blocks; the first 11 are basic composites, while generated composites 
     are assigned a higher number.  This way and individual can be
     represented as shown on figure \ref{old_chrom} where each chromosome
-    represents a certain item in the list of blocks, the numbers for this
-    elements are assigned in a first come first served basis, the numbers are
-    infinitely incremented and the same blocks can be repeated in a structure.
+    represents a certain item in the list of blocks, the numbers for these
+    elements are assigned in a first come first served basis; they can be infinitely incremented. The same blocks can be repeated in a structure.
 

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
Changing many this to these. Please check other possible grammar errors

@@
 Objects in a class can evolve in parallel or as in this case, independently
-of each other. The object-oriented model follows this principles to model
+of each other. The object-oriented model follows these principles to model
 complex behavior and structure \cite{levesque1986knowledge}.
@@
     elements are assigned in a first come first served basis; they can be infinitely incremented. The same blocks can be repeated in a structure.
+    % I don't understand this too well, maybe rephrasing would clarify - JJ
 
@@
     an individual is created it is ready to be evaluated in a simulation on the
-    game environment. Using a similar approach as the composite generator, all
+    game environment. %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
+    Using a similar approach as the composite generator, all
     individuals have a maximum of ten seconds to maintain balance or reach
-    absolute stability, if absolute stability is reached it means one of two
+    absolute stability. If that happens  it means one of two
     things, first the generated structure is completely stable or second, the
@@
     points so before the simulation starts each of them are viable candidates to
-    be an elite member of the population regardless of their relative height or
+    be an elite % Elite? - JJ
+    member of the population regardless of their relative height or
     complexity.
@@
     takes place, in this phase the resulting level is checked for those blocks that
-    survived, that is they where not destroyed by falling. Each one
-    of them is counted and then the resulting number is compared to that of the
-    initial quantity of pieces that were originally put in before the simulation,
-    each block represents a certain percentage of 100\% so the missing pieces 
+    survived, that is,  not destroyed by falling. Every one
+    of them is counted and then the resulting number is compared to the
+    initial quantity of pieces  before the simulation. Each block represents a certain percentage of 100\% so the missing pieces 
     are subtracted from the total. In this moment, each block is counted as if 
     it was not a member of a composite, this is because after the simulation there is
-    only data about each individual block.
+    only data about each individual block. % What is a composite? The fitness is only the number of remaining blocks? Even if they are in the floor?
 
@@
      The positioning of structures in the map is important in order to generate
-     levels that are fun and aesthetic. For this we need a method to indicate the
+     levels that are fun and aesthetically pleasing. For this we need a method to indicate the
      positioning of each structure. We propose the use of a mask where the
@@
      figure \ref{results_old}. There is an option in the system to generate in a
-     %           xxxxxxxxxxx This is missing and I have no idea where it is - JJ
-     first step a collection of masks, following this rules, but this approach
+     first step a collection of masks, following these rules, but this approach
+     % in many cases this is used instead of these. Please check that - JJ
      has a drawback. Pre-generating masks would not allow the generator to
@@
      the total amount of assigned blocks in all columns must be the same as the
-     total pieces allowed in each individual. The number of maximum blocks is as
+     total pieces allowed in each individual. The number of maximum blocks is
      a parameter. An example of this can be seen in figure \ref{new_chrom} where
-     the total of pieces in a individual is 18 and this pieces are distributed
+     the total of pieces in a individual is 18 and these pieces are distributed
      on all the columns available.
@@
         pigs assigned to the level and an array of locations for the placement
-        of this same pigs, a representation of it is shown on figure
+        of these same pigs, a representation of it is shown on figure
         \ref{enemy_layer}. 
@@
     possibility that a mask that uses less pieces that it normally as can obtain a
-    better fitness than one that uses all of them. An example of this two crossover
+    better fitness than one that uses all of them. An example of these two crossover
     types can be seen in figure \ref{crossover} in which the mask of an individual
@@
 
-    This mutations do not have to be used all at the same time on a single
+    These mutation operators do not have to be used all at the same time on a single
     individual but depending on the probabilities they can happen all at once,
@@
 
-    Using all this configurations the system is capable of creating levels, some of
+    Using all these configurations the system is capable of creating levels, some of
     them playable as shown in figure \ref{result_1} however the levels that can be
@@
     changed in future instances but the generator itself is able to be used as a
-    base for a more complex one, and as shown in the future work section this issues
+    base for a more complex one, and as shown in the future work section these issues
     can be solved by different means.
@@
     because the current evaluation method allows us to generate playable levels,
-    this levels are far from ideal in the way that they only use a certain range of
+    these levels are far from ideal in the way that they only use a certain range of
     items present in the game therefore reducing the potential of a level, we expect

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
Adds corrections and acks

@@
     required, since the current way to calculate the fitness and create the next
-    generations of a population the system requires the system to execute
-    simulations of the levels on every generation that passes therefore increasing
-    the time it takes to complete an entire cycle of execution, so in order to
+    generations of a population requires the system to execute
+    simulations of the levels on every generation that passes, therefore increasing
+    the time it takes to complete an entire cycle of execution. In order to
     change this we require to create a way to evaluate a level using only the
@@
     predict the way a level will behave when placed in a real simulation environment
-    therefore drastically reducing execution times.
+    therefore drastically reducing execution times. %You can also take into account restrictions without simulation, as we do in our paper, or use a Physics engine - JJ
 
-    We were able to fulfill our objective of generating levels that could be played, 
-    however as seen in our figures the current state of this system is still in development 
-    phase, and some modifications must be applied in order to optimize some aspects of it, 
+    We were able to fulfill our objective of generating levels that could be played;
+    however, as seen in our figures, the current state of this system is still in the development 
+    phase, and some modifications must be applied in order to optimize some aspects of it. For instance  
     by using a different way of generating individual we were able to reduce the process 
-    time required on a full system execution however we require to search for a way to 
+    time required on a full system execution; however we need to search for a way to 
     avoid using the software to evaluate the individuals, this way we expect to reduce 
-    drastically the time required to process the data of the levels.
+    drastically the time required to process the data of the levels.  % Cite our paper, where we do exactly that - JJ
 
-    Finally a different method to evaluate the individuals must be created, this is
-    because the current evaluation method allows us to generate playable levels,
+    Finally a different method to evaluate the individuals must be created. Since the current evaluation method allows us to generate playable levels,  
     these levels are far from ideal in the way that they only use a certain range of
@@
 
+\section*{Acknowledgments}
+
+This work has been supported in part by: Ministerio espa\~{n}ol de
+Econom\'{\i}a y Competitividad under project TIN2017-85727-C4-2-P (UGR-DeepBio).
+
 \bibliographystyle{IEEEtran}

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
few changes

@@
 \begin{abstract}
-In this paper, we propose an evolutionary algorithm that follows an
-open-ended evolution approach to generate levels for the Angry Birds video
-game. The levels themselves are composed of a set of birds that the player
-can use, a certain amount of pigs that they must destroy, and a given number
+In this paper, we propose an evolutionary algorithm that follows an open-ended
+evolution approach to generate levels for the Angry Birds video game. The levels
+themselves are composed of a set of birds that the player can throw with a
+slingshot, a certain amount of pigs that they must destroy, and a given number
 of pieces that conform structures that may or may not protect the pigs from
-birds. The current goal is the generation of diverse structures playable in
-the game, having the additional characteristics of being fun and enjoyable.
-We propose a multi-layered search, first constructing composite structures
-from basic blocks, to then build more complex structures building from these
-composites, following an open-ended evolution approach in which the
-evolution of structures is not guided towards a single objective but is
-rather free to evolve and generate novelty or diversity. The fitness
-function we use to evaluate the proposed levels considers how complex they
-have become and how different they are from the rest of the group. The
-experiments conducted show that an evolutionary approach allows the
-generated levels to be novel and interesting to play.
+birds thrown at them. The current goal is the generation of diverse structures
+that are playable in the game, having the additional characteristics of being
+fun and enjoyable. We propose a multi-layered search, first constructing
+composite structures from basic blocks, to then build more complex structures
+building from these composites. We follow an open-ended evolution approach in
+which the evolution of structures is not guided towards a single objective but
+is rather free to evolve and generate novelty or diversity. The fitness function
+we use to evaluate the proposed levels considers how complex levels have become
+and how different they are from the rest of the population. The experiments
+conducted show that an evolutionary approach allows the generation of levels
+that are novel and interesting to play.
 % Another revision to English would be good.
@@
 level after a simulation.
-    %%%
-    % TO DO: Laura´s work here 
-    %%%
 
@@
     \label{prop_method}
-    % Is this explanation undertandable ? JSH
+
 In this Section, we describe the approach used in this work, explaining
@@
 \end{figure}
-    % Explain a bit about the competition, from the introduction
-The Angry Birds level generation track is a competition where the objective
-is to generate levels that are \textit{fun} and \textit{enjoyable}; they also have to be challenging but not impossible. The rules for the
-competition specify that a configuration file must be used to generate the
-levels of the game in a limited amount of time. The file contains several
-restrictions; namely:\begin{itemize}
+
+The Angry Birds level generation track is a competition where the objective is
+to generate levels that are \textit{fun} and \textit{enjoyable}; they also have
+to be challenging but not impossible. The rules for the competition specify that
+a configuration file must be used to generate the levels of the game in a
+limited amount of time. The file contains several restrictions;
+namely:\begin{itemize}
 \item   The number of \textit{different}
@@
 
-For instance, a group of generated levels must not have spheres composed of  is ice or stone. Moreover, a banned material can
-not integrate others. 
-\item The third configuration value is the \textit{number of
-pigs} that we must place in a level. 
-\item Finally, the \textit{limit} of time
-that the system has to generate the required amount of levels.
+For instance, a group of generated levels must not have spheres composed of  is
+ice or stone. Moreover, a banned material can not integrate others. 
+\item The third configuration value is the \textit{number of pigs} that we must
+place in a level. 
+\item Finally, the \textit{limit} of time that the system has to generate the
+required amount of levels.
 \end{itemize}
@@
 Structures are represented in a way similar to Togelius et al.
-    \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
-    an ID assigned to it. A structure is created from a list of IDs, every one of them referring to
-    composite blocks; the first 11 are basic composites, while generated composites 
-    are assigned a higher number.  This way and individual can be
-    represented as shown on figure \ref{old_chrom} where each chromosome
-    represents a certain item in the list of blocks, the numbers for these
-    elements are assigned in a first come first served basis; they can be infinitely incremented. The same blocks can be repeated in a structure.
+\cite{togelius2016Representationsforsearch-basedmethods}. We can model a
+structure as a collection of composites, each one selected from a pool of
+currently available composites. Initially, the pool contains only the 11
+original blocks represented as single-element composites. As new composites are
+automatically (or manually) generated from the original blocks, we insert them
+to the pool and assign each one an ID. We can model the chromosome of a
+structure, as shown in Figure \ref{old_chrom} where each gen is an ID from a
+composite in the pool. A chromosome can include the same ID multiple times.
     % I don't understand this too well, maybe rephrasing would clarify - JJ
+    % Done - Mario
 
@@
     game environment. %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
+    % I will comment that we could work on that. At the moment each one is evaluated. - M
+
     Using a similar approach as the composite generator, all
@@
     points so before the simulation starts each of them are viable candidates to
-    be an elite % Elite? - JJ
+    be an Elite % Elite? - JJ
+    % But I think the problem remains, there is no difference even if they all have
+    % zero points. But randomess in the selection coyuld do that. - Mario
     member of the population regardless of their relative height or

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
all corrections and  questions of  JJ addressed

@@
     These structures represent individuals in the evolutionary algorithm. Once
-    an individual is created it is ready to be evaluated in a simulation on the
-    game environment. %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
-    % I will comment that we could work on that. At the moment each one is evaluated. - M
-
+    we create an individual, it is ready to be evaluated in a simulation on the
+    game environment.  It is important to note that this is the most
+    time-consuming task of the process. We could benefit from using alternative
+    techniques like the one proposed by Calle et al. \cite{lauracalle}, where
+    only those individuals that meet certain restrictions are candidates for a
+    run in the simulator.
+    %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
+    % Added a comment about this  - M 
     Using a similar approach as the composite generator, all
@@
     There are other variables we take in to account, but they will be explained
-    later. In this initial stage, each individual in the population has 100
-    points so before the simulation starts each of them are viable candidates to
-    be an Elite % Elite? - JJ
+    later. 
+    % I commented the paragraph below because IMHO the reasoning is not right - Mario 
+    %In this initial stage, each individual in the population has 100
+    %points so before the simulation starts each of them are viable candidates to
+    %be an Elite % Elite? - JJ
+
     % But I think the problem remains, there is no difference even if they all have
     % zero points. But randomess in the selection coyuld do that. - Mario
-    member of the population regardless of their relative height or
-    complexity.
 
-    First, after each of the individual simulations are over the evaluation process
-    takes place, in this phase the resulting level is checked for those blocks that
-    survived, that is,  not destroyed by falling. Every one
-    of them is counted and then the resulting number is compared to the
-    initial quantity of pieces  before the simulation. Each block represents a certain percentage of 100\% so the missing pieces 
-    are subtracted from the total. In this moment, each block is counted as if 
-    it was not a member of a composite, this is because after the simulation there is
-    only data about each individual block. % What is a composite? The fitness is only the number of remaining blocks? Even if they are in the floor?
+    %member of the population regardless of their relative height or
+    %complexity.
+
+    First, after all of the individual simulations are over the evaluation
+    process takes place, in this phase the resulting levels are checked for those
+    blocks that survived, that is,  they were not destroyed by falling. Every one of them
+    is counted and then the resulting number is compared to the initial quantity
+    of pieces found before the simulation started. Each block represents a certain percentage
+    of 100\% so the missing pieces are subtracted from the total. In this
+    moment, each block is counted as if it was not a member of a composite, this
+    is because after the simulation there is only data about each individual block. 
+    % What is a composite? There is a whole section devoted to explaining just that :) - Mario 
+    % The fitness is only the number of remaining blocks? Even if they are in the floor? 
+    % Yes, they some time form nice structures. We used to take height into account, but is not 
+    % that important.  - Mario 
+    % Will comment on it, after checking with Jaime if I'm right.
 
@@
     required, since the current way to calculate the fitness and create the next
-    generations of a population requires the system to execute
-    simulations of the levels on every generation that passes, therefore increasing
+    generations of a population requires the execution of many 
+    simulations on every generation, therefore increasing
     the time it takes to complete an entire cycle of execution. In order to
@@
     predict the way a level will behave when placed in a real simulation environment
-    therefore drastically reducing execution times. %You can also take into account restrictions without simulation, as we do in our paper, or use a Physics engine - JJ
+    therefore drastically reducing execution times. We could take into account restrictions 
+    needed to run a simulation, as it is done by Calle et al. \cite{lauracalle}, 
+    or use a Physics engine that is optimiezed for this task.
 
@@
     by using a different way of generating individual we were able to reduce the process 
-    time required on a full system execution; however we need to search for a way to 
-    avoid using the software to evaluate the individuals, this way we expect to reduce 
-    drastically the time required to process the data of the levels.  % Cite our paper, where we do exactly that - JJ
+    time required on a full system execution; however we still need to work on this problem as
+    we mention before.  % Cite our paper, where we do exactly that - JJ 
+                        % Done - Mario
 
-    Finally a different method to evaluate the individuals must be created. Since the current evaluation method allows us to generate playable levels,  
-    these levels are far from ideal in the way that they only use a certain range of
-    items present in the game therefore reducing the potential of a level, we expect
-    to make the current fitness function work the most efficient that it can but
-    another possible solution is found a good combination of formulas to generate
-    the fitness function.
+    Finally a different method to evaluate the individuals must be created.
+    Since the current evaluation method allows us to generate playable levels,
+    these levels are far from ideal in the way that they only use a certain
+    range of items present in the game therefore reducing the potential of a
+    level, we expect to make the current fitness function work the most
+    efficient that it can but another possible solution is found a good
+    combination of formulas to generate the fitness function.
 

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Changes name of article

--- 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
@@
 when generating content for different video game projects, without
-compromising qualitiy \cite{Yannakakis2017,YannakakisContentGeneration}. In
+compromising quality \cite{Yannakakis2017,YannakakisContentGeneration}. In
 this paper, we introduce an evolutionary content generation system, to
@@
     needed to run a simulation, as it is done by Calle et al. \cite{lauracalle}, 
-    or use a Physics engine that is optimiezed for this task.
+    or use a Physics engine that is optimized for this task.
 

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Revised introduction

@@
 that are novel and interesting to play.
-% Another revision to English would be good.
-% Done - Mario
 \end{abstract}
@@
 Genetic algorithm, procedural generated content, open-ended evolution,
-evolutionary computation
+evolutionary computation, games.
 \end{IEEEkeywords}
@@
 \section{Introduction}
-The video game industry is always looking for content creators to satisfy
-the demand for high-quality content. Current development teams include game
-designers,  artists, animators,  writers, level designers, among others.
+
+The video game industry is always looking for content creators in order to satisfy
+the demand for high-quality, and diverse, content. Current development teams include game 
+designers,  artists, animators,  writers, and level designers, among others.
 Procedural Content Generation (PCG) is often applied to generate many
-aspects of the game, from maps, levels or characters, to narrative and game
+aspects of the game, from maps, levels or characters, to narrative and overall
 design. PCG techniques can lower the cost in both time and human resources
@@
 compromising quality \cite{Yannakakis2017,YannakakisContentGeneration}. In
-this paper, we introduce an evolutionary content generation system, to
-generate fun and exciting levels for the popular Angry Birds video game. We
-follow an Open-Ended Evolution (OEE) approach.  OOE is a type of genetic
-evolution algorithm with a different objective. In this case, the goal is
-not to reach a final state of in the evolution, for instance, to reach an
-optimal solution in a search space. An OEE aims to continue evolving and
+this paper, we introduce an evolutionary content generation system that is able to 
+generate fun and exciting levels for the popular Angry Birds video game \cite{RovioEntertainmentCorporation2009}.
+
+We are goint to follow an Open-Ended Evolution (OEE) approach.  OEE is a type of genetic evolution algorithm in which the goal is
+not so much to reach a final, possible optimal, state of in the evolution, for instance but to continue evolving and
 creating new types of entities, perhaps more complex or novel on each new
-generation. Entities evolve not only inside the frame of their species, but
+generation. Entities evolve not only inside the context of their species, but
 they can also create entirely new species \cite{Standish2003}. Taylor et al.
@@
 of each other. The object-oriented model follows these principles to model
-complex behavior and structure \cite{levesque1986knowledge}.
+complex behavior and structure \cite{levesque1986knowledge}. % Maybe specify what you mean by "classes" in this context - JJ
 
@@
 competition for the Angry Birds video game developed by Rovio Entertainment.
-We briefly explain the game.  The objective is to destroy structures placed
+We briefly explain the game. % Already mentioned above. Maybe it would be better to move this paragraph to where you mention it for the first time - JJ
+The objective is to destroy structures placed
 on a map as well as eliminating green pig-like characters. In order to
@@
 \textit{ice}, \textit{wood} and \textit{stone}, each one with a different
-resistance, ranging from fragile, normal and sturdy in that order. The game
+resistance: fragile, normal or sturdy. The game
 mechanic is to use a slingshot to shoot a certain number of birds with
@@
 Stephenson2018}.
-% What is the problem?
+% What is the problem? Please formulate this with more precision - JJ
 
@@
 and mechanics. In this case, we have additional restrictions, dictated by the
-competition track \cite{Renz}. This case study provides an interesting challenge
+competition track \cite{Renz}. % make some mention to why this is important - JJ
+This case study provides an interesting challenge
 for the participating algorithms. The proposed PCG algorithm has to be flexible

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Revised state of the art. I think we need more here

@@
 \label{SoA}
-In this Section, we present PCG works relevant to the level generation for
-the Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized
+
+The organization by Renz et al. \cite{Renz, Renz2015TheAB}  of an 
 an AI competition to develop intelligent agents that could play new  Angry
-Birds levels better than the best human players. The competition was then
-collocated in other AI conferences. To better train and test agents, more
+Birds levels better than the best human players was a very interesting boost to this area, and also boosted in general PCG by offering a challenge in different levels: from the physical, structural level, to the game play and aesthetic one.
+
+To better train and test agents, more
 novel and some times, challenging levels must be generated. Stephenson et
-al. proposed a related competition this time with the goal of developing a
+al. proposed a related competition \cite{Stephenson2018} this time with the goal of developing a
 level generator for the game. Researchers have proposed several generators
@@
 level after a simulation.
+This model was later sped up using a specific Physics library, which allowed a deeper exploration of the search space \cite{DBLP:conf/ijcci/CalleGVG19}.
+However, the main problem with this approach, which was open-ended in the sense that it was almost impossible to define an optimum, was that it was also free-form and structures obtained were not really all that interesting, although they were very diverse and quite solid.
 

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Rearranges and updates state of the art

@@
 level generator for the game. Researchers have proposed several generators
-in the following years of competition. M. Katina et al.  \cite{Kaidan2015}
-propose a model in which the algorithm controls the generation of content by
-using the skill of a player, while she is actively playing the game. The
+in the following years of competition. M. Katina et al. In Kaidan's model \cite{Kaidan2015}, the algorithm controls the generation of content by
+using the skill of a player, while she is actively playing the game; The
 moment the player finishes a certain level, the algorithm obtains the score
-and generates the next level to play. Y. Jiang et al. \cite{Jiang2017}
-proposed the use of predefined letter patterns and combined them to create a
-small pool of words and letters used to create levels with text on them.
-Users would play the game, and after that,   asked them if they liked the
-layout of the Levels.  Several researchers follow a search-based approach.
+and generates the next level to play. The model proposed by Stephenson and Renz \cite{DBLP:journals/corr/abs-1902-02518} also adapts itself to the level of difficult that's needed.
+
+Several researchers follow a search-based approach.
 Calle et al. \cite{lauracalle} propose a free-search method to generate
-levels.  For this, lists of blocks are placed in the game by the algorithm,
+levels for Angry Birds.  For this, lists of blocks are placed in the game by the algorithm,
 and those maintaining their positions against gravity are selected to build
@@
 
+% This reference is not terribly relevant
+PCG methods are also used in different contexts: Y. Jiang et al. \cite{Jiang2017}
+proposed the use of predefined letter patterns and combined them to create a
+small pool of words and letters used to create levels with text on them.
+Users would play the game, and after that,   asked them if they liked the
+layout of the Levels.
+% ----------------------------------------
     \section{Proposed Method}

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Completes first pass of SoA. Still one to go

@@
 
+The objective of generating levels need not be pure gameplay or enjoyment.
+Angry Birds have been also used for trying to promote mental well-being, the point of it being that the game can be used as a vehicle for art therapy \cite{fang2019angrybirdslike}.
+Instead of using a search-based approach, levels are generated from sketches drawn by the patient using a method called Real Pixel Image Level Generator; the main objective is to get the players to smile.
+This interesting approach of using some external input to generate levels could be adapted or integrated easily into search-based approaches; at the same time, it is a way of exploring how to elicit different response from game players.
+
 % This reference is not terribly relevant
@@
 Users would play the game, and after that,   asked them if they liked the
-layout of the Levels.
+layout of the Levels. This interactive approach could, in principle, be also apprached in the generation of Angry Birds levels.
+
+In our case, interaction is not required or used; our main intention is to generate interesting and aesthetically pleasing levels. The methodology to achieve this is explained below.
+
 % ----------------------------------------

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Finishes state of the art

@@
 This interesting approach of using some external input to generate levels could be adapted or integrated easily into search-based approaches; at the same time, it is a way of exploring how to elicit different response from game players.
+
+It is also interesting how some authors take into account the dynamics of Angry Birds gameplay, where the {\em domino effect} makes a big structure tumble over: Abdullah et al.
+\cite{Abdullah2019} talk about ``Rube Goldberg machines''.
+This specific pattern (structures that can be destroyed with a single strike) makes them interesting, and also since they are designed from a series of pre-defined structures, stability is guaranteed.
+This approach is similar to other which use pre-defined patterns (such as a set of towers) to guarantee stability: Ferreira and Toledo \cite{ferreira2014search} use such approach, with predefined groups of elements stacked always in the same way to guarantee that stability.
+The authors proposed also Tanager \cite{8082517} which again uses different stacks to structure the level and the blocks used in it, but it also encodes empty stacks (which translate to gaps).
+This methodology gives much more variability.
+At the same time, the authors proposed new ways of evaluating the levels, including interacting with actual users.
 

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Finishing revision of the state of the art

@@
 moment the player finishes a certain level, the algorithm obtains the score
-and generates the next level to play. The model proposed by Stephenson and Renz \cite{DBLP:journals/corr/abs-1902-02518} also adapts itself to the level of difficult that's needed.
+and generates the next level to play.
+The model proposed by Stephenson and Renz \cite{DBLP:journals/corr/abs-1902-02518} also adapts itself to the level of difficult that's needed.
+Initial papers \cite{8080448} contained search-based PCGs that established certain patterns in the structure, and assigned blocks to them, looking to optimize overall stability, but also creating a complex fitness function that included several {\em colored} scores that considered how pigs were protected, for instance.
 
